---
title: "ClimatePCA"
author: "JL"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library("GGally")
library(corrplot)
library(ggfortify)
```

```{r}
# Add in climate data:
climate <- read.csv("C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/data_for_publication/CGOP_climatevalues_scaled.csv")

clim.names <- colnames(climate)
year <- climate[,1]
```
What this script does:

Uses cleaned climate data from Cowichan and does a PCA to help determine best 4 climate variables to include in model selection
#First, make correlation plot
```{r}
###################################################################################
#MAKE CORRELATION MATRIX
M<-cor(climate[,-1])
res1 <- cor.mtest(climate[,-1], conf.level = 0.95)
ord <- corrMatOrder(M, order = "AOE")

corrplot(M, p.mat = res1$p, method="circle",type="upper",insig = "p-value", sig.level=-1)
#so yes, some are correlated! onwards
```

Ok, the PCA!
The goal of PCA is to explain most of the variability in the data with a smaller number of variables than the original data set.

```{r}
pca_result <- prcomp(climate[,-1], scale = F) #variables are already scaled
pca_result$rotation

autoplot(pca_result, data = climate, loadings=T,loadings.label=T, label = T)
#or
biplot(pca_result, scale = 0)


#save df with just loadings for PC1:X
pca_loadings <- as.data.frame(pca_result$rotation) %>% select(1:10)
pca_loadings <- tibble::rownames_to_column(pca_loadings, "climate.var")
#this gives us the loadings for each climate variable, loadings can be interpreted as the correlation between the climate variable and the PC.

#make the scree plot: 
summary(pca_result)
VE <- pca_result$sdev^2
PVE <- VE / sum(VE)
PVE <- round(PVE, 2)

qplot(c(1:10), PVE) + 
  geom_col() + 
  xlab("Principal Component") + 
  ylab("Proportion of Variance Explained") +
  #ggtitle("Scree Plot") +
  ylim(0, 1)+
  scale_x_continuous(breaks = c(1,2,3, 4,5, 6,7, 8, 9, 10))
```
PC1 had the strongest loadings for winter temperature and spring temperature
PC2 had strongest loadings for summer temperature, spring precipitation
```{r}
loadings.save <- pca_loadings %>% 
  arrange(desc(abs(PC1)))
pca_loadings %>% 
  arrange(desc(abs(PC1)))
pca_loadings %>% 
  arrange(desc(abs(PC2)))
#write.csv(x = loadings.save, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/figures/climate/PCA long list/loadings table.csv", row.names = F)
```

