---
title: "Primula Clipping Experiment"
author: "JL"
date: "June 18, 2024"
output:
  word_document: default
  html_document: default
---

```{r read in packages, include = FALSE}
#packages:
library(tidyverse)
library(lme4)
theme_set(theme_classic()) # setting for ggplot
```

```{r read in data}
clip <- read.csv("C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/data_for_publication/Primula_Clipping_Experiment.csv")

clip <- clip %>% 
  mutate(year = as.factor(year),
         plot = as.factor(plot),
         tag = as.factor(tag),
         pflowerT1 = as.factor(pflowerT1),
         psurvivalT1 = as.factor(psurvivalT1), 
         trt = as.factor(trt))
clip$trt <- factor(clip$trt, levels = c("drought", "control", "irrigated"))
```

# LRT
How does status influence costs of reproduction?
Maximal model: Vital rate (in t+1) ~ size t + total seeds + preciptrt + total seeds* preciptrt + size*total seeds + size*preciptrt + size*total seeds*preciptrt + (1|plot)
Responses: Size(t+1), p(flower t+1), number flowers(t+1), survival(t+1)

For each vital rate, do likelihood ratio tests to determine significance of fixed effects

```{r growth LRT}
growth_LRT = data.frame(var = NA,
                        chi = NA, 
                        pvalue = NA)

growth_full <- lmer(log.ros.areaT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + log.ros.area:trt + log.ros.area:log.total.seeds:trt + (1|plot), data = clip, REML= F)
growth_no3way <- lmer(log.ros.areaT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + log.ros.area:trt + (1|plot), data = clip, REML= F)
a1 <- anova(growth_full, growth_no3way, test="LRT") #LRT test - removing 3 way interaction does not significantly change model
growth_LRT[1,] <- c("size:seeds:trt", a1[2,6], a1[2,8])


growth_no.seed.trt <- lmer(log.ros.areaT1 ~ log.ros.area + log.total.seeds + trt + log.ros.area:log.total.seeds + log.ros.area:trt + (1|plot), data = clip, REML= F)
a2 <- anova(growth_no3way, growth_no.seed.trt, test="LRT") #LRT test - removing seed:trt interaction does not significantly change model
growth_LRT[2,] <- c("seeds:trt", a2[2,6], a2[2,8])

growth_no.size.seeds <- lmer(log.ros.areaT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:trt + (1|plot), data = clip, REML= F)
a3 <- anova(growth_no3way, growth_no.size.seeds, test="LRT") #LRT test - removing size:seed interaction does not significantly change model
growth_LRT[3,] <- c("size:seed", a3[2,6], a3[2,8])


growth_no.size.trt <- lmer(log.ros.areaT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + (1|plot), data = clip, REML= F)
a4 <- anova(growth_no3way, growth_no.size.trt, test="LRT") #LRT test - removing size:trt does not significantly change model
growth_LRT[4,] <- c("size:trt", a4[2,6], a4[2,8])

growth_no.int <- lmer(log.ros.areaT1 ~ log.ros.area + log.total.seeds + trt + (1|plot), data = clip, REML= F)
growth_no.seeds <- lmer(log.ros.areaT1 ~ log.ros.area + trt + (1|plot), data = clip, REML= F)
a5 <- anova(growth_no.int, growth_no.seeds, test="LRT") #LRT test
growth_LRT[5,] <- c("totalseeds", a5[2,6], a5[2,8])
# 
# 
growth_no.trt <- lmer(log.ros.areaT1 ~ log.ros.area + log.total.seeds + (1|plot), data = clip, REML= F)
a6 <- anova(growth_no.trt, growth_no.int , test="LRT") #LRT test
growth_LRT[6,] <- c("trt", a6[2,6], a6[2,8])
growth_LRT
```

```{r growth best fit model log.ros.area + log.total.seeds}
#best supported model:
growth_no.trt <- lmer(log.ros.areaT1 ~ log.ros.area + log.total.seeds + (1|plot), data = clip, REML= F)
#create df with all possible x values
pred.dat <-  expand.grid(log.ros.area = seq(2, 5.5, by = .1), log.total.seeds = c(0, 1, 2, 2.5, 3, 4, 5, 5.2))
pred.dat.output.g <- cbind(pred.dat, log.ros.areaT1 = predict(growth_no.trt, newdata = pred.dat, type = "response", re.form = ~0))
pred.dat.output.g <- pred.dat.output.g %>% 
  mutate(total.seeds = if_else(log.total.seeds == 0, 0, round(exp(log.total.seeds))))

(growth <- ggplot(clip, aes(x = log.ros.area, y = log.ros.areaT1))+
  geom_abline(slope=1, intercept = 0, color= "black", linewidth = .2)+
  geom_point(aes(size = total.seeds), shape = 1, color = "black", alpha = 0.75)+
  scale_size(range=c(1.25, 2.5))+
  geom_line(data = subset(pred.dat.output.g, log.total.seeds == 5), aes(x = log.ros.area, y = log.ros.areaT1),color = "darkorchid4", linewidth = 1.5)+
  geom_line(data = subset(pred.dat.output.g, log.total.seeds == 2.5), aes(x = log.ros.area, y = log.ros.areaT1), color = "darkorchid2", linetype = "longdash", linewidth = 1.5)+
  geom_line(data = subset(pred.dat.output.g,  log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = "orchid1", linetype = "dashed", linewidth = 1.5)+
  scale_y_continuous(expand = c(0, 0), limits = c(2, 6))+
  scale_x_continuous(expand = c(0, 0), limits = c(2, 6))+
  labs(x = "log(Rosette Area) in 2021", y = "log(Rosette Area) in 2022", size = "Seeds in 2021", color = "Seeds in 2021")+
  theme(axis.line = element_line(colour = 'black', linewidth = 1.1), 
        text = element_text(size = 20),
        legend.title = element_text(size = 8),
        legend.text = element_text(size = 7))+
  coord_fixed(ratio=1) #makes plot square so legend doesnt warp it when saving in ggplot
)

#ggsave(plot = growth, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/clipping experiment/FINALgrowth result fig.png", width =6, height =5, dpi = 300)

#for this model, find % difference in size between low/high seeds
#for median size of plant, how much bigger are you the next year if you flower but make zero seeds versus if you flower and make a lot of seeds

median(clip$log.ros.area)
comp <- pred.dat.output.g %>% 
  filter(log.ros.area == "3.9") %>% 
  mutate(ros.areaT1 = exp(log.ros.areaT1))
```

```{r plower}
pflower_LRT = data.frame(var = NA,
                        chi = NA, 
                        pvalue = NA)

pflower_full <- glmer(pflowerT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + log.ros.area:trt + log.ros.area:log.total.seeds:trt + (1|plot), data = clip, family = "binomial")
pflower_no3way <- glmer(pflowerT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + log.ros.area:trt + (1|plot), data = clip, family = "binomial")
a1 <- anova(pflower_full, pflower_no3way, test="LRT") #LRT test - removing 3 way interaction does not significantly change model
pflower_LRT[1,] <- c("size:seeds:trt", a1[2,6], a1[2,8])


pflower_no.seed.trt <- glmer(pflowerT1 ~ log.ros.area + log.total.seeds + trt + log.ros.area:log.total.seeds + log.ros.area:trt + (1|plot), data = clip, family = "binomial")
a2 <- anova(pflower_no3way, pflower_no.seed.trt, test="LRT") #LRT test - removing seed:trt interaction does not significantly change model
pflower_LRT[2,] <- c("seeds:trt", a2[2,6], a2[2,8])

pflower_no.size.seeds <- glmer(pflowerT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:trt + (1|plot), data = clip, family = "binomial")
a3 <- anova(pflower_no3way, pflower_no.size.seeds, test="LRT") #LRT test - removing size:seed interaction does not significantly change model
pflower_LRT[3,] <- c("size:seed", a3[2,6], a3[2,8])


pflower_no.size.trt <- glmer(pflowerT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + (1|plot), data = clip, family = "binomial")
a4 <- anova(pflower_no3way, pflower_no.size.trt, test="LRT") #LRT test - removing size:trt does not significantly change model
pflower_LRT[4,] <- c("size:trt", a4[2,6], a4[2,8])

pflower_no.int <- glmer(pflowerT1 ~ log.ros.area + log.total.seeds + trt + (1|plot), data = clip, family = "binomial")
pflower_no.trt <- glmer(pflowerT1 ~ log.ros.area + log.total.seeds + (1|plot), data = clip, family = "binomial")
a5 <- anova(pflower_no.int, pflower_no.trt, test="LRT") #LRT test - removing size:trt does not significantly change model
pflower_LRT[5,] <- c("trt", a5[2,6], a5[2,8])

pflower_no.seeds <- glmer(pflowerT1 ~ log.ros.area + trt + (1|plot), data = clip, family = "binomial")
a6 <- anova(pflower_no.int, pflower_no.seeds, test="LRT")
pflower_LRT[6,] <- c("totalseeds", a6[2,6], a6[2,8])
pflower_LRT
```



```{r survival}
survival_LRT = data.frame(var = NA,
                        chi = NA, 
                        pvalue = NA)

survival_full <- glmer(psurvivalT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + log.ros.area:trt + log.ros.area:log.total.seeds:trt + (1|plot), data = clip, family = "binomial")
survival_no3way <- glmer(psurvivalT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + log.ros.area:trt + (1|plot), data = clip, family = "binomial")
a1 <- anova(survival_full, survival_no3way, test="LRT") 
survival_LRT[1,] <- c("size:seeds:trt", a1[2,6], a1[2,8])


survival_no.seed.trt <- glmer(psurvivalT1 ~ log.ros.area + log.total.seeds + trt + log.ros.area:log.total.seeds + log.ros.area:trt + (1|plot), data = clip, family = "binomial")
a2 <- anova(survival_no3way, survival_no.seed.trt, test="LRT") 
survival_LRT[2,] <- c("seeds:trt", a2[2,6], a2[2,8])

survival_no.size.seeds <- glmer(psurvivalT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:trt + (1|plot), data = clip, family = "binomial")
a3 <- anova(survival_no3way, survival_no.size.seeds, test="LRT") 
survival_LRT[3,] <- c("size:seed", a3[2,6], a3[2,8])


survival_no.size.trt <- glmer(psurvivalT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + (1|plot), data = clip, family = "binomial")
a4 <- anova(survival_no3way, survival_no.size.trt, test="LRT") 
survival_LRT[4,] <- c("size:trt", a4[2,6], a4[2,8])

survival_no.int <- glmer(psurvivalT1 ~ log.ros.area + log.total.seeds + trt + (1|plot), data = clip, family = "binomial")
survival_no.seeds <- glmer(psurvivalT1 ~ log.ros.area + trt + (1|plot), data = clip, family = "binomial")
survival_no.trt <- glmer(psurvivalT1 ~ log.ros.area + log.total.seeds + (1|plot), data = clip, family = "binomial")

a5 <- anova(survival_no.int, survival_no.seeds, test="LRT") 
survival_LRT[5,] <- c("totalseeds", NA, NA) #model has weird errors
a6 <- anova(survival_no.int, survival_no.trt, test="LRT") 
survival_LRT[6,] <- c("trt", NA, NA) #model has weird errors
survival_LRT
```

```{r no.flowers}
no.flowers_LRT = data.frame(var = NA,
                        chi = NA, 
                        pvalue = NA)
#colnames(no.flowers_LRT) <- c("var", "chi", "p-value")

no.flowers_full <- glmer(no.flowersT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + log.ros.area:trt + log.ros.area:log.total.seeds:trt + (1|plot), data = clip, family = "poisson")
no.flowers_no3way <- glmer(no.flowersT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + log.ros.area:trt + (1|plot), data = clip, family = "poisson")
a1 <- anova(no.flowers_full, no.flowers_no3way, test="LRT") #LRT test - removing 3 way interaction does not significantly change model
no.flowers_LRT[1,] <- c("size:seeds:trt", a1[2,6], a1[2,8])


no.flowers_no.seed.trt <- glmer(no.flowersT1 ~ log.ros.area + log.total.seeds + trt + log.ros.area:log.total.seeds + log.ros.area:trt + (1|plot), data = clip, family = "poisson")
a2 <- anova(no.flowers_no3way, no.flowers_no.seed.trt, test="LRT") #LRT test - removing seed:trt interaction does not significantly change model
no.flowers_LRT[2,] <- c("seeds:trt", a2[2,6], a2[2,8])

no.flowers_no.size.seeds <- glmer(no.flowersT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:trt + (1|plot), data = clip, family = "poisson")
a3 <- anova(no.flowers_no3way, no.flowers_no.size.seeds, test="LRT") #LRT test - removing size:seed interaction does not significantly change model
no.flowers_LRT[3,] <- c("size:seed", a3[2,6], a3[2,8])


no.flowers_no.size.trt <- glmer(no.flowersT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + (1|plot), data = clip, family = "poisson")
a4 <- anova(no.flowers_no3way, no.flowers_no.size.trt, test="LRT") #LRT test - removing size:trt does not significantly change model
no.flowers_LRT[4,] <- c("size:trt", a4[2,6], a4[2,8])

no.flowers_no.int <- glmer(no.flowersT1 ~ log.ros.area + log.total.seeds + trt + (1|plot), data = clip, family = "poisson")
no.flowers_no.seeds <- glmer(no.flowersT1 ~ log.ros.area + trt + (1|plot), data = clip, family = "poisson")
no.flowers_no.trt <- glmer(no.flowersT1 ~ log.ros.area + log.total.seeds + (1|plot), data = clip, family = "poisson")

a5 <- anova(no.flowers_no.int, no.flowers_no.trt, test="LRT") #LRT test
no.flowers_LRT[5,] <- c("trt", a5[2,6], a5[2,8])
a6 <- anova(no.flowers_no.int, no.flowers_no.seeds, test="LRT") #LRT test
no.flowers_LRT[6,] <- c("totalseeds", a6[2,6], a6[2,8])
no.flowers_LRT
```

These LRT df's are in Table 1 in publication.`

