---
title: "primula_VR_model_selection"
author: "JL"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
## Primula vital rates with climate data

library(tidyverse)
library(AICcmodavg)
library(lme4)
#library(lmtest)
#library(effects)
library(wesanderson) # for colors
FF <- wes_palettes$FantasticFox1
Z <- wes_palettes$Zissou1
R <- wes_palettes$Royal2
I <- wes_palettes$IsleofDogs1
```

```{r sourcing data}
# Read in data ------------------------------------------------------------------------

### read in all years of Primula data and weather data from the Cowichan
# Add in climate data:
source("../scripts/Cowichan_climatevalues.R")

# Add in demography data:
source("../scripts/dode_allyears_cleaned.R")

## Join climate data to demography data by year
primula <- left_join(Dodecatheon, climate, by = "year") %>%
  #i solved these:
  # filter(tag!= "1881") %>% 
  # filter(tag!= "1471") %>% 
  # filter(tag!= "1183") %>% 
  # filter(tag!= "8317") %>% 
  # filter(tag!= "8311") %>% 
  # filter(tag!= "8315") %>% 
  mutate(pflower = as.factor(pflower),
         pflowerT1 = as.factor(pflowerT1),
         psurvivalT1 = as.factor(psurvivalT1))
#there's a problem with these tags that I don't want to deal with rn
## its some thing with the dormancy addition - not sure how to fix it just yet, so leaving it

remove(climate, Dodecatheon)
theme_set(theme_classic()) #for ggplot
```

```{r growth prelim figures}
# Growth Vital Rates ------------------------------------------------------
#####################################################################################################
primula %>% ggplot(aes(x = log.ros.area, y = log.ros.areaT1)) +
  geom_abline(intercept = 0, slope = 1, color = "grey")+
  geom_point() + 
  geom_smooth(method = "lm", se = F)+
  facet_wrap(~trt)
primula %>% ggplot(aes(x = log.ros.area, y = log.ros.areaT1)) +
  geom_abline(intercept = 0, slope = 1, color = "grey")+
  geom_point() + 
  geom_smooth(method = "lm", se = F)+
  facet_wrap(~year)
primula %>% ggplot(aes(x = log.ros.area, y = log.ros.areaT1)) +
  geom_abline(intercept = 0, slope = 1, color = "grey")+
  geom_point() + 
  geom_smooth(method = "lm", se = F)+
  facet_wrap(trt~pflower)
#ggsave("./Figures/vital rate yearly variation/growth.png", width = 5, height = 5)
boxplot(log(ros.area) ~ trt, data = primula)

##########################################################################################################
### Do vital rates differ between years? 
# Not sure if these are of any use? skip down to next section for model selection
gm1 <- lmer(log.ros.areaT1 ~ log.ros.area+(1|plot), data = primula)
gm2 <- lmer(log.ros.areaT1 ~ log.ros.area + year+(1|plot), data = primula)
gm3 <- lmer(log.ros.areaT1 ~ log.ros.area*year+(1|plot), data = primula)

anova(gm1, gm2 ,test="Chisq")
anova(gm2, gm3 ,test="Chisq")

# YES, growth does differ across years

### Do vital rates differ between treatments?

gm1 <- lmer(log.ros.areaT1 ~ log.ros.area +(1|plot) +(1|year), data = primula, REML = F)
gm2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + (1|plot) +(1|year), data = primula, REML = F)
gm3 <- lmer(log.ros.areaT1 ~ log.ros.area * trt + (1|plot) +(1|year), data = primula, REML = F)

anova(gm1, gm2 ,test="Chisq")
anova(gm2, gm3 ,test="Chisq")
summary(gm3)

#no, plants aren't different sized across treatments

# What does this tell us: yes there is a significant interaction between year and treatment (does the influence of treatment on growth varies across years?)
#############################################################################
# Does flowering in the previous year affect growth?

gm1 <- lmer(log.ros.areaT1 ~ log.ros.area + (1|plot) +(1|year), data = primula, REML = F)
gm2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower+ (1|plot) +(1|year), data = primula, REML = F)
gm3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower+ (1|plot) +(1|year), data = primula, REML = F)


anova(gm1, gm2 ,test="Chisq")
anova(gm2, gm3 ,test="Chisq")
summary(gm3
        )


summary(gm3)
#hmm! plants that flower previously are bigger (intercept) but grow more slowly than vegetative plants. Interesting!
# not sure what to do here
##########################################################################
##########################################################################
##########################################################################

#testing this backwards selection that I tried for the clipping analyses
growth.full<- lmerTest::lmer(log.ros.areaT1 ~ log.ros.area*trt*pflower +  grow.season.tot.precip + grow.season.mean.mean.temp + log.ros.area*grow.season.mean.mean.temp + log.ros.area*grow.season.tot.precip + grow.season.tot.precip*trt + grow.season.mean.mean.temp*trt + (1|plot) + (1|year), data = primula, REML= F)

drop1(growth.full)

step_fm <- lmerTest::step(growth.full)
step_fm # Display elimination results
final_fm <- get_model(step_fm)



```

There has to be a way to automate this, but I think there's not because technically this is a bad model selection approach (ie running all possible models and seeing what's best?). But I like this over a PCA, so oh well!

What climate variables to include:
Let's ditch lagged climate, and max/min temp - they are correlated, so i think better to pick the mean.
```{r growth candidate models}
# Candidate models
## sans climate
#gm.base <- lmer(log.ros.areaT1 ~ 1 + (1|plot) + (1|year), data = primula, REML = F)
gm.base.size <- lmer(log.ros.areaT1 ~ log.ros.area + (1|plot) + (1|year), data = primula, REML = F)
gm.base.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.base.trt.int <- lmer(log.ros.areaT1 ~ log.ros.area*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.base.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.base.cor.int <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.base.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.base.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.base.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.base.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*trt*pflower + (1|plot) + (1|year), data = primula, REML = F)
#the rest of the models below are just these + different climate variables + interactions
########################################################################################
##grow season total precip
gm.gs.precip <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.int <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.trt <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.tot.precip + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.tot.precip + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.tot.precip*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.tot.precip*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower* grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int3.1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower* grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)

gm.gs.precip.cor.trt.int4 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt +  grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int4.1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt*grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)

gm.gs.precip.cor.trt.int5 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*trt +  grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int5.1 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.tot.precip + pflower*trt  + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + trt* grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int6.1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt* grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)

gm.gs.precip.cor.trt.int7 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int8 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.tot.precip*pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int9 <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.tot.precip*pflower*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int10 <- lmer(log.ros.areaT1 ~ log.ros.area*trt*grow.season.tot.precip + pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int11 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*trt + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)


#deciding not to have any 3-way interactions here!
###
#grow season ave temp
gm.gs.av.temp <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.int <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.trt <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.mean.mean.temp + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.mean.mean.temp + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.mean.mean.temp*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.mean.mean.temp*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower* grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int3.1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower* grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)

gm.gs.av.temp.cor.trt.int4 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt +  grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int4.1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt*grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)

gm.gs.av.temp.cor.trt.int5 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*trt +  grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int5.1 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.mean.mean.temp + pflower*trt  + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + trt* grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int6.1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt* grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int7 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.mean.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int8 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.mean.mean.temp*pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int9 <- lmer(log.ros.areaT1 ~ log.ros.area+ grow.season.mean.mean.temp*pflower*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int10 <- lmer(log.ros.areaT1 ~ log.ros.area*trt*grow.season.mean.mean.temp + pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int11 <- lmer(log.ros.areaT1 ~ log.ros.area*trt*pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, REML = F)



#deciding not to have any 3-way interactions here!

#########################################################################################
##summer total precip
fm.summer.precip <- lmer(log.ros.areaT1 ~ log.ros.area + summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.int <- lmer(log.ros.areaT1 ~ log.ros.area*summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.trt <- lmer(log.ros.areaT1 ~ log.ros.area + summer.tot.precip + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.tot.precip + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + summer.tot.precip*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.tot.precip*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.cor.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.cor.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.cor.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)

gm.summer.precip.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower* summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.cor.trt.int4 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt +  summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.cor.trt.int5 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*trt +  summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + trt* summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.precip.cor.trt.int7 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
#deciding not to have any 3-way interactions here!
###
#summer ave temp
gm.summer.av.temp <- lmer(log.ros.areaT1 ~ log.ros.area + summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.int <- lmer(log.ros.areaT1 ~ log.ros.area*summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.trt <- lmer(log.ros.areaT1 ~ log.ros.area + summer.mean.temp + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.mean.temp + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + summer.mean.temp*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.mean.temp*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower* summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int4 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt +  summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int5 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*trt +  summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + trt* summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int7 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
#deciding not to have any 3-way interactions here!
###############################################################################
##winter total precip
gm.winter.precip <- lmer(log.ros.areaT1 ~ log.ros.area + winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.int <- lmer(log.ros.areaT1 ~ log.ros.area*winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.trt <- lmer(log.ros.areaT1 ~ log.ros.area + winter.tot.precip + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.tot.precip + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + winter.tot.precip*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.tot.precip*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.cor.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.cor.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.cor.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower* winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.cor.trt.int4 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt +  winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.cor.trt.int5 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*trt +  winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + trt* winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.precip.cor.trt.int7 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
#deciding not to have any 3-way interactions here!
###
#winter ave temp
gm.winter.av.temp <- lmer(log.ros.areaT1 ~ log.ros.area + winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.int <- lmer(log.ros.areaT1 ~ log.ros.area*winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.trt <- lmer(log.ros.areaT1 ~ log.ros.area + winter.mean.temp + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.mean.temp + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + winter.mean.temp*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.mean.temp*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower* winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int4 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt +  winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int5 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*trt +  winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + trt* winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int7 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
##deciding not to have any 3-way interactions here!
################################################################################
#Ok - here I'm just looking at growing season, summer, and winter climate of the current year
###
growth <- mget(ls(pattern = "^gm")) #make a list of all of those models that start with gm (^ means start with)
growth_AICc<-aictab(cand.set = growth, modnames = NULL,second.ord=TRUE,nobs=NULL,sort=TRUE)

#gm.gs.precip.cor.int3 is the best fit:
summary(gm.gs.precip.cor.int3)
#log.ros.areaT1 ~ log.ros.area + pflower + trt * summer.mean.temp +  (1 | plot) + (1 | year)

#rm(list = ls()[grepl("gm", ls())])
#gm17 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*grow.season.mean.max.temp+ (1|plot) + (1|year), data = primula, REML = F) ###

```
Figure for growth:
```{r}
#gm.gs.precip.cor.int3

pred.dat <-  expand.grid(log.ros.area = seq(min(primula$log.ros.area, na.rm = TRUE), max(primula$log.ros.area, na.rm = TRUE), by = .1), grow.season.tot.precip = seq(min(primula$grow.season.tot.precip), max(primula$grow.season.tot.precip), by = .01), pflower = c("0","1"))
pred.output <- predict(gm.gs.precip.cor.int3, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.output <- as.data.frame(pred.output)
pred.dat.output <- cbind(pred.dat, pred.output) %>% 
  rename(log.ros.areaT1 = pred.output)

label <- as_labeller(c("0" = "Vegetative in t", "1" = "Flowered in t"))

ggplot(subset(primula, !is.na(pflower)), aes(x = log.ros.area, y = log.ros.areaT1))+
  geom_point(alpha = 0.25)+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip == 63.6  & pflower == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = "lightblue2", size = 1, linetype = "dashed")+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip == 63.6  & pflower == 1), aes(x = log.ros.area, y = log.ros.areaT1), color = "lightblue2", size = 1)+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip == 155.8  & pflower == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = "dodgerblue", size = 1, linetype = "dashed")+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip == 155.8  & pflower == 1), aes(x = log.ros.area, y = log.ros.areaT1), color = "dodgerblue", size = 1)+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip == 311.6   & pflower == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = "blue2", size = 1, linetype = "dashed")+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip == 311.6   & pflower == 1), aes(x = log.ros.area, y = log.ros.areaT1), color = "blue2", size = 1)+
    geom_abline(slope=1, intercept = 0, linetype = 2, color= "grey", size = 1)+
    facet_wrap(~pflower, labeller = label)+
      scale_y_continuous(expand = c(0, 0), limits = c(0, 6))+
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+
  labs(x = "log(Rosette Area) in t", y = "log(Rosette Area) in t + 1")


#ggsave(plot = growth.fig, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/growth.png", width = 10, height = 6, dpi = 300)
## probably should have some bins here for all the dots...
```

```{r}
label <- as_labeller(c("0" = "Vegetative in t", "1" = "Flowered in t"))

growth.fig <- 
  ggplot(subset(primula, !is.na(pflower)), aes(x = log.ros.area, y = log.ros.areaT1, col = fct_rev(pflower)))+
  geom_abline(slope=1, intercept = 0, linetype = 2, color= "grey", size = 1)+
  geom_point(alpha = 0.25)+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip == 155.8  & pflower == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = "#7aa560", size = 1.5)+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip == 155.8  & pflower == 1), aes(x = log.ros.area, y = log.ros.areaT1), color = "#d983ff", size = 1.5)+

   # facet_wrap(~pflower, labeller = label)+
      scale_y_continuous(expand = c(0, 0), limits = c(0, 6))+
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+
  labs(x = "log(Rosette Area) in t", y = "log(Rosette Area) in t + 1")+
  scale_colour_manual(values = c("#d983ff", "#7aa560")) +
      theme(legend.position = "none")
growth.fig
#ggsave(plot = growth.fig, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/growth.fig.png", width =4, height = 4, dpi = 300)
## probably should have some bins here for all the dots...
```


###
```{r p(flower) testing }
# Probability of flowering  -------------------------------------------------------------

# ## why is N different for pflower?
# test_1702 <- primula %>% 
#   filter(!is.na(pflower),
#          !is.na(log.ros.area),
#          !is.na(pflowerT1))
# test_1703 <- primula %>% 
#   dplyr::filter(!is.na(log.ros.area),
#                 !is.na(pflowerT1))
# overlap <- anti_join(test_1703, test_1702)
# #tag 35 in 2019 did not an entry for pflower/no.flowers - was left blank. Hmm!
# # what to do here - took it out in the cleaning script for 2019

primula %>% filter(!is.na(pflowerT1)) %>% 
  ggplot(aes(x = log.ros.area, y = pflowerT1)) +
  geom_jitter() + 
  geom_smooth(method="glm", method.args=list(family="binomial"), se = F)+
  facet_wrap(~trt)
#ggsave("./Figures/vital rate yearly variation/pflower.png", width = 5, height = 5)

### Do vital rates differ between years?

fm1 <- glm(pflower ~ log(ros.areaTminus1), data = primula, family = "binomial")
fm2 <- glm(pflower ~ log(ros.areaTminus1) + year, data = primula, family = "binomial")
fm3 <- glm(pflower ~ log(ros.areaTminus1)*year, data = primula, family = "binomial")

lrtest(fm1, fm2)
lrtest(fm1, fm3)
# NO

### Do vital rates differ between treatments?

fm1 <- glm(pflower ~ log(ros.areaTminus1), data = primula, family = "binomial")
fm2 <- glm(pflower ~ log(ros.areaTminus1) + trt, data = primula, family = "binomial")
fm3 <- glm(pflower ~ log(ros.areaTminus1)*trt, data = primula, family = "binomial")

lrtest(fm1, fm2)
lrtest(fm1, fm3)

# YES 

# What does this tell us? The probability of flowering does not change across years, but it does change across treatment. However, treatment likely depends on year (some years are drier/wetter, so this will affect strength of treatments/how different they are?). How to test this: Make a model with both and test for a significant interaction? What does the extra water in 2021 mean for this (independent of how much it rained)

fm1 <- glm(pflower ~ log(ros.areaTminus1) + trt, data = primula, family = "binomial")
fm2 <- glm(pflower ~ log(ros.areaTminus1) + trt*year, data = primula, family = "binomial")
fm3 <- glm(pflower ~ log(ros.areaTminus1)*trt + year, data = primula, family = "binomial")

lrtest(fm1, fm2)
lrtest(fm1, fm3)

# What does this tell us: yes there is a significant interaction between year and treatment (read: the influence of treatment on pflower varies across years)
# Does flowering in the previous year affect flowering this year?

fm1 <- glm(pflowerT1 ~ log.ros.area, data = primula, family = "binomial")
fm2 <- glm(pflowerT1 ~ log.ros.area + pflower, data = primula, family = "binomial")
fm3 <- glm(pflowerT1 ~ log.ros.area+ trt, data = primula, family = "binomial")
fm4 <- glm(pflowerT1 ~ log.ros.area +trt + pflower, data = primula, family = "binomial")

lrtest(fm1, fm2, fm3, fm4)
summary(fm2)
rm(list = ls()[grepl("fm", ls())]) #remove these before the candidate sets

```

```{r pflower candidate models}
# Candidate models
## sans climate
#write a function, if model throws an error/warning, have it do this

#fm.base <- glmer(pflowerT1 ~ 1 + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.size <- glmer(pflowerT1 ~ log.ros.area + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.trt <- glmer(pflowerT1 ~ log.ros.area + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.trt.int <- glmer(pflowerT1 ~ log.ros.area*trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.cor.int <- glmer(pflowerT1 ~ log.ros.area*pflower + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*trt*pflower + (1|plot) + (1|year), data = primula, family = "binomial")
#the rest of the models below are just these + different climate variables + interactions
########################################################################################
##grow season total precip
fm.gs.precip <- glmer(pflowerT1 ~ log.ros.area + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.int <- glmer(pflowerT1 ~ log.ros.area*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.trt <- glmer(pflowerT1 ~ log.ros.area + grow.season.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*grow.season.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + grow.season.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*grow.season.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")

fm.gs.precip.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.int2 <- glmer(pflowerT1 ~ log.ros.area + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.int3 <- glmer(pflowerT1 ~ log.ros.area*pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")

fm.gs.precip.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int1.1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int2.1 <- glmer(pflowerT1 ~ log.ros.area*grow.season.tot.precip + trt*pflower + (1|plot) + (1|year), data = primula, family = "binomial")

fm.gs.precip.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area + trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int4 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt +  grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int5 <- glmer(pflowerT1 ~ log.ros.area + pflower*trt +  grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int6 <- glmer(pflowerT1 ~ log.ros.area + pflower + trt* grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int6.1 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt* grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int7 <- glmer(pflowerT1 ~ log.ros.area*grow.season.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")

fm.gs.precip.cor.trt.int8 <- glmer(pflowerT1 ~ log.ros.area*grow.season.tot.precip*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int9 <- glmer(pflowerT1 ~ log.ros.area + grow.season.tot.precip*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int10 <- glmer(pflowerT1 ~ log.ros.area*trt*grow.season.tot.precip + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int11 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower +grow.season.tot.precip+ (1|plot) + (1|year), data = primula, family = "binomial")
###
#grow season ave temp
fm.gs.av.temp <- glmer(pflowerT1 ~ log.ros.area + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.int <- glmer(pflowerT1 ~ log.ros.area*grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.trt <- glmer(pflowerT1 ~ log.ros.area + grow.season.mean.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*grow.season.mean.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + grow.season.mean.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*grow.season.mean.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.int2 <- glmer(pflowerT1 ~ log.ros.area + pflower*grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.int3 <- glmer(pflowerT1 ~ log.ros.area*pflower*grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int1.1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower*grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int2.1 <- glmer(pflowerT1 ~ log.ros.area*grow.season.mean.mean.temp + trt*pflower + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area + trt + pflower* grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int4 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt +  grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int5 <- glmer(pflowerT1 ~ log.ros.area + pflower*trt +  grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int6 <- glmer(pflowerT1 ~ log.ros.area + pflower + trt* grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int6.1 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt* grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int7 <- glmer(pflowerT1 ~ log.ros.area*grow.season.mean.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")

fm.gs.av.temp.cor.trt.int8 <- glmer(pflowerT1 ~ log.ros.area*grow.season.mean.mean.temp*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int9 <- glmer(pflowerT1 ~ log.ros.area+ grow.season.mean.mean.temp*pflower*trt+ (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int10 <- glmer(pflowerT1 ~ log.ros.area*trt*grow.season.mean.mean.temp + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int11 <- glmer(pflowerT1 ~ log.ros.area*trt*pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

# #########################################################################################
# ##summer total precip
# fm.summer.precip <- glmer(pflowerT1 ~ log.ros.area + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.int <- glmer(pflowerT1 ~ log.ros.area*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.trt <- glmer(pflowerT1 ~ log.ros.area + summer.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*summer.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + summer.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*summer.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.int2 <- glmer(pflowerT1 ~ log.ros.area + pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.int3 <- glmer(pflowerT1 ~ log.ros.area*pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area + trt + pflower* summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int4 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt +  summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int5 <- glmer(pflowerT1 ~ log.ros.area + pflower*trt +  summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int6 <- glmer(pflowerT1 ~ log.ros.area + pflower + trt* summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int7 <- glmer(pflowerT1 ~ log.ros.area*summer.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# #deciding not to have any 3-way interactions here!
# ###
# #summer ave temp
# fm.summer.av.temp <- glmer(pflowerT1 ~ log.ros.area + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.int <- glmer(pflowerT1 ~ log.ros.area*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.trt <- glmer(pflowerT1 ~ log.ros.area + summer.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*summer.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + summer.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*summer.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.int2 <- glmer(pflowerT1 ~ log.ros.area + pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.int3 <- glmer(pflowerT1 ~ log.ros.area*pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area + trt + pflower* summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int4 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt +  summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int5 <- glmer(pflowerT1 ~ log.ros.area + pflower*trt +  summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int6 <- glmer(pflowerT1 ~ log.ros.area + pflower + trt* summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int7 <- glmer(pflowerT1 ~ log.ros.area*summer.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# #deciding not to have any 3-way interactions here!
# ###############################################################################
# ##winter total precip
# fm.winter.precip <- glmer(pflowerT1 ~ log.ros.area + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.int <- glmer(pflowerT1 ~ log.ros.area*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.trt <- glmer(pflowerT1 ~ log.ros.area + winter.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*winter.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + winter.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*winter.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.int2 <- glmer(pflowerT1 ~ log.ros.area + pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.int3 <- glmer(pflowerT1 ~ log.ros.area*pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area + trt + pflower* winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int4 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt +  winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int5 <- glmer(pflowerT1 ~ log.ros.area + pflower*trt +  winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int6 <- glmer(pflowerT1 ~ log.ros.area + pflower + trt* winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int7 <- glmer(pflowerT1 ~ log.ros.area*winter.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# #deciding not to have any 3-way interactions here!
# ###
# #winter ave temp
# fm.winter.av.temp <- glmer(pflowerT1 ~ log.ros.area + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.int <- glmer(pflowerT1 ~ log.ros.area*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.trt <- glmer(pflowerT1 ~ log.ros.area + winter.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*winter.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + winter.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*winter.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.cor.int2 <- glmer(pflowerT1 ~ log.ros.area + pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.cor.int3 <- glmer(pflowerT1 ~ log.ros.area*pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area + trt + pflower* winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.cor.trt.int4 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt +  winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.cor.trt.int5 <- glmer(pflowerT1 ~ log.ros.area + pflower*trt +  winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.cor.trt.int6 <- glmer(pflowerT1 ~ log.ros.area + pflower + trt* winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.av.temp.cor.trt.int7 <- glmer(pflowerT1 ~ log.ros.area*winter.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# #deciding not to have any 3-way interactions here!
################################################################################
#Ok - here I'm just looking at growing season, summer, and winter climate of the current year
###

#to do: 
#is this has something, don't include it in the list!
#fm.gs.precip.cor.int3@optinfo$conv$lme4$messages #this is !NULL, which means it did not converge
#
#fm.winter.av.temp.cor.trt.int7@optinfo$conv$lme4$messages #if NULL, then it converges! this is a model that converges



flowering <- mget(ls(pattern = "^fm")) #make a list of all of those models that start with gm (^ means start with)
#now how to get the thing above to work here (ie if you show NULL, include it!!)

# flowering <- flowering %>%  purrr::list_modify("fm.f4" = NULL) %>%  purrr::list_modify("fm11lag" = NULL) %>%  purrr::list_modify("fm.9" = NULL) %>%  
#   purrr::list_modify("fm.f14" = NULL) %>% purrr::list_modify("fm.f12" = NULL) %>% purrr::list_modify("fm.f15" = NULL)  %>% purrr::list_modify("fm17" = NULL) %>% 
#   purrr::list_modify("fm18" = NULL) %>% purrr::list_modify("fm.25" = NULL) %>% purrr::list_modify("fm2" = NULL) %>% purrr::list_modify("fm30" = NULL)# these didnt converge and have low delta AIC's
flowering_AICc<-aictab(cand.set = flowering, modnames = NULL,second.ord=TRUE,nobs=NULL,sort=TRUE)
summary(fm.base.cor.int
)
```



of the base models, fm.base.cor.int is the best (size*pflower interaction) - this is good! But the rest of the models are having problems converging
```{r}
#fm.base.cor.int
pred.dat <-  expand.grid(log.ros.area = seq(min(primula$log.ros.area, na.rm = TRUE), max(primula$log.ros.area, na.rm = TRUE), by = .1), pflower = c("0","1"))
pred.output <- predict(fm.base.cor.int, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.output <- as.data.frame(pred.output)
pred.dat.output <- cbind(pred.dat, pred.output) %>% 
  rename(pflowerT1 = pred.output) 


ggplot(
  subset(primula,!is.na(pflowerT1) &
           !is.na(pflower)),
  aes(
    x = log.ros.area,
    y = pflowerT1,
    color = as.factor(pflower)
  )
) +
  geom_jitter(height = .15, alpha = 0.5) +
  scale_color_manual(values = c("lightsteelblue3", "grey0")) +
  geom_line(
    data = subset(pred.dat.output, pflower == "0"),
    aes(x = log.ros.area, y = pflowerT1),
    linetype = "dashed"
  ) +
  geom_line(data = subset(pred.dat.output, pflower == "1"),
            aes(x = log.ros.area, y = pflowerT1)) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6)) +
  labs(x = "log(Rosette Area) in t", y = "Probability of Flowering in t + 1") +
  theme(legend.position = "none")
pflower.fig

#ggsave(plot = pflower.fig, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/pflower.png", width = 6, height = 6, dpi = 300)
```

```{r}
pflower.fig <- 
  primula %>%
  filter(!is.na(pflowerT1) &
           !is.na(pflower)) %>%
  ggplot(aes(col = fct_rev(pflower))) +
  geom_jitter(aes(x = log.ros.area, y = as.numeric(pflowerT1) - 1),
              width = .1, height = 0.15,
              alpha = 0.2) +
  geom_line(aes(x = log.ros.area, y = as.numeric(pflowerT1),
                ),
            data = pred.dat.output, linewidth = 1.5) + 
  scale_colour_manual(values = c("#d983ff", "#7aa560")) +
  labs(col = NULL,
       lty = NULL,
       x = "log(Rosette Area) in t", y = "Probability of Flowering in t + 1")+
  scale_y_continuous(breaks = c(0,1))+
    theme(legend.position = "none")


pflower.fig

#ggsave(plot = pflower.fig, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/pflower.fig.png", width = 5, height = 5, dpi = 300)
```

#survival:
```{r pflower candidate models}
# Candidate models
## sans climate
#write a function, if model throws an error/warning, have it do this

#sm.base <- glmer(psurvivalT1 ~ 1 + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.size <- glmer(psurvivalT1 ~ log.ros.area + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.trt.int <- glmer(psurvivalT1 ~ log.ros.area*trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.cor.int <- glmer(psurvivalT1 ~ log.ros.area*pflower + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*trt*pflower + (1|plot) + (1|year), data = primula, family = "binomial")
#the rest of the models below are just these + different climate variables + interactions
########################################################################################
##grow season total precip
sm.gs.precip <- glmer(psurvivalT1 ~ log.ros.area + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.int <- glmer(psurvivalT1 ~ log.ros.area*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.trt <- glmer(psurvivalT1 ~ log.ros.area + grow.season.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + grow.season.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")

sm.gs.precip.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.int1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.int2 <- glmer(psurvivalT1 ~ log.ros.area + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.int3 <- glmer(psurvivalT1 ~ log.ros.area*pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")

sm.gs.precip.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int1.1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int2.1 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.tot.precip + trt*pflower + (1|plot) + (1|year), data = primula, family = "binomial")

sm.gs.precip.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int4 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt +  grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int5 <- glmer(psurvivalT1 ~ log.ros.area + pflower*trt +  grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int6 <- glmer(psurvivalT1 ~ log.ros.area + pflower + trt* grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int6.1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt* grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int7 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")

sm.gs.precip.cor.trt.int8 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.tot.precip*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int9 <- glmer(psurvivalT1 ~ log.ros.area + grow.season.tot.precip*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int10 <- glmer(psurvivalT1 ~ log.ros.area*trt*grow.season.tot.precip + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int11 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower +grow.season.tot.precip+ (1|plot) + (1|year), data = primula, family = "binomial")
###
#grow season ave temp
sm.gs.av.temp <- glmer(psurvivalT1 ~ log.ros.area + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.int <- glmer(psurvivalT1 ~ log.ros.area*grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.trt <- glmer(psurvivalT1 ~ log.ros.area + grow.season.mean.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.mean.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + grow.season.mean.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.mean.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.int1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.int2 <- glmer(psurvivalT1 ~ log.ros.area + pflower*grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.int3 <- glmer(psurvivalT1 ~ log.ros.area*pflower*grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int1.1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower*grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int2.1 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.mean.mean.temp + trt*pflower + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower* grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int4 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt +  grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int5 <- glmer(psurvivalT1 ~ log.ros.area + pflower*trt +  grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int6 <- glmer(psurvivalT1 ~ log.ros.area + pflower + trt* grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int6.1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt* grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int7 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.mean.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")

sm.gs.av.temp.cor.trt.int8 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.mean.mean.temp*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int9 <- glmer(psurvivalT1 ~ log.ros.area+ grow.season.mean.mean.temp*pflower*trt+ (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int10 <- glmer(psurvivalT1 ~ log.ros.area*trt*grow.season.mean.mean.temp + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int11 <- glmer(psurvivalT1 ~ log.ros.area*trt*pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

# #########################################################################################
# ##summer total precip
# sm.summer.precip <- glmer(psurvivalT1 ~ log.ros.area + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.int <- glmer(psurvivalT1 ~ log.ros.area*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.trt <- glmer(psurvivalT1 ~ log.ros.area + summer.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*summer.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + summer.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*summer.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.int1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.int2 <- glmer(psurvivalT1 ~ log.ros.area + pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.int3 <- glmer(psurvivalT1 ~ log.ros.area*pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower* summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int4 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt +  summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int5 <- glmer(psurvivalT1 ~ log.ros.area + pflower*trt +  summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int6 <- glmer(psurvivalT1 ~ log.ros.area + pflower + trt* summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int7 <- glmer(psurvivalT1 ~ log.ros.area*summer.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# #deciding not to have any 3-way interactions here!
# ###
# #summer ave temp
# sm.summer.av.temp <- glmer(psurvivalT1 ~ log.ros.area + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.int <- glmer(psurvivalT1 ~ log.ros.area*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.trt <- glmer(psurvivalT1 ~ log.ros.area + summer.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*summer.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + summer.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*summer.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.cor.int1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.cor.int2 <- glmer(psurvivalT1 ~ log.ros.area + pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.cor.int3 <- glmer(psurvivalT1 ~ log.ros.area*pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower* summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.cor.trt.int4 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt +  summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.cor.trt.int5 <- glmer(psurvivalT1 ~ log.ros.area + pflower*trt +  summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.cor.trt.int6 <- glmer(psurvivalT1 ~ log.ros.area + pflower + trt* summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.av.temp.cor.trt.int7 <- glmer(psurvivalT1 ~ log.ros.area*summer.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# #deciding not to have any 3-way interactions here!
# ###############################################################################
# ##winter total precip
# sm.winter.precip <- glmer(psurvivalT1 ~ log.ros.area + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.int <- glmer(psurvivalT1 ~ log.ros.area*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.trt <- glmer(psurvivalT1 ~ log.ros.area + winter.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*winter.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + winter.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*winter.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.int1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.int2 <- glmer(psurvivalT1 ~ log.ros.area + pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.int3 <- glmer(psurvivalT1 ~ log.ros.area*pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower* winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int4 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt +  winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int5 <- glmer(psurvivalT1 ~ log.ros.area + pflower*trt +  winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int6 <- glmer(psurvivalT1 ~ log.ros.area + pflower + trt* winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int7 <- glmer(psurvivalT1 ~ log.ros.area*winter.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# #deciding not to have any 3-way interactions here!
# ###
# #winter ave temp
# sm.winter.av.temp <- glmer(psurvivalT1 ~ log.ros.area + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.int <- glmer(psurvivalT1 ~ log.ros.area*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.trt <- glmer(psurvivalT1 ~ log.ros.area + winter.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*winter.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + winter.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*winter.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.cor.int1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.cor.int2 <- glmer(psurvivalT1 ~ log.ros.area + pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.cor.int3 <- glmer(psurvivalT1 ~ log.ros.area*pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower* winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.cor.trt.int4 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt +  winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.cor.trt.int5 <- glmer(psurvivalT1 ~ log.ros.area + pflower*trt +  winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.cor.trt.int6 <- glmer(psurvivalT1 ~ log.ros.area + pflower + trt* winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.av.temp.cor.trt.int7 <- glmer(psurvivalT1 ~ log.ros.area*winter.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# #deciding not to have any 3-way interactions here!
################################################################################
#Ok - here I'm just looking at growing season, summer, and winter climate of the current year
###

#to do: 
#is this has something, don't include it in the list!
#sm.gs.precip.cor.int3@optinfo$conv$lme4$messages #this is !NULL, which means it did not converge
#
#sm.winter.av.temp.cor.trt.int7@optinfo$conv$lme4$messages #if NULL, then it converges! this is a model that converges



survival <- mget(ls(pattern = "^sm")) #make a list of all of those models that start with gm (^ means start with)
#now how to get the thing above to work here (ie if you show NULL, include it!!)

# flowering <- flowering %>%  purrr::list_modify("sm.f4" = NULL) %>%  purrr::list_modify("sm11lag" = NULL) %>%  purrr::list_modify("sm.9" = NULL) %>%  
#   purrr::list_modify("sm.f14" = NULL) %>% purrr::list_modify("sm.f12" = NULL) %>% purrr::list_modify("sm.f15" = NULL)  %>% purrr::list_modify("sm17" = NULL) %>% 
#   purrr::list_modify("sm18" = NULL) %>% purrr::list_modify("sm.25" = NULL) %>% purrr::list_modify("sm2" = NULL) %>% purrr::list_modify("sm30" = NULL)# these didnt converge and have low delta AIC's
survival_AICc<-aictab(cand.set = survival, modnames = NULL,second.ord=TRUE,nobs=NULL,sort=TRUE)
summary(	
sm.gs.av.temp
)
```
#no flowers
```{r}

noflowers.base <- glmer(flow.sum ~ 1 + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.base.size <- glmer(flow.sum ~ log.ros.area + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.base.trt <- glmer(flow.sum ~ log.ros.area + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.base.trt.int <- glmer(flow.sum ~ log.ros.area*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.base.cor <- glmer(flow.sum ~ log.ros.area + pflower + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.base.cor.int <- glmer(flow.sum ~ log.ros.area*pflower + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.base.cor.trt <- glmer(flow.sum ~ log.ros.area + trt + pflower + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.base.cor.trt.int1 <- glmer(flow.sum ~ log.ros.area*trt + pflower + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.base.cor.trt.int2 <- glmer(flow.sum ~ log.ros.area + trt*pflower + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.base.cor.trt.int3 <- glmer(flow.sum ~ log.ros.area*trt*pflower + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
#the rest of the models below are just these + different climate variables + interactions
########################################################################################
##grow season total precip
noflowers.gs.precip <- glmer(flow.sum ~ log.ros.area + grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.int <- glmer(flow.sum ~ log.ros.area*grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.trt <- glmer(flow.sum ~ log.ros.area + grow.season.tot.precip + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.trt.int1 <- glmer(flow.sum ~ log.ros.area*grow.season.tot.precip + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.trt.int2 <- glmer(flow.sum ~ log.ros.area + grow.season.tot.precip*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.trt.int3 <- glmer(flow.sum ~ log.ros.area*grow.season.tot.precip*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")

noflowers.gs.precip.cor <- glmer(flow.sum ~ log.ros.area + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.int1 <- glmer(flow.sum ~ log.ros.area*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.int2 <- glmer(flow.sum ~ log.ros.area + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.int3 <- glmer(flow.sum ~ log.ros.area*pflower*grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")

noflowers.gs.precip.cor.trt <- glmer(flow.sum ~ log.ros.area + trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int1 <- glmer(flow.sum ~ log.ros.area*trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int1.1 <- glmer(flow.sum ~ log.ros.area*trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int2 <- glmer(flow.sum ~ log.ros.area + trt*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int2.1 <- glmer(flow.sum ~ log.ros.area*grow.season.tot.precip + trt*pflower + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")

noflowers.gs.precip.cor.trt.int3 <- glmer(flow.sum ~ log.ros.area + trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int4 <- glmer(flow.sum ~ log.ros.area*pflower + trt +  grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int5 <- glmer(flow.sum ~ log.ros.area + pflower*trt +  grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int6 <- glmer(flow.sum ~ log.ros.area + pflower + trt* grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int6.1 <- glmer(flow.sum ~ log.ros.area*pflower + trt* grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int7 <- glmer(flow.sum ~ log.ros.area*grow.season.tot.precip + pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")

noflowers.gs.precip.cor.trt.int8 <- glmer(flow.sum ~ log.ros.area*grow.season.tot.precip*pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int9 <- glmer(flow.sum ~ log.ros.area + grow.season.tot.precip*pflower*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int10 <- glmer(flow.sum ~ log.ros.area*trt*grow.season.tot.precip + pflower + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int11 <- glmer(flow.sum ~ log.ros.area*trt + pflower +grow.season.tot.precip+ (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
###
#grow season ave temp
noflowers.gs.av.temp <- glmer(flow.sum ~ log.ros.area + grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.int <- glmer(flow.sum ~ log.ros.area*grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.trt <- glmer(flow.sum ~ log.ros.area + grow.season.mean.mean.temp + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.trt.int1 <- glmer(flow.sum ~ log.ros.area*grow.season.mean.mean.temp + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.trt.int2 <- glmer(flow.sum ~ log.ros.area + grow.season.mean.mean.temp*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.trt.int3 <- glmer(flow.sum ~ log.ros.area*grow.season.mean.mean.temp*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor <- glmer(flow.sum ~ log.ros.area + pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.int1 <- glmer(flow.sum ~ log.ros.area*pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.int2 <- glmer(flow.sum ~ log.ros.area + pflower*grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.int3 <- glmer(flow.sum ~ log.ros.area*pflower*grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt <- glmer(flow.sum ~ log.ros.area + trt + pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int1 <- glmer(flow.sum ~ log.ros.area*trt + pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int1.1 <- glmer(flow.sum ~ log.ros.area*trt + pflower*grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int2 <- glmer(flow.sum ~ log.ros.area + trt*pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int2.1 <- glmer(flow.sum ~ log.ros.area*grow.season.mean.mean.temp + trt*pflower + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int3 <- glmer(flow.sum ~ log.ros.area + trt + pflower* grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int4 <- glmer(flow.sum ~ log.ros.area*pflower + trt +  grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int5 <- glmer(flow.sum ~ log.ros.area + pflower*trt +  grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int6 <- glmer(flow.sum ~ log.ros.area + pflower + trt* grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int6.1 <- glmer(flow.sum ~ log.ros.area*pflower + trt* grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int7 <- glmer(flow.sum ~ log.ros.area*grow.season.mean.mean.temp + pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")

noflowers.gs.av.temp.cor.trt.int8 <- glmer(flow.sum ~ log.ros.area*grow.season.mean.mean.temp*pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int9 <- glmer(flow.sum ~ log.ros.area+ grow.season.mean.mean.temp*pflower*trt+ (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int10 <- glmer(flow.sum ~ log.ros.area*trt*grow.season.mean.mean.temp + pflower + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int11 <- glmer(flow.sum ~ log.ros.area*trt*pflower + grow.season.mean.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")

# #########################################################################################
# ##summer total precip
# noflowers.summer.precip <- glmer(flow.sum ~ log.ros.area + summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.int <- glmer(flow.sum ~ log.ros.area*summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.trt <- glmer(flow.sum ~ log.ros.area + summer.tot.precip + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.trt.int1 <- glmer(flow.sum ~ log.ros.area*summer.tot.precip + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.trt.int2 <- glmer(flow.sum ~ log.ros.area + summer.tot.precip*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.trt.int3 <- glmer(flow.sum ~ log.ros.area*summer.tot.precip*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.cor <- glmer(flow.sum ~ log.ros.area + pflower + summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.cor.int1 <- glmer(flow.sum ~ log.ros.area*pflower + summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.cor.int2 <- glmer(flow.sum ~ log.ros.area + pflower*summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.cor.int3 <- glmer(flow.sum ~ log.ros.area*pflower*summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.cor.trt <- glmer(flow.sum ~ log.ros.area + trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int1 <- glmer(flow.sum ~ log.ros.area*trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int2 <- glmer(flow.sum ~ log.ros.area + trt*pflower + summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int3 <- glmer(flow.sum ~ log.ros.area + trt + pflower* summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int4 <- glmer(flow.sum ~ log.ros.area*pflower + trt +  summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int5 <- glmer(flow.sum ~ log.ros.area + pflower*trt +  summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int6 <- glmer(flow.sum ~ log.ros.area + pflower + trt* summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int7 <- glmer(flow.sum ~ log.ros.area*summer.tot.precip + pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# #deciding not to have any 3-way interactions here!
# ###
# #summer ave temp
# noflowers.summer.av.temp <- glmer(flow.sum ~ log.ros.area + summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.int <- glmer(flow.sum ~ log.ros.area*summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.trt <- glmer(flow.sum ~ log.ros.area + summer.mean.temp + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.trt.int1 <- glmer(flow.sum ~ log.ros.area*summer.mean.temp + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.trt.int2 <- glmer(flow.sum ~ log.ros.area + summer.mean.temp*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.trt.int3 <- glmer(flow.sum ~ log.ros.area*summer.mean.temp*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.cor <- glmer(flow.sum ~ log.ros.area + pflower + summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.cor.int1 <- glmer(flow.sum ~ log.ros.area*pflower + summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.cor.int2 <- glmer(flow.sum ~ log.ros.area + pflower*summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.cor.int3 <- glmer(flow.sum ~ log.ros.area*pflower*summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.cor.trt <- glmer(flow.sum ~ log.ros.area + trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.cor.trt.int1 <- glmer(flow.sum ~ log.ros.area*trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.cor.trt.int2 <- glmer(flow.sum ~ log.ros.area + trt*pflower + summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.cor.trt.int3 <- glmer(flow.sum ~ log.ros.area + trt + pflower* summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.cor.trt.int4 <- glmer(flow.sum ~ log.ros.area*pflower + trt +  summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.cor.trt.int5 <- glmer(flow.sum ~ log.ros.area + pflower*trt +  summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.cor.trt.int6 <- glmer(flow.sum ~ log.ros.area + pflower + trt* summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.summer.av.temp.cor.trt.int7 <- glmer(flow.sum ~ log.ros.area*summer.mean.temp + pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# #deciding not to have any 3-way interactions here!
# ###############################################################################
# ##winter total precip
# noflowers.winter.precip <- glmer(flow.sum ~ log.ros.area + winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.int <- glmer(flow.sum ~ log.ros.area*winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.trt <- glmer(flow.sum ~ log.ros.area + winter.tot.precip + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.trt.int1 <- glmer(flow.sum ~ log.ros.area*winter.tot.precip + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.trt.int2 <- glmer(flow.sum ~ log.ros.area + winter.tot.precip*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.trt.int3 <- glmer(flow.sum ~ log.ros.area*winter.tot.precip*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.cor <- glmer(flow.sum ~ log.ros.area + pflower + winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.cor.int1 <- glmer(flow.sum ~ log.ros.area*pflower + winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.cor.int2 <- glmer(flow.sum ~ log.ros.area + pflower*winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.cor.int3 <- glmer(flow.sum ~ log.ros.area*pflower*winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.cor.trt <- glmer(flow.sum ~ log.ros.area + trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int1 <- glmer(flow.sum ~ log.ros.area*trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int2 <- glmer(flow.sum ~ log.ros.area + trt*pflower + winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int3 <- glmer(flow.sum ~ log.ros.area + trt + pflower* winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int4 <- glmer(flow.sum ~ log.ros.area*pflower + trt +  winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int5 <- glmer(flow.sum ~ log.ros.area + pflower*trt +  winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int6 <- glmer(flow.sum ~ log.ros.area + pflower + trt* winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int7 <- glmer(flow.sum ~ log.ros.area*winter.tot.precip + pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# #deciding not to have any 3-way interactions here!
# ###
# #winter ave temp
# noflowers.winter.av.temp <- glmer(flow.sum ~ log.ros.area + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.int <- glmer(flow.sum ~ log.ros.area*winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.trt <- glmer(flow.sum ~ log.ros.area + winter.mean.temp + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.trt.int1 <- glmer(flow.sum ~ log.ros.area*winter.mean.temp + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.trt.int2 <- glmer(flow.sum ~ log.ros.area + winter.mean.temp*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.trt.int3 <- glmer(flow.sum ~ log.ros.area*winter.mean.temp*trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.cor <- glmer(flow.sum ~ log.ros.area + pflower + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.cor.int1 <- glmer(flow.sum ~ log.ros.area*pflower + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.cor.int2 <- glmer(flow.sum ~ log.ros.area + pflower*winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.cor.int3 <- glmer(flow.sum ~ log.ros.area*pflower*winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.cor.trt <- glmer(flow.sum ~ log.ros.area + trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.cor.trt.int1 <- glmer(flow.sum ~ log.ros.area*trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.cor.trt.int2 <- glmer(flow.sum ~ log.ros.area + trt*pflower + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.cor.trt.int3 <- glmer(flow.sum ~ log.ros.area + trt + pflower* winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.cor.trt.int4 <- glmer(flow.sum ~ log.ros.area*pflower + trt +  winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.cor.trt.int5 <- glmer(flow.sum ~ log.ros.area + pflower*trt +  winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.cor.trt.int6 <- glmer(flow.sum ~ log.ros.area + pflower + trt* winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# noflowers.winter.av.temp.cor.trt.int7 <- glmer(flow.sum ~ log.ros.area*winter.mean.temp + pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sum > 0), family = "poisson")
# #deciding not to have any 3-way interactions here!
################################################################################
#Ok - here I'm just looking at growing season, summer, and winter climate of the current year
###

#to do: 
#is this has something, don't include it in the list!
#noflowers.gs.precip.cor.int3@optinfo$conv$lme4$messages #this is !NULL, which means it did not converge
#
#noflowers.winter.av.temp.cor.trt.int7@optinfo$conv$lme4$messages #if NULL, then it converges! this is a model that converges



poisson <- mget(ls(pattern = "^noflowers")) #make a list of all of those models that start with gm (^ means start with)
#now how to get the thing above to work here (ie if you show NULL, include it!!)

# flowering <- flowering %>%  purrr::list_modify("noflowers.f4" = NULL) %>%  purrr::list_modify("noflowers11lag" = NULL) %>%  purrr::list_modify("noflowers.9" = NULL) %>%  
#   purrr::list_modify("noflowers.f14" = NULL) %>% purrr::list_modify("noflowers.f12" = NULL) %>% purrr::list_modify("noflowers.f15" = NULL)  %>% purrr::list_modify("noflowers17" = NULL) %>% 
#   purrr::list_modify("noflowers18" = NULL) %>% purrr::list_modify("noflowers.25" = NULL) %>% purrr::list_modify("noflowers2" = NULL) %>% purrr::list_modify("noflowers30" = NULL)# these didnt converge and have low delta AIC's
poisson_AICc<-aictab(cand.set = poisson, modnames = NULL,second.ord=TRUE,nobs=NULL,sort=TRUE)
summary(	
noflowers.base.cor.int

)











```

