---
title: "primula_VR_model_selection"
author: "JL"
date: "`r Sys.Date()`"
output: html_document
---


```{r packages}
## Primula vital rates with climate data

library(tidyverse)
library(AICcmodavg)
library(lme4)
#library(lmtest)
#library(effects)
library(wesanderson) # for colors
library(patchwork)
FF <- wes_palettes$FantasticFox1
Z <- wes_palettes$Zissou1
R <- wes_palettes$Royal2
I <- wes_palettes$IsleofDogs1
theme_set(theme_classic()) #for ggplot
```

Standardizing predictor variables:
- The convention that you standardize predictions primarily exists so that the units of the regression coefficients are the same.
- Standardizing consists in subtracting the mean and dividing by the standard deviation
-  What it changes is the correlation between main effects and their interactions (which seemed to be a problem previously)


```{r sourcing data}
# Read in data ------------------------------------------------------------------------

### read in all years of Primula data and weather data from the Cowichan
# Add in climate data:
climate_scale <- read.csv("C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/data_for_publication/CGOP_climatevalues_scaled.csv")

# Add in demography data:
primula <- read.csv("C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/data_for_publication/Primula_Demography_Data_2016to2023.csv")

## Join climate data to demography data by year
primula <- left_join(primula, climate_scale, by = "year") %>%
  mutate(pflower = as.factor(pflower),
         pflowerT1 = as.factor(pflowerT1),
         psurvivalT1 = as.factor(psurvivalT1))

remove(climate_scale)

# table(primula$pflower) #example to get sample sizes
# table(primula$trt) #example to get sample sizes
# table(primula$year) #example to get sample sizes
# table(primula$plot) #example to get sample sizes
```

```{r growth prelim figures}
# Growth Vital Rates ------------------------------------------------------
#####################################################################################################
primula %>% ggplot(aes(x = log.ros.area, y = log.ros.areaT1)) +
  geom_abline(intercept = 0, slope = 1, color = "grey")+
  geom_point() + 
  geom_smooth(method = "lm", se = F)+
  facet_wrap(~trt)
primula %>% ggplot(aes(x = log.ros.area, y = log.ros.areaT1)) +
  geom_abline(intercept = 0, slope = 1, color = "grey")+
  geom_point() + 
  geom_smooth(method = "lm", se = F)+
  facet_wrap(~year)
#ggsave("./Figures/vital rate yearly variation/growth.png", width = 5, height = 5)
primula %>% ggplot(aes(x = log.ros.area, y = log.ros.areaT1)) +
  geom_abline(intercept = 0, slope = 1, color = "grey")+
  geom_point() + 
  geom_smooth(method = "lm", se = F)+
  facet_wrap(trt~year)

boxplot(log(ros.area) ~ trt, data = primula)

##########################################################################################################
### Do vital rates differ between years? 
# Not sure if these are of any use? skip down to next section for model selection
gm1 <- lmer(log.ros.areaT1 ~ log.ros.area+(1|plot), data = primula)
gm2 <- lmer(log.ros.areaT1 ~ log.ros.area + year+(1|plot), data = primula)
gm3 <- lmer(log.ros.areaT1 ~ log.ros.area*year+(1|plot), data = primula)

anova(gm1, gm2 ,test="Chisq")
anova(gm2, gm3 ,test="Chisq")

# YES, growth does differ across years
#). We then tested for correlations between year random effects and each of the climate variables: mean daily precipitation, mean daily temperature, and proportion wet days across each season (spring, summer, fall, winter) and across one transition year (May 16, year t – May 15 year t+1). 




### Do vital rates differ between treatments?

gm1 <- lmer(log.ros.areaT1 ~ log.ros.area +(1|plot) +(1|year), data = primula, REML = F)
gm2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + (1|plot) +(1|year), data = primula, REML = F)
gm3 <- lmer(log.ros.areaT1 ~ log.ros.area * trt + (1|plot) +(1|year), data = primula, REML = F)

anova(gm1, gm2 ,test="Chisq")
anova(gm2, gm3 ,test="Chisq")
summary(gm3)

#no, plants aren't different sized across treatments

# What does this tell us: yes there is a significant interaction between year and treatment (does the influence of treatment on growth varies across years?)
#############################################################################
# Does flowering in the previous year affect growth?

gm1 <- lmer(log.ros.areaT1 ~ log.ros.area + (1|plot) +(1|year), data = primula, REML = F)
gm2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower+ (1|plot) +(1|year), data = primula, REML = F)
gm3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower+ (1|plot) +(1|year), data = primula, REML = F)


anova(gm1, gm2 ,test="Chisq")
anova(gm2, gm3 ,test="Chisq")
summary(gm3
        )


summary(gm3)
#hmm! plants that flower previously are bigger (intercept) but grow more slowly than vegetative plants. Interesting!
# not sure what to do here
##########################################################################
##########################################################################
##########################################################################

#testing this backwards selection that I tried for the clipping analyses
growth.full<- lmerTest::lmer(log.ros.areaT1 ~ log.ros.area*trt*pflower +  grow.season.tot.precip.scale + grow.season.mean.temp.scale + log.ros.area*grow.season.mean.temp.scale + log.ros.area*grow.season.tot.precip.scale + grow.season.tot.precip.scale*trt + grow.season.mean.temp.scale*trt + log.ros.area*grow.season.tot.precip.scale*trt + (1|plot) + (1|year), data = primula, REML= F)

drop1(growth.full)

step_fm <- lmerTest::step(growth.full)
step_fm # Display elimination results
final_fm <- get_model(step_fm)



```


What climate variables to include:
We've settled on: Winter, summer, and spring mean temp; and growing season precip
```{r growth candidate models}
# Candidate models
## sans climate
#gm.base <- lmer(log.ros.areaT1 ~ 1 + (1|plot) + (1|year), data = primula, REML = F)
gm.base.size <- lmer(log.ros.areaT1 ~ log.ros.area + (1|plot) + (1|year), data = primula, REML = F)
gm.base.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.base.trt.int <- lmer(log.ros.areaT1 ~ log.ros.area*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.base.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.base.cor.int <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.base.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.base.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.base.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.base.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*trt*pflower + (1|plot) + (1|year), data = primula, REML = F)

#the rest of the models below are just these + different climate variables + interactions
########################################################################################
##grow season total precip
gm.gs.precip <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.int <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)

gm.gs.precip.trt <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.tot.precip + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.tot.precip + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.tot.precip*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.tot.precip*trt + (1|plot) + (1|year), data = primula, REML = F)

gm.gs.precip.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)

gm.gs.precip.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + trt*grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int4 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int5 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt +  grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt*grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int7 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int8 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.tot.precip + pflower*trt  + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int9 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, REML = F)

gm.gs.precip.cor.trt.int10 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.tot.precip*pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int11 <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.tot.precip*pflower*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int12 <- lmer(log.ros.areaT1 ~ log.ros.area*trt*grow.season.tot.precip + pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.precip.cor.trt.int13 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*trt + grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)



###
#grow season ave temp
gm.gs.av.temp <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.int <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)

gm.gs.av.temp.trt <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.mean.temp + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.mean.temp + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.mean.temp*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.mean.temp*trt + (1|plot) + (1|year), data = primula, REML = F)

gm.gs.av.temp.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)

gm.gs.av.temp.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + trt*grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int4 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower*grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int5 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt +  grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt*grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int7 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower*grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int8 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.mean.temp + pflower*trt  + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int9 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, REML = F)

gm.gs.av.temp.cor.trt.int10 <- lmer(log.ros.areaT1 ~ log.ros.area*grow.season.mean.temp*pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int11 <- lmer(log.ros.areaT1 ~ log.ros.area + grow.season.mean.temp*pflower*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int12 <- lmer(log.ros.areaT1 ~ log.ros.area*trt*grow.season.mean.temp + pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.gs.av.temp.cor.trt.int13 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*trt + grow.season.mean.temp + (1|plot) + (1|year), data = primula, REML = F)

#########################################################################################
##summer total precip
# gm.summer.precip <- lmer(log.ros.areaT1 ~ log.ros.area + summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.int <- lmer(log.ros.areaT1 ~ log.ros.area*summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# 
# gm.summer.precip.trt <- lmer(log.ros.areaT1 ~ log.ros.area + summer.tot.precip + trt + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.tot.precip + trt + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + summer.tot.precip*trt + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.tot.precip*trt + (1|plot) + (1|year), data = primula, REML = F)
# 
# gm.summer.precip.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# 
# gm.summer.precip.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + trt*summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.trt.int4 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.trt.int5 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt +  summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt*summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.trt.int7 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.trt.int8 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.tot.precip + pflower*trt  + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.trt.int9 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
# 
# gm.summer.precip.cor.trt.int10 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.tot.precip*pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.trt.int11 <- lmer(log.ros.areaT1 ~ log.ros.area + summer.tot.precip*pflower*trt + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.trt.int12 <- lmer(log.ros.areaT1 ~ log.ros.area*trt*summer.tot.precip + pflower + (1|plot) + (1|year), data = primula, REML = F)
# gm.summer.precip.cor.trt.int13 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*trt + summer.tot.precip + (1|plot) + (1|year), data = primula, REML = F)

###
#summer ave temp
gm.summer.av.temp <- lmer(log.ros.areaT1 ~ log.ros.area + summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.int <- lmer(log.ros.areaT1 ~ log.ros.area*summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)

gm.summer.av.temp.trt <- lmer(log.ros.areaT1 ~ log.ros.area + summer.mean.temp + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.mean.temp + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + summer.mean.temp*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.mean.temp*trt + (1|plot) + (1|year), data = primula, REML = F)

gm.summer.av.temp.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)

gm.summer.av.temp.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + trt*summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int4 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int5 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt +  summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt*summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int7 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int8 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.mean.temp + pflower*trt  + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int9 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, REML = F)

gm.summer.av.temp.cor.trt.int10 <- lmer(log.ros.areaT1 ~ log.ros.area*summer.mean.temp*pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int11 <- lmer(log.ros.areaT1 ~ log.ros.area + summer.mean.temp*pflower*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int12 <- lmer(log.ros.areaT1 ~ log.ros.area*trt*summer.mean.temp + pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.summer.av.temp.cor.trt.int13 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*trt + summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)


###############################################################################
##winter total precip
# gm.winter.precip <- lmer(log.ros.areaT1 ~ log.ros.area + winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.int <- lmer(log.ros.areaT1 ~ log.ros.area*winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# 
# gm.winter.precip.trt <- lmer(log.ros.areaT1 ~ log.ros.area + winter.tot.precip + trt + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.tot.precip + trt + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + winter.tot.precip*trt + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.tot.precip*trt + (1|plot) + (1|year), data = primula, REML = F)
# 
# gm.winter.precip.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# 
# gm.winter.precip.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + trt*winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.trt.int4 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.trt.int5 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt +  winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt*winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.trt.int7 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.trt.int8 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.tot.precip + pflower*trt  + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.trt.int9 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
# 
# gm.winter.precip.cor.trt.int10 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.tot.precip*pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.trt.int11 <- lmer(log.ros.areaT1 ~ log.ros.area + winter.tot.precip*pflower*trt + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.trt.int12 <- lmer(log.ros.areaT1 ~ log.ros.area*trt*winter.tot.precip + pflower + (1|plot) + (1|year), data = primula, REML = F)
# gm.winter.precip.cor.trt.int13 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*trt + winter.tot.precip + (1|plot) + (1|year), data = primula, REML = F)

###
#winter ave temp
gm.winter.av.temp <- lmer(log.ros.areaT1 ~ log.ros.area + winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.int <- lmer(log.ros.areaT1 ~ log.ros.area*winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)

gm.winter.av.temp.trt <- lmer(log.ros.areaT1 ~ log.ros.area + winter.mean.temp + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.mean.temp + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + winter.mean.temp*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.mean.temp*trt + (1|plot) + (1|year), data = primula, REML = F)

gm.winter.av.temp.cor <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)

gm.winter.av.temp.cor.trt <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int1 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int2 <- lmer(log.ros.areaT1 ~ log.ros.area + trt*pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int3 <- lmer(log.ros.areaT1 ~ log.ros.area + pflower + trt*winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int4 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int5 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt +  winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt*winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int7 <- lmer(log.ros.areaT1 ~ log.ros.area*trt + pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int8 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.mean.temp + pflower*trt  + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int9 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, REML = F)

gm.winter.av.temp.cor.trt.int10 <- lmer(log.ros.areaT1 ~ log.ros.area*winter.mean.temp*pflower + trt + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int11 <- lmer(log.ros.areaT1 ~ log.ros.area + winter.mean.temp*pflower*trt + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int12 <- lmer(log.ros.areaT1 ~ log.ros.area*trt*winter.mean.temp + pflower + (1|plot) + (1|year), data = primula, REML = F)
gm.winter.av.temp.cor.trt.int13 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*trt + winter.mean.temp + (1|plot) + (1|year), data = primula, REML = F)

################################################################################
#Ok - here I'm just looking at growing season, summer, and winter climate of the current year
###
growth <- mget(ls(pattern = "^gm")) #make a list of all of those models that start with gm (^ means start with)
growth_AICc<-aictab(cand.set = growth, modnames = NULL,second.ord=TRUE,nobs=NULL,sort=TRUE)

#rm(list = ls()[grepl("gm", ls())])
#current best fit:
gm.summer.av.temp.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt*summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
summary(gm.summer.av.temp.cor.trt.int6)
#next best:
gm.gs.precip.cor.int3 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, REML = F)
summary(gm.gs.precip.cor.int3)


#saving AIC table:
## names of models:
# names <- as.data.frame(names(growth))
# growth_AICc <- growth_AICc %>% 
#   arrange(Modnames)
# 
# names=data.frame(model.names = c(1:105))
# growth_AICc$model.names[[i]]
# 
# for (i in 1:105) {
#     names$formulas[[i]]<- formula(growth[[i]])
#     names$formulas <- names$formulas
# }

AIC.save <- growth_AICc %>% 
  arrange(AICc) %>% 
  slice_head(n =10)
AIC.save$vitalrate <- "growth"

```

```{r}
#current best fit:
gm.summer.av.temp.cor.trt.int6 <- lmer(log.ros.areaT1 ~ log.ros.area*pflower + trt*summer.mean.temp + (1|plot) + (1|year), data = primula, REML = F)
summary(gm.summer.av.temp.cor.trt.int6)
```

Figure for growth:

```{r}
pred.dat <- expand.grid(
  log.ros.area = seq(min(primula$log.ros.area, na.rm = TRUE), max(primula$log.ros.area, na.rm = TRUE), by = .1), 
  summer.mean.temp = c(-1, 0, 1), 
  pflower = c("0","1"), 
  trt = c("irrigated", "control", "drought"))
pred.dat.output.g <- cbind(pred.dat, log.ros.areaT1 = predict(gm.summer.av.temp.cor.trt.int6, newdata = pred.dat, type = "response", re.form = ~0))

(irrgrowth <- ggplot(data = subset(primula, !is.na(pflower) & trt == "irrigated"), aes(x = log.ros.area, y = log.ros.areaT1))+
  geom_point(alpha= 0.2, shape = 1)+
  geom_abline(slope=1, intercept = 0, color= "black", linewidth = .2)+
  geom_line(data = subset(pred.dat.output.g, trt == "irrigated"), aes(x = log.ros.area, y = log.ros.areaT1, color = as.character(summer.mean.temp), linetype = pflower),linewidth = 1.25)+
  scale_color_manual(values = c("#323697", "#94c8e0", "#f2623f"), name = "Temp.")+
  scale_linetype_manual(values=c("dotted", "solid"), labels = c("vegetative", "flowered"), name = "") +  
  scale_y_continuous(expand = c(0, 0), limits = c(0, 6))+
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+  
  labs(x = "log(Rosette Area) in t", y = "log(Rosette Area) in t + 1", title = "Irrigated")+
  theme(axis.line = element_line(colour = 'black', linewidth = 1.1), 
        text = element_text(size = 20), 
        plot.title = element_text(vjust = - 5, hjust = .03, colour = "#2892c7")))

  #annotate("text",x = .75, y = 5.75, label = "a) irrigated")#+ 
#theme(legend.position="none")

#ggsave(plot = irrgrowth, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/growth irr.png", width = 6, height = 6, dpi = 300)
(cgrowth <- ggplot(data = subset(primula, !is.na(pflower) & trt == "control"), aes(x = log.ros.area, y = log.ros.areaT1))+
  geom_point(alpha= 0.2, shape = 1)+
  geom_abline(slope=1, intercept = 0, color= "black", linewidth = .2)+
  geom_line(data = subset(pred.dat.output.g, trt == "control"), aes(x = log.ros.area, y = log.ros.areaT1, color = as.character(summer.mean.temp), linetype = pflower),linewidth = 1.25)+
  scale_color_manual(values = c("#323697", "#94c8e0", "#f2623f"), name = "Temp.")+
  scale_linetype_manual(values=c("dotted", "solid"), labels = c("vegetative", "flowered"), name = "") +  
  scale_y_continuous(expand = c(0, 0), limits = c(0, 6))+
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+  
  labs(x = "log(Rosette Area) in t", y = "log(Rosette Area) in t + 1", title = "Control")+
  theme(axis.line = element_line(colour = 'black', linewidth = 1.1), 
        text = element_text(size = 20), 
        plot.title = element_text(vjust = - 5, hjust = .03, colour = "#5f9034")))
#ggsave(plot = cgrowth, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/growth control.png", width = 6, height = 6, dpi = 300)

(drgrowth <- ggplot(data = subset(primula, !is.na(pflower) & trt == "drought"), aes(x = log.ros.area, y = log.ros.areaT1))+
  geom_point(alpha= 0.2, shape = 1)+
  geom_abline(slope=1, intercept = 0, color= "black", linewidth = .2)+
  geom_line(data = subset(pred.dat.output.g, trt == "drought"), aes(x = log.ros.area, y = log.ros.areaT1, color = as.character(summer.mean.temp), linetype = pflower),linewidth = 1.25)+
  scale_color_manual(values = c("#323697", "#94c8e0", "#f2623f"), name = "Temp.")+
  scale_linetype_manual(values=c("dotted", "solid"), labels = c("vegetative", "flowered"), name = "") +  
  scale_y_continuous(expand = c(0, 0), limits = c(0, 6))+
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+  
  labs(x = "log(Rosette Area) in t", y = "log(Rosette Area) in t + 1", title = "Drought")+
  theme(axis.line = element_line(colour = 'black', linewidth = 1.1), 
        text = element_text(size = 20), 
        plot.title = element_text(vjust = - 5, hjust = .03, colour = "#e81014")))
#ggsave(plot = drgrowth, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/growth drought.png", width = 6, height = 6, dpi = 300)

#patch these together
(together <- irrgrowth + cgrowth +  drgrowth + plot_layout(guides = "collect", axis_titles = "collect", ncol = 3)+plot_annotation(tag_level = "A"))
ggsave(plot = together, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/growthVR 2-16.png", width = 16, height = 6, dpi = 300)



```
this is for the formorly best fit model - wont work with the scale as is
```{r}
#gm.gs.precip.cor.int3

pred.dat <-  expand.grid(log.ros.area = seq(min(primula$log.ros.area, na.rm = TRUE), max(primula$log.ros.area, na.rm = TRUE), by = .1), grow.season.tot.precip.scale = seq(min(primula$grow.season.tot.precip.scale), max(primula$grow.season.tot.precip.scale), by = .01), pflower = c("0","1"))
pred.output <- predict(gm.gs.precip.cor.int3, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.output <- as.data.frame(pred.output)
pred.dat.output <- cbind(pred.dat, pred.output) %>% 
  rename(log.ros.areaT1 = pred.output)

label <- as_labeller(c("0" = "Vegetative in t", "1" = "Flowered in t"))

ggplot(subset(primula, !is.na(pflower)), aes(x = log.ros.area, y = log.ros.areaT1))+
  geom_point(alpha = 0.25)+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip.scale == 63.6  & pflower == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = "lightblue2", size = 1, linetype = "dashed")+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip.scale == 63.6  & pflower == 1), aes(x = log.ros.area, y = log.ros.areaT1), color = "lightblue2", size = 1)+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip.scale == 155.8  & pflower == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = "dodgerblue", size = 1, linetype = "dashed")+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip.scale == 155.8  & pflower == 1), aes(x = log.ros.area, y = log.ros.areaT1), color = "dodgerblue", size = 1)+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip.scale == 311.6   & pflower == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = "blue2", size = 1, linetype = "dashed")+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip.scale == 311.6   & pflower == 1), aes(x = log.ros.area, y = log.ros.areaT1), color = "blue2", size = 1)+
    geom_abline(slope=1, intercept = 0, linetype = 2, color= "grey", size = 1)+
    facet_wrap(~pflower, labeller = label)+
      scale_y_continuous(expand = c(0, 0), limits = c(0, 6))+
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+
  labs(x = "log(Rosette Area) in t", y = "log(Rosette Area) in t + 1")


#ggsave(plot = growth.fig, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/growth.png", width = 10, height = 6, dpi = 300)
## probably should have some bins here for all the dots...
```

^ but under one precip
```{r}
label <- as_labeller(c("0" = "Vegetative in t", "1" = "Flowered in t"))

growth.fig <- 
  ggplot(subset(primula, !is.na(pflower)), aes(x = log.ros.area, y = log.ros.areaT1, col = fct_rev(pflower)))+
  geom_abline(slope=1, intercept = 0, linetype = 2, color= "grey", size = 1)+
  geom_point(alpha = 0.25)+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip == 155.8  & pflower == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = "#7aa560", size = 1.5)+
  geom_line(data = subset(pred.dat.output, grow.season.tot.precip == 155.8  & pflower == 1), aes(x = log.ros.area, y = log.ros.areaT1), color = "#d983ff", size = 1.5)+

   # facet_wrap(~pflower, labeller = label)+
      scale_y_continuous(expand = c(0, 0), limits = c(0, 6))+
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+
  labs(x = "log(Rosette Area) in t", y = "log(Rosette Area) in t + 1")+
  scale_colour_manual(values = c("#d983ff", "#7aa560")) +
      theme(legend.position = "none")
growth.fig
#ggsave(plot = growth.fig, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/growth.fig.png", width =4, height = 4, dpi = 300)
## probably should have some bins here for all the dots...
```


###
```{r p(flower) testing }
# Probability of flowering  -------------------------------------------------------------

# ## why is N different for pflower?
# test_1702 <- primula %>% 
#   filter(!is.na(pflower),
#          !is.na(log.ros.area),
#          !is.na(pflowerT1))
# test_1703 <- primula %>% 
#   dplyr::filter(!is.na(log.ros.area),
#                 !is.na(pflowerT1))
# overlap <- anti_join(test_1703, test_1702)
# #tag 35 in 2019 did not an entry for pflower/no.flowers - was left blank. Hmm!
# # what to do here - took it out in the cleaning script for 2019

primula %>% filter(!is.na(pflowerT1)) %>% 
  ggplot(aes(x = log.ros.area, y = pflowerT1)) +
  geom_jitter() + 
  geom_smooth(method="glm", method.args=list(family="binomial"), se = F)+
  facet_wrap(~trt)
#ggsave("./Figures/vital rate yearly variation/pflower.png", width = 5, height = 5)

### Do vital rates differ between years?

fm1 <- glm(pflower ~ log(ros.areaTminus1), data = primula, family = "binomial")
fm2 <- glm(pflower ~ log(ros.areaTminus1) + year, data = primula, family = "binomial")
fm3 <- glm(pflower ~ log(ros.areaTminus1)*year, data = primula, family = "binomial")

lrtest(fm1, fm2)
lrtest(fm1, fm3)
# NO

### Do vital rates differ between treatments?

fm1 <- glm(pflower ~ log(ros.areaTminus1), data = primula, family = "binomial")
fm2 <- glm(pflower ~ log(ros.areaTminus1) + trt, data = primula, family = "binomial")
fm3 <- glm(pflower ~ log(ros.areaTminus1)*trt, data = primula, family = "binomial")

lrtest(fm1, fm2)
lrtest(fm1, fm3)

# YES 

# What does this tell us? The probability of flowering does not change across years, but it does change across treatment. However, treatment likely depends on year (some years are drier/wetter, so this will affect strength of treatments/how different they are?). How to test this: Make a model with both and test for a significant interaction? What does the extra water in 2021 mean for this (independent of how much it rained)

fm1 <- glm(pflower ~ log(ros.areaTminus1) + trt, data = primula, family = "binomial")
fm2 <- glm(pflower ~ log(ros.areaTminus1) + trt*year, data = primula, family = "binomial")
fm3 <- glm(pflower ~ log(ros.areaTminus1)*trt + year, data = primula, family = "binomial")

lrtest(fm1, fm2)
lrtest(fm1, fm3)

# What does this tell us: yes there is a significant interaction between year and treatment (read: the influence of treatment on pflower varies across years)
# Does flowering in the previous year affect flowering this year?

fm1 <- glm(pflowerT1 ~ log.ros.area, data = primula, family = "binomial")
fm2 <- glm(pflowerT1 ~ log.ros.area + pflower, data = primula, family = "binomial")
fm3 <- glm(pflowerT1 ~ log.ros.area+ trt, data = primula, family = "binomial")
fm4 <- glm(pflowerT1 ~ log.ros.area +trt + pflower, data = primula, family = "binomial")

lrtest(fm1, fm2, fm3, fm4)
summary(fm2)
rm(list = ls()[grepl("fm", ls())]) #remove these before the candidate sets

```

```{r pflower candidate models}
# Candidate models
## sans climate
#write a function, if model throws an error/warning, have it do this

fm.base <- glmer(pflowerT1 ~ 1 + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.size <- glmer(pflowerT1 ~ log.ros.area + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.trt <- glmer(pflowerT1 ~ log.ros.area + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.trt.int <- glmer(pflowerT1 ~ log.ros.area*trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.cor.int <- glmer(pflowerT1 ~ log.ros.area*pflower + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
fm.base.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.base.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*trt*pflower + (1|plot) + (1|year), data = primula, family = "binomial")

#the rest of the models below are just these + different climate variables + interactions
########################################################################################
##grow season total precip
fm.gs.precip <- glmer(pflowerT1 ~ log.ros.area + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.int <- glmer(pflowerT1 ~ log.ros.area*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")

fm.gs.precip.trt <- glmer(pflowerT1 ~ log.ros.area + grow.season.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*grow.season.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + grow.season.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.precip.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*grow.season.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")

fm.gs.precip.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.int2 <- glmer(pflowerT1 ~ log.ros.area + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.precip.cor.int3 <- glmer(pflowerT1 ~ log.ros.area*pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")

fm.gs.precip.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.precip.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area + pflower + trt*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int4 <- glmer(pflowerT1 ~ log.ros.area + trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
##fm.gs.precip.cor.trt.int5 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt +  grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int6 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.precip.cor.trt.int7 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int8 <- glmer(pflowerT1 ~ log.ros.area*grow.season.tot.precip + pflower*trt  + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int9 <- glmer(pflowerT1 ~ log.ros.area*grow.season.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")

#fm.gs.precip.cor.trt.int10 <- glmer(pflowerT1 ~ log.ros.area*grow.season.tot.precip*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.precip.cor.trt.int11 <- glmer(pflowerT1 ~ log.ros.area + grow.season.tot.precip*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.precip.cor.trt.int12 <- glmer(pflowerT1 ~ log.ros.area*trt*grow.season.tot.precip + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.precip.cor.trt.int13 <- glmer(pflowerT1 ~ log.ros.area*pflower*trt + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")



###
#grow season ave temp
fm.gs.av.temp <- glmer(pflowerT1 ~ log.ros.area + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.int <- glmer(pflowerT1 ~ log.ros.area*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

fm.gs.av.temp.trt <- glmer(pflowerT1 ~ log.ros.area + grow.season.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*grow.season.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + grow.season.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.av.temp.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*grow.season.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")

fm.gs.av.temp.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.int2 <- glmer(pflowerT1 ~ log.ros.area + pflower*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.av.temp.cor.int3 <- glmer(pflowerT1 ~ log.ros.area*pflower*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

fm.gs.av.temp.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.av.temp.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area + pflower + trt*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int4 <- glmer(pflowerT1 ~ log.ros.area + trt + pflower*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.av.temp.cor.trt.int5 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt +  grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.av.temp.cor.trt.int6 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.av.temp.cor.trt.int7 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.av.temp.cor.trt.int8 <- glmer(pflowerT1 ~ log.ros.area*grow.season.mean.temp + pflower*trt  + (1|plot) + (1|year), data = primula, family = "binomial")
fm.gs.av.temp.cor.trt.int9 <- glmer(pflowerT1 ~ log.ros.area*grow.season.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")

#fm.gs.av.temp.cor.trt.int10 <- glmer(pflowerT1 ~ log.ros.area*grow.season.mean.temp*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.av.temp.cor.trt.int11 <- glmer(pflowerT1 ~ log.ros.area + grow.season.mean.temp*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.av.temp.cor.trt.int12 <- glmer(pflowerT1 ~ log.ros.area*trt*grow.season.mean.temp + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.gs.av.temp.cor.trt.int13 <- glmer(pflowerT1 ~ log.ros.area*pflower*trt + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

#########################################################################################
##summer total precip
# fm.summer.precip <- glmer(pflowerT1 ~ log.ros.area + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.int <- glmer(pflowerT1 ~ log.ros.area*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# fm.summer.precip.trt <- glmer(pflowerT1 ~ log.ros.area + summer.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*summer.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + summer.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*summer.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# fm.summer.precip.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.int2 <- glmer(pflowerT1 ~ log.ros.area + pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.int3 <- glmer(pflowerT1 ~ log.ros.area*pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# fm.summer.precip.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area + pflower + trt*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int4 <- glmer(pflowerT1 ~ log.ros.area + trt + pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int5 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt +  summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int6 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int7 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int8 <- glmer(pflowerT1 ~ log.ros.area*summer.tot.precip + pflower*trt  + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int9 <- glmer(pflowerT1 ~ log.ros.area*summer.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# fm.summer.precip.cor.trt.int10 <- glmer(pflowerT1 ~ log.ros.area*summer.tot.precip*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int11 <- glmer(pflowerT1 ~ log.ros.area + summer.tot.precip*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int12 <- glmer(pflowerT1 ~ log.ros.area*trt*summer.tot.precip + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.precip.cor.trt.int13 <- glmer(pflowerT1 ~ log.ros.area*pflower*trt + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# ###
# #summer ave temp
# fm.summer.av.temp <- glmer(pflowerT1 ~ log.ros.area + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.int <- glmer(pflowerT1 ~ log.ros.area*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# fm.summer.av.temp.trt <- glmer(pflowerT1 ~ log.ros.area + summer.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*summer.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + summer.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*summer.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# fm.summer.av.temp.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.int2 <- glmer(pflowerT1 ~ log.ros.area + pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.int3 <- glmer(pflowerT1 ~ log.ros.area*pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# fm.summer.av.temp.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area + pflower + trt*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int4 <- glmer(pflowerT1 ~ log.ros.area + trt + pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int5 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt +  summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int6 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int7 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int8 <- glmer(pflowerT1 ~ log.ros.area*summer.mean.temp + pflower*trt  + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int9 <- glmer(pflowerT1 ~ log.ros.area*summer.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# fm.summer.av.temp.cor.trt.int10 <- glmer(pflowerT1 ~ log.ros.area*summer.mean.temp*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int11 <- glmer(pflowerT1 ~ log.ros.area + summer.mean.temp*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int12 <- glmer(pflowerT1 ~ log.ros.area*trt*summer.mean.temp + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.summer.av.temp.cor.trt.int13 <- glmer(pflowerT1 ~ log.ros.area*pflower*trt + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# 
# ###############################################################################
# ##winter total precip
# fm.winter.precip <- glmer(pflowerT1 ~ log.ros.area + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.int <- glmer(pflowerT1 ~ log.ros.area*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# fm.winter.precip.trt <- glmer(pflowerT1 ~ log.ros.area + winter.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*winter.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + winter.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*winter.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# fm.winter.precip.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.int2 <- glmer(pflowerT1 ~ log.ros.area + pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.int3 <- glmer(pflowerT1 ~ log.ros.area*pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# fm.winter.precip.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area + pflower + trt*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int4 <- glmer(pflowerT1 ~ log.ros.area + trt + pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int5 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt +  winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int6 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int7 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int8 <- glmer(pflowerT1 ~ log.ros.area*winter.tot.precip + pflower*trt  + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int9 <- glmer(pflowerT1 ~ log.ros.area*winter.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# fm.winter.precip.cor.trt.int10 <- glmer(pflowerT1 ~ log.ros.area*winter.tot.precip*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int11 <- glmer(pflowerT1 ~ log.ros.area + winter.tot.precip*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int12 <- glmer(pflowerT1 ~ log.ros.area*trt*winter.tot.precip + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
# fm.winter.precip.cor.trt.int13 <- glmer(pflowerT1 ~ log.ros.area*pflower*trt + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# ###
#winter ave temp
fm.winter.av.temp <- glmer(pflowerT1 ~ log.ros.area + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.int <- glmer(pflowerT1 ~ log.ros.area*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

fm.winter.av.temp.trt <- glmer(pflowerT1 ~ log.ros.area + winter.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*winter.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + winter.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.winter.av.temp.trt.int3 <- glmer(pflowerT1 ~ log.ros.area*winter.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")

fm.winter.av.temp.cor <- glmer(pflowerT1 ~ log.ros.area + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.cor.int2 <- glmer(pflowerT1 ~ log.ros.area + pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.winter.av.temp.cor.int3 <- glmer(pflowerT1 ~ log.ros.area*pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

fm.winter.av.temp.cor.trt <- glmer(pflowerT1 ~ log.ros.area + trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.winter.av.temp.cor.trt.int1 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.cor.trt.int2 <- glmer(pflowerT1 ~ log.ros.area + trt*pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.cor.trt.int3 <- glmer(pflowerT1 ~ log.ros.area + pflower + trt*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.cor.trt.int4 <- glmer(pflowerT1 ~ log.ros.area + trt + pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.cor.trt.int5 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt +  winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.cor.trt.int6 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.cor.trt.int7 <- glmer(pflowerT1 ~ log.ros.area*trt + pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.cor.trt.int8 <- glmer(pflowerT1 ~ log.ros.area*winter.mean.temp + pflower*trt  + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.cor.trt.int9 <- glmer(pflowerT1 ~ log.ros.area*winter.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")

#fm.winter.av.temp.cor.trt.int10 <- glmer(pflowerT1 ~ log.ros.area*winter.mean.temp*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
fm.winter.av.temp.cor.trt.int11 <- glmer(pflowerT1 ~ log.ros.area + winter.mean.temp*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.winter.av.temp.cor.trt.int12 <- glmer(pflowerT1 ~ log.ros.area*trt*winter.mean.temp + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
#fm.winter.av.temp.cor.trt.int13 <- glmer(pflowerT1 ~ log.ros.area*pflower*trt + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

flowering <- mget(ls(pattern = "^fm")) #make a list of all of those models that start with fm (^ means start with)
#now how to get the thing above to work here (ie if you show NULL, include it!!)

# flowering <- flowering %>%  purrr::list_modify("fm.f4" = NULL) %>%  purrr::list_modify("fm11lag" = NULL) %>%  purrr::list_modify("fm.9" = NULL) %>%  
#   purrr::list_modify("fm.f14" = NULL) %>% purrr::list_modify("fm.f12" = NULL) %>% purrr::list_modify("fm.f15" = NULL)  %>% purrr::list_modify("fm17" = NULL) %>% 
#   purrr::list_modify("fm18" = NULL) %>% purrr::list_modify("fm.25" = NULL) %>% purrr::list_modify("fm2" = NULL) %>% purrr::list_modify("fm30" = NULL)# these didnt converge and have low delta AIC's
flowering_AICc<-aictab(cand.set = flowering, modnames = NULL,second.ord=TRUE,nobs=NULL,sort=TRUE)

#rm(list = ls()[grepl("fm", ls())])
#starting from 74
#this is the best one that also converges
#fm.summer.precip.cor.trt.int6
#fm.gs.precip.cor.trt.int10 <- glmer(pflowerT1 ~ log.ros.area*grow.season.tot.precip*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
#summary(fm.gs.precip.cor.trt.int10)
fm.gs.av.temp.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
summary(fm.gs.av.temp.cor.int1)

#fm.summer.precip.cor.trt.int6 <- glmer(pflowerT1 ~ log.ros.area*pflower + trt*summer.tot.precip.scale + (1|plot) + (1|year), data = primula, family = "binomial")
#summary(fm.summer.precip.cor.trt.int6)

AIC.save.flow <- flowering_AICc %>% 
  arrange(AICc) %>% 
  slice_head(n =10)
AIC.save.flow$vitalrate <- "pflower"
AIC.save <- rbind(AIC.save, AIC.save.flow)
```

```{r best fit model}
fm.gs.av.temp.cor.int1 <- glmer(pflowerT1 ~ log.ros.area*pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
summary(fm.gs.av.temp.cor.int1)
```


```{r t}
#fm.gs.precip.cor.trt.int10
pred.dat <- expand.grid(
  log.ros.area = seq(min(primula$log.ros.area, na.rm = TRUE), max(primula$log.ros.area, na.rm = TRUE), by = .1), 
  grow.season.mean.temp = c(-1, 0, 1), 
  pflower = c("0","1"))
pred.dat.output.f <- cbind(pred.dat, pflowerT1 = predict(fm.gs.av.temp.cor.int1, newdata = pred.dat, type = "response", re.form = ~0))

(pflow <- ggplot(subset(primula,!is.na(pflowerT1) & !is.na(pflower)), aes(x = log.ros.area, y = as.numeric(pflowerT1) - 1)) +
  geom_jitter(height = .025, alpha = 0.05) +
  geom_line(data = subset(pred.dat.output.f, pflower == "0" & grow.season.mean.temp == 0), aes(x = log.ros.area, y = pflowerT1), linetype = "dotted", color = "#94c8e0", size = 1.5) +
  geom_line(data = subset(pred.dat.output.f, pflower == "1" & grow.season.mean.temp == 0), aes(x = log.ros.area, y = pflowerT1), color = "#94c8e0", size = 1.5) +
  geom_line(data = subset(pred.dat.output.f, pflower == "0" & grow.season.mean.temp == 1), aes(x = log.ros.area, y = pflowerT1), linetype = "dotted", color = "#f2623f", size = 1.5) +
  geom_line(data = subset(pred.dat.output.f, pflower == "1" & grow.season.mean.temp == 1), aes(x = log.ros.area, y = pflowerT1), color = "#f2623f", size = 1.5) +
  geom_line(data = subset(pred.dat.output.f, pflower == "0" & grow.season.mean.temp == -1), aes(x = log.ros.area, y = pflowerT1), linetype = "dotted", color = "#323697", size = 1.5) +
  geom_line(data = subset(pred.dat.output.f, pflower == "1" & grow.season.mean.temp == -1), aes(x = log.ros.area, y = pflowerT1), color = "#323697", size = 1.5) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6)) +
  labs(x = "log(Rosette Area) in t", y = "Probability of Flowering in t + 1") +
   #annotate("text",x = .9, y = 1.25, label = "b) average summer")+  
  theme(axis.line = element_line(colour = 'black', linewidth = 1.1), text = element_text(size = 20)))


#ggsave(plot = pflow, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/5 gs temp flowering.png", width = 6, height = 6, dpi = 300)

```

```{r}
#fm.base.cor.int
pred.dat <-  expand.grid(log.ros.area = seq(min(primula$log.ros.area, na.rm = TRUE), max(primula$log.ros.area, na.rm = TRUE), by = .1), pflower = c("0","1"))
pred.output <- predict(fm.base.cor.int, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.output <- as.data.frame(pred.output)
pred.dat.output <- cbind(pred.dat, pred.output) %>% 
  rename(pflowerT1 = pred.output) 


ggplot(
  subset(primula,!is.na(pflowerT1) &
           !is.na(pflower)),
  aes(
    x = log.ros.area,
    y = pflowerT1,
    color = as.factor(pflower)
  )
) +
  geom_jitter(height = .15, alpha = 0.5) +
  scale_color_manual(values = c("lightsteelblue3", "grey0")) +
  geom_line(
    data = subset(pred.dat.output, pflower == "0"),
    aes(x = log.ros.area, y = pflowerT1),
    linetype = "dashed"
  ) +
  geom_line(data = subset(pred.dat.output, pflower == "1"),
            aes(x = log.ros.area, y = pflowerT1)) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6)) +
  labs(x = "log(Rosette Area) in t", y = "Probability of Flowering in t + 1") +
  theme(legend.position = "none")
pflower.fig

#ggsave(plot = pflower.fig, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/pflower.png", width = 6, height = 6, dpi = 300)
```

```{r}
pflower.fig <- 
  primula %>%
  filter(!is.na(pflowerT1) &
           !is.na(pflower)) %>%
  ggplot(aes(col = fct_rev(pflower))) +
  geom_jitter(aes(x = log.ros.area, y = as.numeric(pflowerT1) - 1),
              width = .1, height = 0.15,
              alpha = 0.2) +
  geom_line(aes(x = log.ros.area, y = as.numeric(pflowerT1),
                ),
            data = pred.dat.output, linewidth = 1.5) + 
  scale_colour_manual(values = c("#d983ff", "#7aa560")) +
  labs(col = NULL,
       lty = NULL,
       x = "log(Rosette Area) in t", y = "Probability of Flowering in t + 1")+
  scale_y_continuous(breaks = c(0,1))+
    theme(legend.position = "none")


pflower.fig

#ggsave(plot = pflower.fig, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/pflower.fig.png", width = 5, height = 5, dpi = 300)
```

#survival:
```{r pflower candidate models}
# Candidate models
## sans climate
#write a function, if model throws an error/warning, have it do this

#sm.base <- glmer(psurvivalT1 ~ 1 + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.size <- glmer(psurvivalT1 ~ log.ros.area + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.trt.int <- glmer(psurvivalT1 ~ log.ros.area*trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.cor.int <- glmer(psurvivalT1 ~ log.ros.area*pflower + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
sm.base.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.base.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*trt*pflower + (1|plot) + (1|year), data = primula, family = "binomial")
#the rest of the models below are just these + different climate variables + interactions
########################################################################################
##grow season total precip
sm.gs.precip <- glmer(psurvivalT1 ~ log.ros.area + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.int <- glmer(psurvivalT1 ~ log.ros.area*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")

sm.gs.precip.trt <- glmer(psurvivalT1 ~ log.ros.area + grow.season.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + grow.season.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.gs.precip.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")

sm.gs.precip.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.int1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.int2 <- glmer(psurvivalT1 ~ log.ros.area + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.gs.precip.cor.int3 <- glmer(psurvivalT1 ~ log.ros.area*pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")

sm.gs.precip.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area + pflower + trt*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int4 <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int5 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt +  grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.gs.precip.cor.trt.int6 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int7 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int8 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.tot.precip + pflower*trt  + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int9 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")

#sm.gs.precip.cor.trt.int10 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.tot.precip*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.precip.cor.trt.int11 <- glmer(psurvivalT1 ~ log.ros.area + grow.season.tot.precip*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.gs.precip.cor.trt.int12 <- glmer(psurvivalT1 ~ log.ros.area*trt*grow.season.tot.precip + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.gs.precip.cor.trt.int13 <- glmer(psurvivalT1 ~ log.ros.area*pflower*trt + grow.season.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")



###
#grow season ave temp
sm.gs.av.temp <- glmer(psurvivalT1 ~ log.ros.area + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.int <- glmer(psurvivalT1 ~ log.ros.area*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

sm.gs.av.temp.trt <- glmer(psurvivalT1 ~ log.ros.area + grow.season.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + grow.season.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.gs.av.temp.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")

sm.gs.av.temp.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.int1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.int2 <- glmer(psurvivalT1 ~ log.ros.area + pflower*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.gs.av.temp.cor.int3 <- glmer(psurvivalT1 ~ log.ros.area*pflower*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

sm.gs.av.temp.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area + pflower + trt*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int4 <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int5 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt +  grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.gs.av.temp.cor.trt.int6 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int7 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower*grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int8 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.mean.temp + pflower*trt  + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int9 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")

#sm.gs.av.temp.cor.trt.int10 <- glmer(psurvivalT1 ~ log.ros.area*grow.season.mean.temp*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.gs.av.temp.cor.trt.int11 <- glmer(psurvivalT1 ~ log.ros.area + grow.season.mean.temp*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.gs.av.temp.cor.trt.int12 <- glmer(psurvivalT1 ~ log.ros.area*trt*grow.season.mean.temp + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.gs.av.temp.cor.trt.int13 <- glmer(psurvivalT1 ~ log.ros.area*pflower*trt + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

#########################################################################################
##summer total precip
# sm.summer.precip <- glmer(psurvivalT1 ~ log.ros.area + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.int <- glmer(psurvivalT1 ~ log.ros.area*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# sm.summer.precip.trt <- glmer(psurvivalT1 ~ log.ros.area + summer.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*summer.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + summer.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*summer.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# sm.summer.precip.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.int1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.int2 <- glmer(psurvivalT1 ~ log.ros.area + pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.int3 <- glmer(psurvivalT1 ~ log.ros.area*pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# sm.summer.precip.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area + pflower + trt*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int4 <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int5 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt +  summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int6 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int7 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower*summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int8 <- glmer(psurvivalT1 ~ log.ros.area*summer.tot.precip + pflower*trt  + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int9 <- glmer(psurvivalT1 ~ log.ros.area*summer.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# sm.summer.precip.cor.trt.int10 <- glmer(psurvivalT1 ~ log.ros.area*summer.tot.precip*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int11 <- glmer(psurvivalT1 ~ log.ros.area + summer.tot.precip*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int12 <- glmer(psurvivalT1 ~ log.ros.area*trt*summer.tot.precip + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.summer.precip.cor.trt.int13 <- glmer(psurvivalT1 ~ log.ros.area*pflower*trt + summer.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# ###
#summer ave temp
sm.summer.av.temp <- glmer(psurvivalT1 ~ log.ros.area + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.summer.av.temp.int <- glmer(psurvivalT1 ~ log.ros.area*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

sm.summer.av.temp.trt <- glmer(psurvivalT1 ~ log.ros.area + summer.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.summer.av.temp.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*summer.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.summer.av.temp.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + summer.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.summer.av.temp.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*summer.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")

sm.summer.av.temp.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.summer.av.temp.cor.int1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.summer.av.temp.cor.int2 <- glmer(psurvivalT1 ~ log.ros.area + pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.summer.av.temp.cor.int3 <- glmer(psurvivalT1 ~ log.ros.area*pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

sm.summer.av.temp.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.summer.av.temp.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.summer.av.temp.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.summer.av.temp.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area + pflower + trt*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.summer.av.temp.cor.trt.int4 <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.summer.av.temp.cor.trt.int5 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt +  summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.summer.av.temp.cor.trt.int6 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.summer.av.temp.cor.trt.int7 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower*summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.summer.av.temp.cor.trt.int8 <- glmer(psurvivalT1 ~ log.ros.area*summer.mean.temp + pflower*trt  + (1|plot) + (1|year), data = primula, family = "binomial")
sm.summer.av.temp.cor.trt.int9 <- glmer(psurvivalT1 ~ log.ros.area*summer.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")

#sm.summer.av.temp.cor.trt.int10 <- glmer(psurvivalT1 ~ log.ros.area*summer.mean.temp*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.summer.av.temp.cor.trt.int11 <- glmer(psurvivalT1 ~ log.ros.area + summer.mean.temp*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.summer.av.temp.cor.trt.int12 <- glmer(psurvivalT1 ~ log.ros.area*trt*summer.mean.temp + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.summer.av.temp.cor.trt.int13 <- glmer(psurvivalT1 ~ log.ros.area*pflower*trt + summer.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")


###############################################################################
##winter total precip
# sm.winter.precip <- glmer(psurvivalT1 ~ log.ros.area + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.int <- glmer(psurvivalT1 ~ log.ros.area*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# sm.winter.precip.trt <- glmer(psurvivalT1 ~ log.ros.area + winter.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*winter.tot.precip + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + winter.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*winter.tot.precip*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# sm.winter.precip.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.int1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.int2 <- glmer(psurvivalT1 ~ log.ros.area + pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.int3 <- glmer(psurvivalT1 ~ log.ros.area*pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# sm.winter.precip.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area + pflower + trt*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int4 <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int5 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt +  winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int6 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int7 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower*winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int8 <- glmer(psurvivalT1 ~ log.ros.area*winter.tot.precip + pflower*trt  + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int9 <- glmer(psurvivalT1 ~ log.ros.area*winter.tot.precip + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# 
# sm.winter.precip.cor.trt.int10 <- glmer(psurvivalT1 ~ log.ros.area*winter.tot.precip*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int11 <- glmer(psurvivalT1 ~ log.ros.area + winter.tot.precip*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int12 <- glmer(psurvivalT1 ~ log.ros.area*trt*winter.tot.precip + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
# sm.winter.precip.cor.trt.int13 <- glmer(psurvivalT1 ~ log.ros.area*pflower*trt + winter.tot.precip + (1|plot) + (1|year), data = primula, family = "binomial")

###
#winter ave temp
sm.winter.av.temp <- glmer(psurvivalT1 ~ log.ros.area + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.int <- glmer(psurvivalT1 ~ log.ros.area*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

sm.winter.av.temp.trt <- glmer(psurvivalT1 ~ log.ros.area + winter.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*winter.mean.temp + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + winter.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.winter.av.temp.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area*winter.mean.temp*trt + (1|plot) + (1|year), data = primula, family = "binomial")

sm.winter.av.temp.cor <- glmer(psurvivalT1 ~ log.ros.area + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.cor.int1 <- glmer(psurvivalT1 ~ log.ros.area*pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.cor.int2 <- glmer(psurvivalT1 ~ log.ros.area + pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.winter.av.temp.cor.int3 <- glmer(psurvivalT1 ~ log.ros.area*pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

sm.winter.av.temp.cor.trt <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.cor.trt.int1 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.cor.trt.int2 <- glmer(psurvivalT1 ~ log.ros.area + trt*pflower + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.cor.trt.int3 <- glmer(psurvivalT1 ~ log.ros.area + pflower + trt*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.cor.trt.int4 <- glmer(psurvivalT1 ~ log.ros.area + trt + pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.cor.trt.int5 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt +  winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.winter.av.temp.cor.trt.int6 <- glmer(psurvivalT1 ~ log.ros.area*pflower + trt*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.cor.trt.int7 <- glmer(psurvivalT1 ~ log.ros.area*trt + pflower*winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.cor.trt.int8 <- glmer(psurvivalT1 ~ log.ros.area*winter.mean.temp + pflower*trt  + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.cor.trt.int9 <- glmer(psurvivalT1 ~ log.ros.area*winter.mean.temp + pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")

#sm.winter.av.temp.cor.trt.int10 <- glmer(psurvivalT1 ~ log.ros.area*winter.mean.temp*pflower + trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.cor.trt.int11 <- glmer(psurvivalT1 ~ log.ros.area + winter.mean.temp*pflower*trt + (1|plot) + (1|year), data = primula, family = "binomial")
sm.winter.av.temp.cor.trt.int12 <- glmer(psurvivalT1 ~ log.ros.area*trt*winter.mean.temp + pflower + (1|plot) + (1|year), data = primula, family = "binomial")
#sm.winter.av.temp.cor.trt.int13 <- glmer(psurvivalT1 ~ log.ros.area*pflower*trt + winter.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

#is this has something, don't include it in the list!
#sm.gs.precip.cor.int3@optinfo$conv$lme4$messages #this is !NULL, which means it did not converge
#
#sm.winter.av.temp.cor.trt.int7@optinfo$conv$lme4$messages #if NULL, then it converges! this is a model that converges

survival <- mget(ls(pattern = "^sm")) #make a list of all of those models that start with gm (^ means start with)
#now how to get the thing above to work here (ie if you show NULL, include it!!)

# flowering <- flowering %>%  purrr::list_modify("sm.f4" = NULL) %>%  purrr::list_modify("sm11lag" = NULL) %>%  purrr::list_modify("sm.9" = NULL) %>%  
#   purrr::list_modify("sm.f14" = NULL) %>% purrr::list_modify("sm.f12" = NULL) %>% purrr::list_modify("sm.f15" = NULL)  %>% purrr::list_modify("sm17" = NULL) %>% 
#   purrr::list_modify("sm18" = NULL) %>% purrr::list_modify("sm.25" = NULL) %>% purrr::list_modify("sm2" = NULL) %>% purrr::list_modify("sm30" = NULL)# these didnt converge and have low delta AIC's
survival_AICc<-aictab(cand.set = survival, modnames = NULL,second.ord=TRUE,nobs=NULL,sort=TRUE)
#best fit is:
sm.gs.av.temp <- glmer(psurvivalT1 ~ log.ros.area + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

summary(	
sm.gs.av.temp
)
#rm(list = ls()[grepl("sm", ls())])

#and it converges etc

AIC.save.surv <- survival_AICc %>% 
  arrange(AICc) %>% 
  slice_head(n =10)
AIC.save.surv$vitalrate <- "survival"
AIC.save <- rbind(AIC.save, AIC.save.surv)
```

```{r}
#best fit is:
sm.gs.av.temp <- glmer(psurvivalT1 ~ log.ros.area + grow.season.mean.temp + (1|plot) + (1|year), data = primula, family = "binomial")

summary(	
sm.gs.av.temp
)
```


#survial figure
```{r}
pred.dat <- expand.grid(
  log.ros.area = seq(min(primula$log.ros.area, na.rm = TRUE), max(primula$log.ros.area, na.rm = TRUE), by = .1), 
  grow.season.mean.temp = c(-1, 0, 1))
pred.dat.output.s <- cbind(pred.dat, survT1 = predict(sm.gs.av.temp, newdata = pred.dat, type = "response", re.form = ~0))


(survival <- 

  ggplot(subset(primula, !is.na(psurvivalT1)), aes(x = log.ros.area, y = as.numeric(psurvivalT1)-1))+
  geom_jitter(height = .025, alpha = 0.05) +
  geom_line(data = subset(pred.dat.output.s, grow.season.mean.temp == -1), aes(x = log.ros.area, y = survT1), color = "#323697", size = 1.5) +
  geom_line(data = subset(pred.dat.output.s, grow.season.mean.temp == 1), aes(x = log.ros.area, y = survT1), color = "#f2623f", size = 1.5) +
  geom_line(data = subset(pred.dat.output.s, grow.season.mean.temp == 0), aes(x = log.ros.area, y = survT1), color = "#94c8e0", size = 1.5) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+
  labs(x = "log(Rosette Area) in t", y = "Survival in t+1")+
  theme(axis.line = element_line(colour = 'black', linewidth = 1.1), text = element_text(size = 20)))
survival
#ggsave(plot = survival, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/2survival temp.fig.png", width = 6, height = 6, dpi = 300)

```

#no flowers

```{r does no. flowers change across years}

ggplot(data = subset(primula, flow.sumT1 > 0), aes(x = log.ros.area, y = flow.sumT1, group = year)) + 
  geom_point()+
    geom_smooth(method="glm", method.args=list(family="poisson"), se = F)+
  facet_wrap(~year)

ggplot(data = subset(primula, flow.sum > 0), aes(x = log.ros.area, y = flow.sum)) + 
  geom_point()
```


```{r model selection}
noflowers.base <- glmer(flow.sumT1 ~ 1 + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.base.size <- glmer(flow.sumT1 ~ log.ros.area + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.base.trt <- glmer(flow.sumT1 ~ log.ros.area + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.base.trt.int <- glmer(flow.sumT1 ~ log.ros.area*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.base.cor <- glmer(flow.sumT1 ~ log.ros.area + pflower + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.base.cor.int <- glmer(flow.sumT1 ~ log.ros.area*pflower + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.base.cor.trt <- glmer(flow.sumT1 ~ log.ros.area + trt + pflower + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.base.cor.trt.int1 <- glmer(flow.sumT1 ~ log.ros.area*trt + pflower + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.base.cor.trt.int2 <- glmer(flow.sumT1 ~ log.ros.area + trt*pflower + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.base.cor.trt.int3 <- glmer(flow.sumT1 ~ log.ros.area*trt*pflower + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#the rest of the models below are just these + different climate variables + interactions
########################################################################################
##grow season total precip
noflowers.gs.precip <- glmer(flow.sumT1 ~ log.ros.area + grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.int <- glmer(flow.sumT1 ~ log.ros.area*grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

noflowers.gs.precip.trt <- glmer(flow.sumT1 ~ log.ros.area + grow.season.tot.precip + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.trt.int1 <- glmer(flow.sumT1 ~ log.ros.area*grow.season.tot.precip + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.trt.int2 <- glmer(flow.sumT1 ~ log.ros.area + grow.season.tot.precip*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.precip.trt.int3 <- glmer(flow.sumT1 ~ log.ros.area*grow.season.tot.precip*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

noflowers.gs.precip.cor <- glmer(flow.sumT1 ~ log.ros.area + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.cor.int1 <- glmer(flow.sumT1 ~ log.ros.area*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.cor.int2 <- glmer(flow.sumT1 ~ log.ros.area + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.cor.int3 <- glmer(flow.sumT1 ~ log.ros.area*pflower*grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

noflowers.gs.precip.cor.trt <- glmer(flow.sumT1 ~ log.ros.area + trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.precip.cor.trt.int1 <- glmer(flow.sumT1 ~ log.ros.area*trt + pflower + grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int2 <- glmer(flow.sumT1 ~ log.ros.area + trt*pflower + grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int3 <- glmer(flow.sumT1 ~ log.ros.area + pflower + trt*grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int4 <- glmer(flow.sumT1 ~ log.ros.area + trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.precip.cor.trt.int5 <- glmer(flow.sumT1 ~ log.ros.area*pflower + trt +  grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int6 <- glmer(flow.sumT1 ~ log.ros.area*pflower + trt*grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int7 <- glmer(flow.sumT1 ~ log.ros.area*trt + pflower*grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.precip.cor.trt.int8 <- glmer(flow.sumT1 ~ log.ros.area*grow.season.tot.precip + pflower*trt  + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int9 <- glmer(flow.sumT1 ~ log.ros.area*grow.season.tot.precip + pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

#noflowers.gs.precip.cor.trt.int10 <- glmer(flow.sumT1 ~ log.ros.area*grow.season.tot.precip*pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int11 <- glmer(flow.sumT1 ~ log.ros.area + grow.season.tot.precip*pflower*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.precip.cor.trt.int12 <- glmer(flow.sumT1 ~ log.ros.area*trt*grow.season.tot.precip + pflower + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.precip.cor.trt.int13 <- glmer(flow.sumT1 ~ log.ros.area*pflower*trt + grow.season.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")



###
#grow season ave temp
noflowers.gs.av.temp <- glmer(flow.sumT1 ~ log.ros.area + grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.av.temp.int <- glmer(flow.sumT1 ~ log.ros.area*grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

noflowers.gs.av.temp.trt <- glmer(flow.sumT1 ~ log.ros.area + grow.season.mean.temp + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.av.temp.trt.int1 <- glmer(flow.sumT1 ~ log.ros.area*grow.season.mean.temp + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.av.temp.trt.int2 <- glmer(flow.sumT1 ~ log.ros.area + grow.season.mean.temp*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.av.temp.trt.int3 <- glmer(flow.sumT1 ~ log.ros.area*grow.season.mean.temp*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

noflowers.gs.av.temp.cor <- glmer(flow.sumT1 ~ log.ros.area + pflower + grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.av.temp.cor.int1 <- glmer(flow.sumT1 ~ log.ros.area*pflower + grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.av.temp.cor.int2 <- glmer(flow.sumT1 ~ log.ros.area + pflower*grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.av.temp.cor.int3 <- glmer(flow.sumT1 ~ log.ros.area*pflower*grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

noflowers.gs.av.temp.cor.trt <- glmer(flow.sumT1 ~ log.ros.area + trt + pflower + grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.av.temp.cor.trt.int1 <- glmer(flow.sumT1 ~ log.ros.area*trt + pflower + grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int2 <- glmer(flow.sumT1 ~ log.ros.area + trt*pflower + grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int3 <- glmer(flow.sumT1 ~ log.ros.area + pflower + trt*grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.gs.av.temp.cor.trt.int4 <- glmer(flow.sumT1 ~ log.ros.area + trt + pflower*grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.av.temp.cor.trt.int5 <- glmer(flow.sumT1 ~ log.ros.area*pflower + trt +  grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.av.temp.cor.trt.int6 <- glmer(flow.sumT1 ~ log.ros.area*pflower + trt*grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.av.temp.cor.trt.int7 <- glmer(flow.sumT1 ~ log.ros.area*trt + pflower*grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.av.temp.cor.trt.int8 <- glmer(flow.sumT1 ~ log.ros.area*grow.season.mean.temp + pflower*trt  + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.av.temp.cor.trt.int9 <- glmer(flow.sumT1 ~ log.ros.area*grow.season.mean.temp + pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

#noflowers.gs.av.temp.cor.trt.int10 <- glmer(flow.sumT1 ~ log.ros.area*grow.season.mean.temp*pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.av.temp.cor.trt.int11 <- glmer(flow.sumT1 ~ log.ros.area + grow.season.mean.temp*pflower*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.av.temp.cor.trt.int12 <- glmer(flow.sumT1 ~ log.ros.area*trt*grow.season.mean.temp + pflower + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.gs.av.temp.cor.trt.int13 <- glmer(flow.sumT1 ~ log.ros.area*pflower*trt + grow.season.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

#########################################################################################
##summer total precip
# noflowers.summer.precip <- glmer(flow.sumT1 ~ log.ros.area + summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.int <- glmer(flow.sumT1 ~ log.ros.area*summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# 
# noflowers.summer.precip.trt <- glmer(flow.sumT1 ~ log.ros.area + summer.tot.precip + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.trt.int1 <- glmer(flow.sumT1 ~ log.ros.area*summer.tot.precip + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.trt.int2 <- glmer(flow.sumT1 ~ log.ros.area + summer.tot.precip*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.trt.int3 <- glmer(flow.sumT1 ~ log.ros.area*summer.tot.precip*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# 
# noflowers.summer.precip.cor <- glmer(flow.sumT1 ~ log.ros.area + pflower + summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.int1 <- glmer(flow.sumT1 ~ log.ros.area*pflower + summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.int2 <- glmer(flow.sumT1 ~ log.ros.area + pflower*summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.int3 <- glmer(flow.sumT1 ~ log.ros.area*pflower*summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# 
# noflowers.summer.precip.cor.trt <- glmer(flow.sumT1 ~ log.ros.area + trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int1 <- glmer(flow.sumT1 ~ log.ros.area*trt + pflower + summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int2 <- glmer(flow.sumT1 ~ log.ros.area + trt*pflower + summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int3 <- glmer(flow.sumT1 ~ log.ros.area + pflower + trt*summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int4 <- glmer(flow.sumT1 ~ log.ros.area + trt + pflower*summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int5 <- glmer(flow.sumT1 ~ log.ros.area*pflower + trt +  summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int6 <- glmer(flow.sumT1 ~ log.ros.area*pflower + trt*summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int7 <- glmer(flow.sumT1 ~ log.ros.area*trt + pflower*summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int8 <- glmer(flow.sumT1 ~ log.ros.area*summer.tot.precip + pflower*trt  + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int9 <- glmer(flow.sumT1 ~ log.ros.area*summer.tot.precip + pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# 
# noflowers.summer.precip.cor.trt.int10 <- glmer(flow.sumT1 ~ log.ros.area*summer.tot.precip*pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int11 <- glmer(flow.sumT1 ~ log.ros.area + summer.tot.precip*pflower*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int12 <- glmer(flow.sumT1 ~ log.ros.area*trt*summer.tot.precip + pflower + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.summer.precip.cor.trt.int13 <- glmer(flow.sumT1 ~ log.ros.area*pflower*trt + summer.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# 
# ###
#summer ave temp
noflowers.summer.av.temp <- glmer(flow.sumT1 ~ log.ros.area + summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.summer.av.temp.int <- glmer(flow.sumT1 ~ log.ros.area*summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

noflowers.summer.av.temp.trt <- glmer(flow.sumT1 ~ log.ros.area + summer.mean.temp + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.summer.av.temp.trt.int1 <- glmer(flow.sumT1 ~ log.ros.area*summer.mean.temp + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.summer.av.temp.trt.int2 <- glmer(flow.sumT1 ~ log.ros.area + summer.mean.temp*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.summer.av.temp.trt.int3 <- glmer(flow.sumT1 ~ log.ros.area*summer.mean.temp*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

noflowers.summer.av.temp.cor <- glmer(flow.sumT1 ~ log.ros.area + pflower + summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.summer.av.temp.cor.int1 <- glmer(flow.sumT1 ~ log.ros.area*pflower + summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.summer.av.temp.cor.int2 <- glmer(flow.sumT1 ~ log.ros.area + pflower*summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.summer.av.temp.cor.int3 <- glmer(flow.sumT1 ~ log.ros.area*pflower*summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

noflowers.summer.av.temp.cor.trt <- glmer(flow.sumT1 ~ log.ros.area + trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.summer.av.temp.cor.trt.int1 <- glmer(flow.sumT1 ~ log.ros.area*trt + pflower + summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.summer.av.temp.cor.trt.int2 <- glmer(flow.sumT1 ~ log.ros.area + trt*pflower + summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.summer.av.temp.cor.trt.int3 <- glmer(flow.sumT1 ~ log.ros.area + pflower + trt*summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.summer.av.temp.cor.trt.int4 <- glmer(flow.sumT1 ~ log.ros.area + trt + pflower*summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.summer.av.temp.cor.trt.int5 <- glmer(flow.sumT1 ~ log.ros.area*pflower + trt +  summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.summer.av.temp.cor.trt.int6 <- glmer(flow.sumT1 ~ log.ros.area*pflower + trt*summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.summer.av.temp.cor.trt.int7 <- glmer(flow.sumT1 ~ log.ros.area*trt + pflower*summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.summer.av.temp.cor.trt.int8 <- glmer(flow.sumT1 ~ log.ros.area*summer.mean.temp + pflower*trt  + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.summer.av.temp.cor.trt.int9 <- glmer(flow.sumT1 ~ log.ros.area*summer.mean.temp + pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

#noflowers.summer.av.temp.cor.trt.int10 <- glmer(flow.sumT1 ~ log.ros.area*summer.mean.temp*pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.summer.av.temp.cor.trt.int11 <- glmer(flow.sumT1 ~ log.ros.area + summer.mean.temp*pflower*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.summer.av.temp.cor.trt.int12 <- glmer(flow.sumT1 ~ log.ros.area*trt*summer.mean.temp + pflower + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.summer.av.temp.cor.trt.int13 <- glmer(flow.sumT1 ~ log.ros.area*pflower*trt + summer.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")


###############################################################################
##winter total precip
# noflowers.winter.precip <- glmer(flow.sumT1 ~ log.ros.area + winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.int <- glmer(flow.sumT1 ~ log.ros.area*winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# 
# noflowers.winter.precip.trt <- glmer(flow.sumT1 ~ log.ros.area + winter.tot.precip + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.trt.int1 <- glmer(flow.sumT1 ~ log.ros.area*winter.tot.precip + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.trt.int2 <- glmer(flow.sumT1 ~ log.ros.area + winter.tot.precip*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.trt.int3 <- glmer(flow.sumT1 ~ log.ros.area*winter.tot.precip*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# 
# noflowers.winter.precip.cor <- glmer(flow.sumT1 ~ log.ros.area + pflower + winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.int1 <- glmer(flow.sumT1 ~ log.ros.area*pflower + winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.int2 <- glmer(flow.sumT1 ~ log.ros.area + pflower*winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.int3 <- glmer(flow.sumT1 ~ log.ros.area*pflower*winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# 
# noflowers.winter.precip.cor.trt <- glmer(flow.sumT1 ~ log.ros.area + trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int1 <- glmer(flow.sumT1 ~ log.ros.area*trt + pflower + winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int2 <- glmer(flow.sumT1 ~ log.ros.area + trt*pflower + winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int3 <- glmer(flow.sumT1 ~ log.ros.area + pflower + trt*winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int4 <- glmer(flow.sumT1 ~ log.ros.area + trt + pflower*winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int5 <- glmer(flow.sumT1 ~ log.ros.area*pflower + trt +  winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int6 <- glmer(flow.sumT1 ~ log.ros.area*pflower + trt*winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int7 <- glmer(flow.sumT1 ~ log.ros.area*trt + pflower*winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int8 <- glmer(flow.sumT1 ~ log.ros.area*winter.tot.precip + pflower*trt  + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int9 <- glmer(flow.sumT1 ~ log.ros.area*winter.tot.precip + pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# 
# noflowers.winter.precip.cor.trt.int10 <- glmer(flow.sumT1 ~ log.ros.area*winter.tot.precip*pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int11 <- glmer(flow.sumT1 ~ log.ros.area + winter.tot.precip*pflower*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int12 <- glmer(flow.sumT1 ~ log.ros.area*trt*winter.tot.precip + pflower + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
# noflowers.winter.precip.cor.trt.int13 <- glmer(flow.sumT1 ~ log.ros.area*pflower*trt + winter.tot.precip + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

###
#winter ave temp
noflowers.winter.av.temp <- glmer(flow.sumT1 ~ log.ros.area + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.int <- glmer(flow.sumT1 ~ log.ros.area*winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

noflowers.winter.av.temp.trt <- glmer(flow.sumT1 ~ log.ros.area + winter.mean.temp + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.trt.int1 <- glmer(flow.sumT1 ~ log.ros.area*winter.mean.temp + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.trt.int2 <- glmer(flow.sumT1 ~ log.ros.area + winter.mean.temp*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.trt.int3 <- glmer(flow.sumT1 ~ log.ros.area*winter.mean.temp*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

noflowers.winter.av.temp.cor <- glmer(flow.sumT1 ~ log.ros.area + pflower + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.int1 <- glmer(flow.sumT1 ~ log.ros.area*pflower + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.int2 <- glmer(flow.sumT1 ~ log.ros.area + pflower*winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.int3 <- glmer(flow.sumT1 ~ log.ros.area*pflower*winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

noflowers.winter.av.temp.cor.trt <- glmer(flow.sumT1 ~ log.ros.area + trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.trt.int1 <- glmer(flow.sumT1 ~ log.ros.area*trt + pflower + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.trt.int2 <- glmer(flow.sumT1 ~ log.ros.area + trt*pflower + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.trt.int3 <- glmer(flow.sumT1 ~ log.ros.area + pflower + trt*winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.trt.int4 <- glmer(flow.sumT1 ~ log.ros.area + trt + pflower*winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.trt.int5 <- glmer(flow.sumT1 ~ log.ros.area*pflower + trt +  winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.trt.int6 <- glmer(flow.sumT1 ~ log.ros.area*pflower + trt*winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.trt.int7 <- glmer(flow.sumT1 ~ log.ros.area*trt + pflower*winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.trt.int8 <- glmer(flow.sumT1 ~ log.ros.area*winter.mean.temp + pflower*trt  + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.trt.int9 <- glmer(flow.sumT1 ~ log.ros.area*winter.mean.temp + pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

noflowers.winter.av.temp.cor.trt.int10 <- glmer(flow.sumT1 ~ log.ros.area*winter.mean.temp*pflower + trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
#noflowers.winter.av.temp.cor.trt.int11 <- glmer(flow.sumT1 ~ log.ros.area + winter.mean.temp*pflower*trt + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.trt.int12 <- glmer(flow.sumT1 ~ log.ros.area*trt*winter.mean.temp + pflower + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")
noflowers.winter.av.temp.cor.trt.int13 <- glmer(flow.sumT1 ~ log.ros.area*pflower*trt + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")



#to do: 
#is this has something, don't include it in the list!
#noflowers.gs.precip.cor.int3@optinfo$conv$lme4$messages #this is !NULL, which means it did not converge
#
#noflowers.winter.av.temp.cor.trt.int7@optinfo$conv$lme4$messages #if NULL, then it converges! this is a model that converges



poisson <- mget(ls(pattern = "^noflowers")) #make a list of all of those models that start with gm (^ means start with)

poisson_AICc<-aictab(cand.set = poisson, modnames = NULL,second.ord=TRUE,nobs=NULL,sort=TRUE)

#noflowers.winter.av.temp <- glmer(flow.sumT1 ~ log.ros.area + winter.mean.temp.scale + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

summary(noflowers.winter.av.temp)


#rm(list = ls()[grepl("noflowers", ls())])

#best fit model is that - lots of convergence/singular/rank deficient errors - the poissons are hard to fit!

AIC.save.nof <- poisson_AICc %>% 
  arrange(AICc) %>% 
  slice_head(n =10)
AIC.save.nof$vitalrate <- "no.flowers"
AIC.save <- rbind(AIC.save, AIC.save.nof)
```

```{r run best fit model}

noflowers.winter.av.temp <- glmer(flow.sumT1 ~ log.ros.area + winter.mean.temp + (1|plot) + (1|year), data = subset(primula, flow.sumT1 > 0), family = "poisson")

summary(noflowers.winter.av.temp)
```


```{r figures}
pred.dat <- expand.grid(
  log.ros.area = seq(1.5, 6, by = .1), 
  winter.mean.temp = c(-1, 0, 1))
pred.dat.output.n <- cbind(pred.dat, noflowers = predict(noflowers.winter.av.temp, newdata = pred.dat, type = "response", re.form = ~0))

(poisson <- 
  ggplot(subset(primula, !is.na(flow.sumT1) & flow.sumT1>0), aes(x = log.ros.area, y = flow.sumT1))+
  #geom_jitter(height = .05)+
  geom_point(alpha = 0.1) +
  geom_line(data = subset(pred.dat.output.n, winter.mean.temp == -1), aes(x = log.ros.area, y = noflowers), color = "#323697", size = 1.5) +
  geom_line(data = subset(pred.dat.output.n, winter.mean.temp == 1), aes(x = log.ros.area, y = noflowers), color = "#f2623f", size = 1.5) +
  geom_line(data = subset(pred.dat.output.n, winter.mean.temp == 0), aes(x = log.ros.area, y = noflowers), color = "#94c8e0", size = 1.5) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+
  scale_y_continuous(n.breaks = 8) +
  labs(x = "log(Rosette Area) in t", y = "Flowers in t+1")+
    theme(axis.line = element_line(colour = 'black', linewidth = 1.1), text = element_text(size = 20)))

poisson
#ggsave(plot = poisson, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/2no.flowers winter temp.fig.png", width = 5, height = 5, dpi = 300)

```

```{r put all of them together?}

(others <- (survival | pflow | poisson)+plot_annotation(tag_levels = 'A'))
(all <- together/(survival +pflow + poisson) + plot_layout(guides = "collect", axis_titles = "collect") + plot_annotation(tag_levels = list(c("A", "", "", "B", "C", "D")))) 


ggsave(plot = all, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/all2.png", width = 15, height = 10, dpi = 300)

ggsave(plot = others, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/vr april 3.png", width = 15, height = 8, dpi = 300)
```



```{r}
#saving AIc table
#write.csv(x = AIC.save, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/tables/climate VR AIC/all_AIC.csv")

```


#no.seeds
partitioning out successful seed set
(1) probability of flowering (above)
(2) if you flower, how many do you make (above)
(3) how many flowers get to make seeds - successful fruitset
(4) if you make seeds, how many make seeds - 

```{r}
# If you make seeds, how many do you make?
#if you make seeds, how many do you make
#Now, make a model for number of seeds produced:
#first some graphs

  
ggplot(subset(primula, total.seeds >0), aes(x = log.ros.area, y = total.seeds, color = trt))+
  geom_point()+
  geom_smooth(method="glm", method.args=list(family="poisson"), se = F)+
  facet_wrap(~year)
ggplot(subset(primula, total.seeds >0), aes(x = log.ros.area, y = total.seeds))+
  geom_point()+
  geom_smooth(method="glm", method.args=list(family="poisson"), se = F)+
  facet_wrap(~trt)
ggplot(subset(primula, total.seeds >0), aes(x = log.ros.area, y = total.seeds, color = trt))+
  geom_point()+
  geom_smooth(method="glm", method.args=list(family="poisson"), se = F)

  
ggplot(subset(primula, total.seeds >0), aes(x = log.ros.area, y = percapseeds, color = trt))+
  geom_point()+
  geom_smooth(method="glm", method.args=list(family="poisson"), se = F)+
  facet_wrap(~year)
ggplot(subset(primula, total.seeds >0), aes(x = log.ros.area, y = percapseeds))+
  geom_point()+
  geom_smooth(method="glm", method.args=list(family="poisson"), se = F)+
  facet_wrap(~trt)
ggplot(subset(primula, total.seeds >0), aes(x = log.ros.area, y = percapseeds, color = trt))+
  geom_point()+
  geom_smooth(method="glm", method.args=list(family="poisson"), se = F)
```


```{r}

#is it size dependent?

seed <- glmer(total.seeds~1+(1|plot), data = subset(primula, total.seeds >0), family = "poisson")
seed1 <- glmer(total.seeds~log.ros.area + (1|year) + (1|plot), data = subset(primula, total.seeds >0), family = "poisson")
seed2  <- glmer(total.seeds~log.ros.area+trt + (1|year) + (1|plot), data = subset(primula, total.seeds >0), family = "poisson")
seed3  <- glmer(total.seeds~log.ros.area*trt + (1|year)+ (1|plot), data = subset(primula, total.seeds >0), family = "poisson")

#these are for per capita
cap <- glmer(percapseeds~1+(1|plot), data = subset(primula, total.seeds >0), family = "poisson")
cap1 <- glmer(percapseeds~log.ros.area + (1|year) + (1|plot), data = subset(primula, total.seeds >0), family = "poisson")
cap2  <- glmer(percapseeds~log.ros.area+trt + (1|year) + (1|plot), data = subset(primula, total.seeds >0), family = "poisson")
cap3  <- glmer(percapseeds~log.ros.area*trt + (1|year)+ (1|plot), data = subset(primula, total.seeds >0), family = "poisson")
cap4  <- glmer(percapseeds~trt + (1|year)+ (1|plot), data = subset(primula, total.seeds >0), family = "poisson")


capsules <- mget(ls(pattern = "^cap")) #make a list of all of those models that start with gm (^ means start with)
capsule_AICc<-aictab(cand.set = capsules, modnames = NULL,second.ord=TRUE,nobs=NULL,sort=TRUE)
summary(cap4)

pred.dat <- expand.grid(trt = c("control", "irrigated", "drought"))
pred <- predict(cap4, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred <- as.data.frame(pred)
pred <- cbind(pred.dat, pred)
#flowers in drought plots make 6 seeds, control make 11, irrigated make 13

ggplot(data = subset(primula, total.seeds >0), aes(x=trt, y=percapseeds, color = trt))+
  geom_boxplot()

# here's number of seeds per plant made on average
seeds <- mean(primula$total.seeds, na.rm = T) #36? seems fine for now
```

```{r include = F, eval = FALSE}
# ok, for the seed addition graph, I want to make it into one:
### I want to have one set of lines for 2021's data, and then one line for everything together
### same for the dots, I want the 2021 dots to be hollow, the rest can be filled

#noseeds3
pred.seeds.year <- expand.grid(log.ros.area = seq(3, 6, by = .1), trt = c("control", "drought", "irrigated"), year = c("2021", "2022", "2023")) %>% 
      mutate(pred_values = predict(seed3, newdata = ., type = "response", re.form= ~(1|year)))

#no.seeds <- #
  ggplot(data = subset(primula, total.seeds >0), aes(x=log.ros.area, y=total.seeds, color = trt, fill = year))+
  geom_jitter(height = 0.025, size = 2, alpha= 0.5) +
  geom_line(data = subset(pred.seeds.year, year == "2021" & trt == "drought" & log.ros.area < 5.5), aes(x = log.ros.area, y = pred_values), color = Z[5], linewidth = 1.25, linetype = "solid") +
    geom_line(data = subset(pred.seeds.year, year == "2021" & trt == "irrigated"), aes(x = log.ros.area, y = pred_values), color = Z[1], linewidth = 1.25, linetype = "solid") +
    geom_line(data = subset(pred.seeds.year, year == "2021" & trt == "control" & log.ros.area < 5.6), aes(x = log.ros.area, y = pred_values), color = Z[3], linewidth = 1.25, linetype = "solid") +
      geom_line(data = subset(pred.seeds.year, year == "2022" & trt == "drought" & log.ros.area < 5.5), aes(x = log.ros.area, y = pred_values), color = Z[5], linewidth = 1.25, linetype = "dashed") +
    geom_line(data = subset(pred.seeds.year, year == "2022" & trt == "irrigated"), aes(x = log.ros.area, y = pred_values), color = Z[1], linewidth = 1.25, linetype = "dashed") +
    geom_line(data = subset(pred.seeds.year, year == "2022" & trt == "control" & log.ros.area < 5.6), aes(x = log.ros.area, y = pred_values), color = Z[3], linewidth = 1.25, linetype = "dashed") +
          geom_line(data = subset(pred.seeds.year, year == "2023" & trt == "drought" & log.ros.area < 5.5), aes(x = log.ros.area, y = pred_values), color = Z[5], linewidth = 1.25, linetype = "dotted") +
    geom_line(data = subset(pred.seeds.year, year == "2023" & trt == "irrigated"), aes(x = log.ros.area, y = pred_values), color = Z[1], linewidth = 1.25, linetype = "dotted") +
    geom_line(data = subset(pred.seeds, year == "2023" & trt == "control" & log.ros.area < 5.6), aes(x = log.ros.area, y = pred_values), color = Z[3], linewidth = 1.25, linetype = "dotted") +
  theme(axis.line = element_line(colour = 'black', linewidth = 1.1), text = element_text(size = 15))+ 
    scale_color_manual(values = c("irrigated" = Z[1],"control" = Z[3], "drought" = Z[5]))

    
    
  geom_line(data = pred.irrigated, aes(x = log.ros.area, y = pred.irrigated), color = Z[1], linewidth = 1.25) + 
  geom_line(data = pred.control, aes(x = log.ros.area, y = pred.control), color = Z[3], linewidth = 1.25) + 
  labs(x = "log(Rosette Area) in t", y = "Total seeds in t") 
poster <- 
  ggplot(data = subset(primula, total.seeds >0), aes(x=log.ros.area, y=total.seeds, color = trt))+
  geom_jitter(height = 0.025, size = 2, alpha= 0.5) +
  geom_line(data = pred.drought, aes(x = log.ros.area, y = pred.drought), color = Z[5], linewidth = 2) +
  geom_line(data = pred.irrigated, aes(x = log.ros.area, y = pred.irrigated), color = Z[1], linewidth = 2) + 
  geom_line(data = pred.control, aes(x = log.ros.area, y = pred.control), color = Z[3], linewidth = 2) + 
  labs(x = "Plant size", y = "Total seeds") +
  theme(axis.line = element_line(colour = 'black', linewidth = 1.1), text = element_text(size = 20))+ 
    scale_color_manual(values = c("irrigated" = Z[1],"control" = Z[3], "drought" = Z[5]))+
    theme(legend.position="none")
poster
no.seeds
#ggsave(plot = no.seeds, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/poisson.seedproduction.png", width = 5, height = 5, dpi = 300)

#ggsave(plot = poster, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/climate vital rate selection/poster.seedproduction.png", width = 6, height = 6, dpi = 300)

```
