---
title: "Primula Clipping Experiment"
author: "JL"
date: "2/13/2023"
output:
  word_document: default
  html_document: default
---

To do:
- 6/26 update: Met with Jenn, we came up with more ideas:
  - let's take out the vegetative plants, bc we think theyre doing weird things
  - there are more interactions that I didnt try before - we also think that the 
  stepwise selection is wrong, theyre not nested models so it wont work
  - change clipping trt to ln(seeds) and log(fruits produced) - a better measure of reproductive effort! 
  We will have to treat clipping and abortion the same way, which is maybe questionable...
  - ^we can compare which one is better
  - Throw in soil moisture in case that fits better - daily average soil moisutre
  April-end of May

```{r, include = FALSE}
#packages:
#read
library(tidyverse)
library(lubridate)
library(AICcmodavg)
library(lme4)
library(car)
library(wesanderson) # for colors
library(lmerTest)

theme_set(theme_classic()) #for ggplot
FF <- wes_palettes$FantasticFox1
Z <- wes_palettes$Zissou1
R <- wes_palettes$Royal2
I <- wes_palettes$IsleofDogs1
```

```{r}
#read in data, make df's
# Add in demography data:
source("../scripts/dode_allyears_cleaned.R")

#add in tags in clipping experiment
clip <- read.csv("../data/2021_Primula_Clipping.csv")
clip <- clip %>% 
  select(1:8, -c(coor, date.of.clipping)) %>% 
  mutate(tag = as.character(tag),
         plot = as.character(plot),
         initial.flower = no.flowers.at.start +no.buds.at.start)

#adding in soil moisture data
sm <- read.csv("C:/Users/Jenna/Dropbox/Williams' Lab/Students/Jenna/loggerdata/cleaned.data/SM_AprilMayavg_allyears.csv")
sm <- sm %>% mutate(plot = as.character(plot),
                    year = as.character(year))

#add in number of seeds made
seeds21 <- read.csv("C:/Users/Jenna/Dropbox/Williams' Lab/Cowichan IDE/Cowichan_DemographyData/Dodecatheon/2021_Dodecatheon_Seed_Counts.csv")

#In 2021, which flowers made it to being a capsule?
#seeds21 <- subset(seeds21, tag != "1556") # not an experiment plant
#seeds21 <- subset(seeds21, tag != 1998) # not an experiment plant
#seeds21 <- subset(seeds21, tag != 1813)
seeds21 <- seeds21 %>% 
  mutate(pseeds = if_else(no.seeds > 0, 1, 0),
         tag = as.character(tag),
         plot = as.character(plot))
seeds21$pseeds[is.na(seeds21$pseeds)] <- 1 #assuming the plants where we couldn't count capsules separately had all their capsules contribute to seed total


cap <- seeds21 %>% group_by(tag, plot) %>% 
  dplyr::summarize(no.success.cap = sum(pseeds),
            total.seeds = sum(no.seeds))
cap$total.seeds[cap$tag == 1556] <- 29
cap$total.seeds[cap$tag == 1988] <- 58
cap$total.seeds[cap$tag == 1988] <- 58
cap$total.seeds[cap$tag == 282] <- 50
cap$total.seeds[cap$tag == 494] <-98

#adding cap to the clip df

clip <- full_join(clip, cap) %>% 
  mutate(total.seeds = if_else(no.success.cap == 0, 0, total.seeds))
remove(cap)
clip$no.success.cap[is.na(clip$no.success.cap)] <- 0
clip$initial.flower[clip$tag == 1490] <- 6
clip$initial.flower[clip$tag == 5769] <- 5
clip$initial.flower[clip$tag == 962] <- 6
clip$initial.flower[clip$tag == 5746] <- 5
clip$no.success.cap[clip$tag == 540] <- 4
clip$no.success.cap[clip$tag == 693] <- 2



############################################################################
#add in clipping experiment treatments

clip <-  left_join(clip, Dodecatheon, by = c("tag", "plot")) %>% 
  filter(year == 2021) %>% 
  mutate(fruitset = no.success.cap/initial.flower) %>% 
  mutate(pflower = as.factor(pflower),
         rgr = log.ros.areaT1-log.ros.area) #calc relative growth rate

# these are all of the tags in the clipping experiment for 2021 and 2022
#add soil moisture:
clip <- left_join(clip, sm)

#subsetting - get rid of 12 and 14 (only 3 observations per plot - maybe this will help?)
clip <- clip %>% filter(plot != "12") %>% 
  filter(plot != "14")

#this is code to get the vegetative plants back in - unchecked for now
# ###
# # what sizes are plants in 2021 to 2022
# Dodecatheon.21 <- Dodecatheon %>% 
#   filter(year == "2021")
# #of the plants that flowered in 2021, what was their min size? it doesnt look like I need to set a max size
# ggplot(Dodecatheon.21, aes(log.ros.area, log.ros.areaT1, color = pflower)) +
#   geom_jitter()+
#   facet_wrap(~trt)
# ggplot(subset(Dodecatheon.21, !is.na(pflower)), aes(log.ros.area))+
#   geom_histogram()+
#   facet_wrap(pflower~trt)
# min <- Dodecatheon.21 %>% 
#   group_by(pflower, trt) %>% 
#   summarize(min.size = min(log.ros.area, na.rm = TRUE))
# clip2 <- Dodecatheon.21 %>% 
#   filter(log.ros.area > 2) %>% 
#   mutate(pflower = as.factor(pflower))
# join <-  left_join(clip2, clip)
# join <- join %>% 
#   #eft_join(join,sm, by = c("trt", "plot", "year")) %>% 
#   mutate(treatment = if_else(is.na(treatment) & pflower == 0, "veg", if_else(is.na(treatment) & pflower == 1, "flowernt", treatment),  treatment),
#          rgr = log.ros.areaT1-log.ros.area)
# 
# remove(sm, clip2, Dodecatheon, min, Dodecatheon.21)
# 
# #non experiment plants that flowered:
# no.exp <- read.csv("/Users/Jenna/Dropbox/Williams' Lab/Cowichan IDE/Cowichan_DemographyData/Dodecatheon/2021_Dodecatheon_Resurveys.csv", header=T)
# no.exp <- no.exp %>% 
#   filter(!is.na(pseeds)) %>% 
#   dplyr::rename(fruitset1 = pseeds) %>% 
#   select(c(plot, tag, fruitset1)) %>% 
#   mutate(plot = as.character(plot),
#          tag = as.character(tag))


#making a decision here that I may need to change: setting pseeds = fruitset (ie assuming that for these plants, if you made seeds, all of your flowers made seeds) - I have the data to check this, but will go check this later

clip <- clip %>% 
  mutate(log.cap = log(no.success.cap + 1), #because there are zeros 
          total.seeds = if_else(fruitset == 0, 0, total.seeds),
          pseeds = if_else(total.seeds > 0, 1, 0),
          log.total.seeds = log(total.seeds + 1), #because there are zeros 
         psurvivalT1 = if_else(is.na(psurvivalT1), 0, psurvivalT1))
clip <- clip %>%
  select(-c(no.flowers.at.start, no.buds.at.start, tag.pulled, problem.tag, toothpick, lv.length))


#clip.sub filtered out the plots with very few observations

```

```{r}
ggplot(clip, aes(x = log.ros.area, y = log.ros.areaT1))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  geom_abline(slope=1, intercept=0)+
  facet_wrap(~plot)
ggplot(clip, aes(x = log.ros.area, y = pflowerT1))+
  geom_point()+
  geom_smooth(method = "glm", method.args = list(family = binomial), se = F)+  
  geom_abline(slope=1, intercept=0)+
  facet_wrap(~plot)
```


#Fig 2:
Boxplot for number of seeds made across clipping treatment

```{r}
no.seeds.boxplot.trt <- ggplot(subset(clip, !is.na(treatment)), aes(treatment, log.total.seeds))+
  geom_boxplot(aes(color = trt))+
  facet_wrap(~trt)+
  scale_color_manual(values = c(Z[3], Z[5], Z[1]))+
  labs(y = "Log(total seeds)", x = "Number of flowers clipped")+
  theme(legend.position = "none")
no.seeds.boxplot.trt
ggsave(plot = no.seeds.boxplot.trt, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/clipping experiment/round 2/no.seeds.boxplot.trt.png", width = 6, height = 6, dpi = 300)

no.seeds.boxplot <- ggplot(subset(clip, !is.na(treatment)), aes(treatment, log.total.seeds))+
  geom_boxplot()+
  scale_color_manual(values = c(Z[3], Z[5], Z[1]))+
  labs(y = "Log(total seeds)", x = "Number of flowers clipped")
no.seeds.boxplot
ggsave(plot = no.seeds.boxplot, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/clipping experiment/round 2/no.seeds.boxplot.png", width = 6, height = 6, dpi = 300)
```


#These are the vital rate models we want to build:

```{r growth model selection}
growth.01 <- lmer(log.ros.areaT1 ~ log.ros.area +(1|plot), data = clip, REML = F)
growth.02 <- lmer(log.ros.areaT1 ~ log.ros.area*trt +(1|plot), data = clip, REML= F)
growth.03 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + log.total.seeds + (1|plot), data = clip, REML= F)
growth.04 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + log.total.seeds + trt:log.total.seeds + log.ros.area:trt + (1|plot), data = clip, REML= F)
growth.05 <- lmer(log.ros.areaT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + log.ros.area:trt + log.ros.area:log.total.seeds:trt + (1|plot), data = clip, REML= F)

growth.06 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + log.cap + (1|plot), data = clip, REML= F)
growth.07 <- lmer(log.ros.areaT1 ~ log.ros.area + trt + log.cap + trt:log.cap + log.ros.area:trt + (1|plot), data = clip, REML= F)
growth.08 <- lmer(log.ros.areaT1 ~ log.ros.area + log.cap + trt + log.cap:trt + log.ros.area:log.cap + log.ros.area:trt + log.ros.area:log.total.seeds:trt + (1|plot), data = clip, REML= F)

#add in SM data for fun
growth.09 <- lmer(log.ros.areaT1 ~ log.ros.area*sm_avg +(1|plot), data = clip, REML= F)
growth.10 <- lmer(log.ros.areaT1 ~ log.ros.area + sm_avg + log.total.seeds + (1|plot), data = clip, REML= F)
growth.11 <- lmer(log.ros.areaT1 ~ log.ros.area + sm_avg + log.total.seeds + sm_avg:log.total.seeds + log.ros.area:sm_avg + (1|plot), data = clip, REML= F)
growth.12 <- lmer(log.ros.areaT1 ~ log.ros.area + log.total.seeds + sm_avg + log.total.seeds:sm_avg + log.ros.area:log.total.seeds + log.ros.area:sm_avg + log.ros.area:log.total.seeds:sm_avg + (1|plot), data = clip, REML= F)

growth.13 <- lmer(log.ros.areaT1 ~ log.ros.area + sm_avg + log.cap + (1|plot), data = clip, REML= F)
growth.14 <- lmer(log.ros.areaT1 ~ log.ros.area + sm_avg + log.cap + sm_avg:log.cap + log.ros.area:sm_avg + (1|plot), data = clip, REML= F)
growth.15 <- lmer(log.ros.areaT1 ~ log.ros.area + log.cap + sm_avg + log.cap:sm_avg + log.ros.area:log.cap + log.ros.area:sm_avg + log.ros.area:log.total.seeds:sm_avg + (1|plot), data = clip, REML= F)
growth.16 <- lmer(log.ros.areaT1 ~ log.ros.area + log.total.seeds + (1|plot), data = clip, REML= F)
growth.17 <- lmer(log.ros.areaT1 ~ log.ros.area*log.total.seeds + (1|plot), data = clip, REML= F)
growth.18 <- lmer(log.ros.areaT1 ~ log.ros.area + log.cap + (1|plot), data = clip, REML= F)
growth.19 <- lmer(log.ros.areaT1 ~ log.ros.area*log.cap + (1|plot), data = clip, REML= F)

model.names = c("log(size)", 
                "log(size)*IDE", 
                "log(size) + IDE + log(total seeds)", 
                "log(size) + IDE + log(total seeds) + IDE:log(total seeds) + log(size):IDE",
                "log(size) + log(total seeds) + IDE + log(total seeds):IDE + log(size):log(total seeds) + log(size):IDE + log(size):log(total seeds):IDE",
                "log(size) + IDE + log(total capsules)",
                "log(size) + IDE + log(total capsules) + IDE:log(total capsules) + log(size):IDE",
                "log(size) + log(total capsules) + IDE + log(total capsules):IDE + log(size):log(total capsules) + log(size):IDE + log(size):log(total seeds):IDE",
                "log(size)*soil moisture",
                "log(size) + soil moisture + log(total seeds)",
                "log(size) + soil moisture + log(total seeds) + soil moisture:log(total seeds) + log(size):soil moisture",
                "log(size) + log(total seeds) + soil moisture + log(total seeds):soil moisture + log(size):log(total seeds) + log(size):soil moisture + log(size):log(total seeds):soil moisture",
                "log(size) + soil moisture + log(total capsules)",
                "log(size) + soil moisture + log(total capsules) + soil moisture:log(total capsules) + log(size):soil moisture",
                "log(size) + log(total capsules) + soil moisture + log(total capsules):soil moisture + log(size):log(total capsules) + log(size):soil moisture + log(size):log(total seeds):soil moisture",
                "log(size) + log(total seeds)",
                "log(size)*log(total seeds)",
                "log(size) + log(total capsules)",
                "log(size)*log(total capsules)")

gr.mods <- mget(ls(pattern = "growth")) #make a list of all of those models that start with gm (^ means start with)
gr_AICc<-aictab(cand.set = gr.mods, modnames = model.names,second.ord=TRUE,nobs=NULL,sort=TRUE)
#test<-aictab(cand.set = gr.mods, modnames = NULL,second.ord=TRUE,nobs=NULL,sort=TRUE)
gr.AIC <- as.data.frame(gr_AICc)
#write.csv(x = gr.AIC, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/tables/clipping experiment/growth AIC table.csv")


summary(growth.16)
#rm(list = ls()[grepl("growth", ls())]) #removes these models
```


```{r growth best fit model log.ros.area + log.total.seeds}
#create df with all possible x values
#this is for model without an interaction
pred.dat <-  expand.grid(log.ros.area = seq(2, 5.5, by = .1), log.total.seeds = seq(0, 5.3, by = .1))
pred.output <- predict(growth.16, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.output <- as.data.frame(pred.output)
pred.dat.output <- cbind(pred.dat, pred.output) %>% 
  rename(log.ros.areaT1 = pred.output)

#graph it
growth <- ggplot(clip, aes(x = log.ros.area, y = log.ros.areaT1))+
  geom_abline(slope=1, intercept = 0, linetype = 2, color= "grey", size = 1)+
  geom_point()+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 5), aes(x = log.ros.area, y = log.ros.areaT1), color = "darkorchid4")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 4), aes(x = log.ros.area, y = log.ros.areaT1), color = "darkorchid3")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 3), aes(x = log.ros.area, y = log.ros.areaT1), color = "darkorchid2")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 2), aes(x = log.ros.area, y = log.ros.areaT1), color = "darkorchid1")+
  geom_line(data = subset(pred.dat.output,  log.total.seeds == 1), aes(x = log.ros.area, y = log.ros.areaT1), color = "violet")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = "grey")+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 6))+
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+
  labs(x = "log(Rosette Area) in 2021", y = "log(Rosette Area) in 2022")
growth
#ggsave(plot = growth, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/clipping experiment/round 2/growth.png", width = 6, height = 6, dpi = 300)
```

```{r growth figures - 2nd lowest AIC - log.ros.area + sm_avg + log.total.seeds}
#create df with all possible x values
#this is for model without an interaction
pred.dat <-  expand.grid(log.ros.area = seq(2, 5.5, by = .1), sm_avg = seq(.1, .25, by = .01), log.total.seeds = seq(0, 5.3, by = .1))
pred.output <- predict(growth.10, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.output <- as.data.frame(pred.output)
pred.dat.output <- cbind(pred.dat, pred.output) %>% 
  rename(log.ros.areaT1 = pred.output)

#graph it
ggplot(clip, aes(x = log.ros.area, y = log.ros.areaT1))+
  geom_point()+
  geom_line(data = subset(pred.dat.output, sm_avg == .25 & log.total.seeds == 5.3), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[1], size = 1)+
  geom_line(data = subset(pred.dat.output, sm_avg == .13 & log.total.seeds == 5.3), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[3], size = 1)+
  geom_line(data = subset(pred.dat.output, sm_avg == .1 & log.total.seeds == 5.3), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[5], size = 1)+
  geom_line(data = subset(pred.dat.output, sm_avg == .25 & log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1),  linetype = "dashed", color = Z[1])+
  geom_line(data = subset(pred.dat.output, sm_avg == .13 & log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[3], linetype = "dashed", size = 1)+
  geom_line(data = subset(pred.dat.output, sm_avg == .1 & log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[5], linetype = "dashed", size = 1)+
    geom_abline(slope=1, intercept = 0, linetype = 2, color= "grey", size = 1)+
    scale_y_continuous(expand = c(0, 0), limits = c(0, 6))+
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+
  labs(x = "log(Rosette Area) in 2021", y = "log(Rosette Area) in 2022")

#these seem kind of weird - I think the interaction may make more sense
```


```{r growth figure 3 - log.ros.area + trt + log.total.seeds, include=FALSE}
#create df with all possible x values
#this is for model without an interaction
# pred.dat <-  expand.grid(log.ros.area = seq(2, 5.5, by = .1), trt = c("irrigated", "control", "drought"), log.total.seeds = seq(0, 5.3, by = .1))
# pred.output <- predict(growth.3, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
# pred.output <- as.data.frame(pred.output)
# pred.dat.output <- cbind(pred.dat, pred.output) %>% 
#   rename(log.ros.areaT1 = pred.output)
# 
# #graph it
# ggplot(clip, aes(x = log.ros.area, y = log.ros.areaT1))+
#   geom_point()+
#   geom_line(data = subset(pred.dat.output, trt == "irrigated" & log.total.seeds == 5.3), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[1])+
#   geom_line(data = subset(pred.dat.output,  trt == "control" & log.total.seeds == 5.3), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[3], size = 1)+
#   geom_line(data = subset(pred.dat.output, trt == "drought" & log.total.seeds == 5.3), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[5], size = 1)+
#   geom_line(data = subset(pred.dat.output,  trt == "irrigated" & log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1),  linetype = "dashed", color = Z[1])+
#   geom_line(data = subset(pred.dat.output, trt == "control" & log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[3], linetype = "dashed", size = 1)+
#   geom_line(data = subset(pred.dat.output, trt == "drought" & log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[5], linetype = "dashed", size = 1)+
#       geom_abline(slope=1, intercept = 0, linetype = 2, color= "grey", size = 1)+
#     scale_y_continuous(expand = c(0, 0), limits = c(0, 6))+
#   scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+
#   labs(x = "log(Rosette Area) in 2021", y = "log(Rosette Area) in 2022")
# #why would drought grow more? but plants that make seeds are smaller than plants that make seeds! so that's something
```
```{r pflower model selection}
pf.01 <- glmer(pflowerT1 ~ log.ros.area +(1|plot), data = clip, family = "binomial")
pf.02 <- glmer(pflowerT1 ~ log.ros.area*trt +(1|plot), data = clip, family = "binomial")
pf.03 <- glmer(pflowerT1 ~ log.ros.area + trt + log.total.seeds + (1|plot), data = clip, family = "binomial")
pf.04 <- glmer(pflowerT1 ~ log.ros.area + trt + log.total.seeds + trt:log.total.seeds + log.ros.area:trt + (1|plot), data = clip, family = "binomial")
pf.05 <- glmer(pflowerT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + log.ros.area:trt + log.ros.area:log.total.seeds:trt + (1|plot), data = clip, family = "binomial")

pf.06 <- glmer(pflowerT1 ~ log.ros.area + trt + log.cap + (1|plot), data = clip, family = "binomial")
pf.07 <- glmer(pflowerT1 ~ log.ros.area + trt + log.cap + trt:log.cap + log.ros.area:trt + (1|plot), data = clip, family = "binomial")
pf.08 <- glmer(pflowerT1 ~ log.ros.area + log.cap + trt + log.cap:trt + log.ros.area:log.cap + log.ros.area:trt + log.ros.area:log.total.seeds:trt + (1|plot), data = clip, family = "binomial")

pf.09 <- glmer(pflowerT1 ~ log.ros.area*sm_avg +(1|plot), data = clip, family = "binomial")
pf.10 <- glmer(pflowerT1 ~ log.ros.area + sm_avg + log.total.seeds + (1|plot), data = clip, family = "binomial")
pf.11 <- glmer(pflowerT1 ~ log.ros.area + sm_avg + log.total.seeds + sm_avg:log.total.seeds + log.ros.area:sm_avg + (1|plot), data = clip, family = "binomial")
pf.12 <- glmer(pflowerT1 ~ log.ros.area + log.total.seeds + sm_avg + log.total.seeds:sm_avg + log.ros.area:log.total.seeds + log.ros.area:sm_avg + log.ros.area:log.total.seeds:sm_avg + (1|plot), data = clip, family = "binomial")

pf.13 <- glmer(pflowerT1 ~ log.ros.area + sm_avg + log.cap + (1|plot), data = clip, family = "binomial")
pf.14 <- glmer(pflowerT1 ~ log.ros.area + sm_avg + log.cap + sm_avg:log.cap + log.ros.area:sm_avg + (1|plot), data = clip, family = "binomial")
pf.15 <- glmer(pflowerT1 ~ log.ros.area + log.cap + sm_avg + log.cap:sm_avg + log.ros.area:log.cap + log.ros.area:sm_avg + log.ros.area:log.total.seeds:sm_avg + (1|plot), data = clip, family = "binomial")

pf.16 <- glmer(pflowerT1 ~ log.ros.area + log.total.seeds +(1|plot), data = clip, family = "binomial")
pf.17 <- glmer(pflowerT1 ~ log.ros.area*log.total.seeds +(1|plot), data = clip, family = "binomial")
pf.18 <- glmer(pflowerT1 ~ log.ros.area + log.cap +(1|plot), data = clip, family = "binomial")
pf.19 <- glmer(pflowerT1 ~ log.ros.area*log.cap +(1|plot), data = clip, family = "binomial")

pflower <- mget(ls(pattern = "pf")) #make a list of all of those models that start with gm (^ means start with)
pflower_AICc<-aictab(cand.set = pflower, modnames = model.names,second.ord=TRUE,nobs=NULL,sort=TRUE)
pflower.AIC <- as.data.frame(pflower_AICc)

#write.csv(x = pflower.AIC, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/tables/clipping experiment/pflower AIC table.csv")
#rm(list = ls()[grepl("pflower", ls())]) #removes these models
summary(pf.16)
```

```{r pflower best fit model}
#create df with all possible x values
#this is for model without an interaction
pred.dat <-  expand.grid(log.ros.area = seq(2, 5.5, by = .1), log.total.seeds = seq(0, 5.3, by = .1))
pred.output <- predict(pf.16, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.output <- as.data.frame(pred.output)
pred.dat.output <- cbind(pred.dat, pred.output) %>% 
  rename(log.ros.areaT1 = pred.output)

pflower.fig <- ggplot(clip, aes(x = log.ros.area, y = pflowerT1))+
  geom_jitter(height = .01)+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 5), aes(x = log.ros.area, y = log.ros.areaT1), color = "darkorchid4")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 4), aes(x = log.ros.area, y = log.ros.areaT1), color = "darkorchid3")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 3), aes(x = log.ros.area, y = log.ros.areaT1), color = "darkorchid2")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 2), aes(x = log.ros.area, y = log.ros.areaT1), color = "darkorchid1")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 1), aes(x = log.ros.area, y = log.ros.areaT1), color = "violet")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = "grey")+
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+
  labs(x = "log(Rosette Area) in 2021", y = "Probability of Flowering in 2022")
pflower.fig

#ggsave(plot = pflower.fig, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/clipping experiment/round 2/pflower.png", width = 6, height = 6, dpi = 300)
```

```{r pflower fig 1 - pf.3}
#create df with all possible x values
#this is for model without an interaction
pred.dat <-  expand.grid(log.ros.area = seq(2, 5.5, by = .1), trt = c("irrigated", "control", "drought"), log.total.seeds = seq(0, 5.3, by = .1))
pred.output <- predict(pf.03, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.output <- as.data.frame(pred.output)
pred.dat.output <- cbind(pred.dat, pred.output) %>% 
  rename(log.ros.areaT1 = pred.output)

ggplot(clip, aes(x = log.ros.area, y = pflowerT1))+
  geom_point()+
  geom_line(data = subset(pred.dat.output, trt == "irrigated" & log.total.seeds == 5.3), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[1])+
  geom_line(data = subset(pred.dat.output,  trt == "control" & log.total.seeds == 5.3), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[3], size = 1)+
  geom_line(data = subset(pred.dat.output, trt == "drought" & log.total.seeds == 5.3), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[5], size = 1)+
  geom_line(data = subset(pred.dat.output,  trt == "irrigated" & log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1),  linetype = "dashed", color = Z[1])+
  geom_line(data = subset(pred.dat.output, trt == "control" & log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[3], linetype = "dashed", size = 1)+
  geom_line(data = subset(pred.dat.output, trt == "drought" & log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = Z[5], linetype = "dashed", size = 1)


```
```{r pflower fig 1 - pf.11 - this one wasnt singular}
#create df with all possible x values
#this is for model without an interaction
pred.dat <-  expand.grid(log.ros.area = seq(2, 5.5, by = .1), sm_avg = seq(.1, .25, by = .01), log.total.seeds = seq(0, 5.3, by = .1))
pred.output <- predict(pf.11, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.output <- as.data.frame(pred.output)
pred.dat.output <- cbind(pred.dat, pred.output) %>% 
  rename(log.ros.areaT1 = pred.output)

ggplot(clip, aes(x = log.ros.area, y = pflowerT1))+
  geom_point()+
  geom_line(data = subset(pred.dat.output, sm_avg == .25 & log.total.seeds == 5.3), aes(x = log.ros.area, y = log.ros.areaT1), color = "blue")+
  geom_line(data = subset(pred.dat.output,  sm_avg == .13 & log.total.seeds == 5.3), aes(x = log.ros.area, y = log.ros.areaT1), color = "grey", size = 1)+
  geom_line(data = subset(pred.dat.output, sm_avg == .1 & log.total.seeds == 5.3), aes(x = log.ros.area, y = log.ros.areaT1), color = "red", size = 1)+
  geom_line(data = subset(pred.dat.output,  sm_avg == .25 & log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1),  linetype = "dashed", color = "blue")+
  geom_line(data = subset(pred.dat.output, sm_avg == .13 & log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = "grey", linetype = "dashed", size = 1)+
  geom_line(data = subset(pred.dat.output, sm_avg == .1 & log.total.seeds == 0), aes(x = log.ros.area, y = log.ros.areaT1), color = "red", linetype = "dashed", size = 1)

#why are  plants that make more seeds more likely to flower the next year. What to do???
```

```{r poisson}
nof.01 <- glmer(no.flowersT1 ~ log.ros.area + (1|plot), data = clip, family = "poisson")
nof.02 <- glmer(no.flowersT1 ~ log.ros.area*trt + (1|plot), data = clip, family = "poisson")
nof.03 <- glmer(no.flowersT1 ~ log.ros.area + trt + log.total.seeds + (1|plot), data = clip, family = "poisson")
nof.04 <- glmer(no.flowersT1 ~ log.ros.area + trt + log.total.seeds + trt:log.total.seeds + log.ros.area:trt + (1|plot), data = clip, family = "poisson")
nof.05 <- glmer(no.flowersT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + log.ros.area:trt + log.ros.area:log.total.seeds:trt + (1|plot), data = clip, family = "poisson")

nof.06 <- glmer(no.flowersT1 ~ log.ros.area + trt + log.cap + (1|plot), data = clip, family = "poisson")
nof.07 <- glmer(no.flowersT1 ~ log.ros.area + trt + log.cap + trt:log.cap + log.ros.area:trt + (1|plot), data = clip, family = "poisson")
nof.08 <- glmer(no.flowersT1 ~ log.ros.area + log.cap + trt + log.cap:trt + log.ros.area:log.cap + log.ros.area:trt + log.ros.area:log.total.seeds:trt + (1|plot), data = clip, family = "poisson")

nof.09 <- glmer(no.flowersT1 ~ log.ros.area*sm_avg + (1|plot), data = clip, family = "poisson")
nof.10 <- glmer(no.flowersT1 ~ log.ros.area + sm_avg + log.total.seeds + (1|plot), data = clip, family = "poisson")
nof.11 <- glmer(no.flowersT1 ~ log.ros.area + sm_avg + log.total.seeds + sm_avg:log.total.seeds + log.ros.area:sm_avg + (1|plot), data = clip, family = "poisson")
nof.12 <- glmer(no.flowersT1 ~ log.ros.area + log.total.seeds + sm_avg + log.total.seeds:sm_avg + log.ros.area:log.total.seeds + log.ros.area:sm_avg + log.ros.area:log.total.seeds:sm_avg + (1|plot), data = clip, family = "poisson")

nof.13 <- glmer(no.flowersT1 ~ log.ros.area + sm_avg + log.cap + (1|plot), data = clip, family = "poisson")
nof.14 <- glmer(no.flowersT1 ~ log.ros.area + sm_avg + log.cap + sm_avg:log.cap + log.ros.area:sm_avg + (1|plot), data = clip, family = "poisson")
nof.15 <- glmer(no.flowersT1 ~ log.ros.area + log.cap + sm_avg + log.cap:sm_avg + log.ros.area:log.cap + log.ros.area:sm_avg + log.ros.area:log.total.seeds:sm_avg + (1|plot), data = clip, family = "poisson")
nof.16 <- glmer(no.flowersT1 ~ log.ros.area + log.total.seeds + (1|plot), data = clip, family = "poisson")
nof.17 <- glmer(no.flowersT1 ~ log.ros.area*log.total.seeds + (1|plot), data = clip, family = "poisson")
nof.18 <- glmer(no.flowersT1 ~ log.ros.area + log.cap + (1|plot), data = clip, family = "poisson")
nof.19 <- glmer(no.flowersT1 ~ log.ros.area*log.cap + (1|plot), data = clip, family = "poisson")


flowers <- mget(ls(pattern = "nof.")) #make a list of all of those models that start with gm (^ means start with)
flowers_AICc<-aictab(cand.set = flowers, modnames = model.names,second.ord=TRUE,nobs=NULL,sort=TRUE)
noflower.AIC <- as.data.frame(flowers_AICc)
#write.csv(x = noflower.AIC, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/tables/clipping experiment/no.flower AIC table.csv")
#rm(list = ls()[grepl("flowers", ls())]) #removes these models
summary(nof.16)
```

```{r poisson fig 1 - best fit, but singular! }
#create df with all possible x values
#this is for model without an interaction
pred.dat <-  expand.grid(log.ros.area = seq(2, 5.5, by = .1), log.total.seeds = seq(0, 5.3, by = .1))
pred.output <- predict(nof.16, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.output <- as.data.frame(pred.output)
pred.dat.output <- cbind(pred.dat, pred.output) %>% 
  rename(no.flowersT1 = pred.output)

no.flowers <- ggplot(clip, aes(x = log.ros.area, y = no.flowersT1))+
  geom_point()+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 5), aes(x = log.ros.area, y = no.flowersT1), color = "darkorchid4")+
  geom_line(data = subset(pred.dat.output,  log.total.seeds == 4), aes(x = log.ros.area, y = no.flowersT1), color = "darkorchid3")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 3), aes(x = log.ros.area, y = no.flowersT1), color = "darkorchid2")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 2), aes(x = log.ros.area, y = no.flowersT1), color = "darkorchid1")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 1), aes(x = log.ros.area, y = no.flowersT1), color = "violet")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 0), aes(x = log.ros.area, y = no.flowersT1), color = "grey")+
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+
  labs(x = "log(Rosette Area) in 2021", y = "No. flowers in 2022")

no.flowers
#ggsave(plot = no.flowers, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/clipping experiment/round 2/no.flower.png", width = 6, height = 6, dpi = 300)


#this seems reasonable...but is a singular fit!
```

```{r poisson fig 1 -int}
#create df with all possible x values
#this is for model without an interaction
pred.dat <-  expand.grid(log.ros.area = seq(2, 5.5, by = .1), log.total.seeds = seq(0, 5.3, by = .1))
pred.output <- predict(nof.17, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.output <- as.data.frame(pred.output)
pred.dat.output <- cbind(pred.dat, pred.output) %>% 
  rename(no.flowersT1 = pred.output)

no.flowers1 <- ggplot(clip, aes(x = log.ros.area, y = no.flowersT1))+
  geom_point()+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 5), aes(x = log.ros.area, y = no.flowersT1), color = "darkorchid4")+
  geom_line(data = subset(pred.dat.output,  log.total.seeds == 4), aes(x = log.ros.area, y = no.flowersT1), color = "darkorchid3")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 3), aes(x = log.ros.area, y = no.flowersT1), color = "darkorchid2")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 2), aes(x = log.ros.area, y = no.flowersT1), color = "darkorchid1")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 1), aes(x = log.ros.area, y = no.flowersT1), color = "violet")+
  geom_line(data = subset(pred.dat.output, log.total.seeds == 0), aes(x = log.ros.area, y = no.flowersT1), color = "grey")+
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+
  labs(x = "log(Rosette Area) in 2021", y = "No. flowers in 2022")

no.flowers1
#ggsave(plot = no.flowers1, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/clipping experiment/round 2/no.flower.png", width = 6, height = 6, dpi = 300)


#this seems reasonable...but is a singular fit!
```

```{r survival}
sur.01 <- glmer(psurvivalT1 ~ log.ros.area +(1|plot), data = clip, family = "binomial")
sur.02 <- glmer(psurvivalT1 ~ log.ros.area*trt +(1|plot), data = clip, family = "binomial")
sur.03 <- glmer(psurvivalT1 ~ log.ros.area + trt + log.total.seeds + (1|plot), data = clip, family = "binomial")
sur.04 <- glmer(psurvivalT1 ~ log.ros.area + trt + log.total.seeds + trt:log.total.seeds + log.ros.area:trt + (1|plot), data = clip, family = "binomial")
sur.05 <- glmer(psurvivalT1 ~ log.ros.area + log.total.seeds + trt + log.total.seeds:trt + log.ros.area:log.total.seeds + log.ros.area:trt + log.ros.area:log.total.seeds:trt + (1|plot), data = clip, family = "binomial")

sur.06 <- glmer(psurvivalT1 ~ log.ros.area + trt + log.cap + (1|plot), data = clip, family = "binomial")
sur.07 <- glmer(psurvivalT1 ~ log.ros.area + trt + log.cap + trt:log.cap + log.ros.area:trt + (1|plot), data = clip, family = "binomial")
sur.08 <- glmer(psurvivalT1 ~ log.ros.area + log.cap + trt + log.cap:trt + log.ros.area:log.cap + log.ros.area:trt + log.ros.area:log.total.seeds:trt + (1|plot), data = clip, family = "binomial")

sur.09 <- glmer(psurvivalT1 ~ log.ros.area*sm_avg +(1|plot), data = clip, family = "binomial")
sur.10 <- glmer(psurvivalT1 ~ log.ros.area + sm_avg + log.total.seeds + (1|plot), data = clip, family = "binomial")
sur.11 <- glmer(psurvivalT1 ~ log.ros.area + sm_avg + log.total.seeds + sm_avg:log.total.seeds + log.ros.area:sm_avg + (1|plot), data = clip, family = "binomial")
sur.12 <- glmer(psurvivalT1 ~ log.ros.area + log.total.seeds + sm_avg + log.total.seeds:sm_avg + log.ros.area:log.total.seeds + log.ros.area:sm_avg + log.ros.area:log.total.seeds:sm_avg + (1|plot), data = clip, family = "binomial")

sur.13 <- glmer(psurvivalT1 ~ log.ros.area + sm_avg + log.cap + (1|plot), data = clip, family = "binomial")
sur.14 <- glmer(psurvivalT1 ~ log.ros.area + sm_avg + log.cap + sm_avg:log.cap + log.ros.area:sm_avg + (1|plot), data = clip, family = "binomial")
sur.15 <- glmer(psurvivalT1 ~ log.ros.area + log.cap + sm_avg + log.cap:sm_avg + log.ros.area:log.cap + log.ros.area:sm_avg + log.ros.area:log.total.seeds:sm_avg + (1|plot), data = clip, family = "binomial")

sur.16 <- glmer(psurvivalT1 ~ log.ros.area + log.total.seeds + (1|plot), data = clip, family = "binomial")
sur.17 <- glmer(psurvivalT1 ~ log.ros.area*log.total.seeds + (1|plot), data = clip, family = "binomial")
sur.18 <- glmer(psurvivalT1 ~ log.ros.area + log.cap + (1|plot), data = clip, family = "binomial")
sur.19 <- glmer(psurvivalT1 ~ log.ros.area*log.cap +(1|plot), data = clip, family = "binomial")


survival <- mget(ls(pattern = "sur.")) #make a list of all of those models that start with gm (^ means start with)
survival_AICc<-aictab(cand.set = survival, modnames = model.names,second.ord=TRUE,nobs=NULL,sort=TRUE)
surv.AIC <- as.data.frame(survival_AICc)
#write.csv(x = surv.AIC, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/tables/clipping experiment/survival AIC table.csv")
#rm(list = ls()[grepl("sur", ls())]) #removes these models
#the "best" 2 models give weird warnigns so going with the null model with just size
```

```{r survival best fit }
#create df with all possible x values
#this is for model without an interaction
pred.dat <-  expand.grid(log.ros.area = seq(2, 5.5, by = .1))
pred.output <- predict(sur.01, newdata = pred.dat, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.output <- as.data.frame(pred.output)
pred.dat.output <- cbind(pred.dat, pred.output) %>% 
  rename(survT1 = pred.output)

survival <- ggplot(clip, aes(x = log.ros.area, y = psurvivalT1))+
  geom_point()+
  geom_line(data = pred.dat.output, aes(x = log.ros.area, y = survT1))+
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))+
  labs(x = "log(Rosette Area) in 2021", y = "Survival in 2022")
survival
#ggsave(plot = survival, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/clipping experiment/round 2/survival.png", width = 6, height = 6, dpi = 300)

```



#############################################################################################










```{r include = F, eval = FALSE}
################################################################################
# Plan B! 

# calculate relative growth rate - did plants that were clipped grow more or less than plants that weren't
clip %>% ggplot(aes(trt, rgr))+
  geom_boxplot()#+
  facet_wrap(~treatment)

m1 <- lmer(rgr~trt+ (1|plot), data = clip, REML = F)
anova(m1)
summary(m1)
#drought plants grew more than control plants! and irrigated grew less than control plants? hmm that seems weird. But no effect of clipping treatment on growth 
#
# to make sure these are the same size: only include plants that were above ground in 2022
# 
fnull <- glmer(pflowerT1 ~ 1 + (1|plot), data = subset(clip.sub, !is.na(rgr)), family = "binomial")
f1 <- glmer(pflowerT1 ~ rgr + (1|plot), data = subset(clip.sub, !is.na(rgr)), family = "binomial")
anova(fnull, f1, test="Chisq") #LTR test
#nope!

f2<- glmer(pflowerT1 ~ fruitset + (1|plot), data = subset(clip.sub, !is.na(rgr)), family = "binomial")
anova(fnull, f2, test="Chisq") #LTR test
#yep!

f3<- glmer(pflowerT1 ~ fruitset + rgr + (1|plot), data = subset(clip.sub, !is.na(rgr)), family = "binomial")
anova(f2, f3, test="Chisq") #LTR test
#nope adding rgr doesnt help

f4<- glmer(pflowerT1 ~ fruitset*rgr + (1|plot), data = subset(clip.sub, !is.na(rgr)), family = "binomial")
anova(f2, f4, test="Chisq") #LTR test
#nope

f5<- glmer(pflowerT1 ~ trt + (1|plot), data = subset(clip.sub, !is.na(rgr)), family = "binomial") #singular fit!
anova(fnull, f5, test="Chisq") #LTR test



```

```{r include = F, eval = FALSE}
#not using size in model - this may be weird..
#GROWTH

ggplot(clip.sub, aes(x = trt, y = log.ros.areaT1))+
  geom_boxplot()
ggplot(clip.sub, aes(x = plot, y = log.ros.areaT1, color = trt))+
  geom_boxplot()
ggplot(clip.sub, aes(x = treatment, y = log.ros.areaT1))+
  geom_boxplot()+
  facet_wrap(~trt)

#with random effects
gnull<- lmer(log.ros.areaT1 ~ trt +(1|plot), data = clip.sub, REML = F)
gnull1<- lmer(log.ros.areaT1 ~ treatment + (1|plot), data = clip.sub, REML= F)
gnull2<- lmer(log.ros.areaT1 ~ treatment + trt + (1|plot), data = clip.sub, REML= F)
anova(gnull, gnull2, test="Chisq") #this is LRT?
summary(gnull2)

```

```{r include = F, eval = FALSE}

#with random effects
gnull<- lmer(log.ros.areaT1 ~ trt +(1|plot), data = clip.sub, REML = F)
gnull1<- lmer(log.ros.areaT1 ~  fruitset*trt + (1|plot), data = clip.sub, REML= F)
anova(gnull, gnull1, test="Chisq") #this is LRT?
summary(gnull1)

fnull<- lmer(pflowerT1 ~ (1|plot), data = clip.sub, REML = F)
fnull1<- lmer(pflowerT1 ~ fruitset + (1|plot), data = clip.sub, REML= F)
fnull2<- lmer(pflowerT1 ~ treatment + trt + (1|plot), data = clip.sub, REML= F)
anova(fnull, fnull1, test="Chisq") #this is LRT?
summary(gnull2)
```


Maybe cost is in whether or not you flower, not how much effort you put into flowering?

Growth::
```{r growth,  include = F, eval = FALSE}
#######################################################################################

join <- join %>% 
  mutate(plot = as.factor(plot),
         trt = as.factor(trt),
         treatment = as.factor(treatment))

###
ggplot(clip, aes(x = log.ros.area, y = log.ros.areaT1))+
  geom_jitter()+
  geom_smooth(method = "lm", se = F)+
  geom_abline(slope=1, intercept=0)+
  facet_wrap(~treatment)
ggplot(join, aes(x = log.ros.area, y = log.ros.areaT1))+
  geom_jitter()+
  geom_smooth(method = "lm", se = F)+
  geom_abline(slope=1, intercept=0)+
  facet_wrap(trt~treatment)

#gnull.base <- lmer(log.ros.areaT1 ~ 1 + (1|plot), data = join, REML = F)
gnull<- lmer(log.ros.areaT1 ~ log.ros.area + (1|plot), data = join, REML = F)
#growth <- anova(gnull.base, gnull, test="Chisq") #this is LRT

#including size improves the model:

gnull1<- lmer(log.ros.areaT1 ~ log.ros.area + treatment + (1|plot), data = join, REML = F)
summary(gnull1)
growth <- anova(gnull, gnull1, test="Chisq") #this is LRT
growth #no cost on growth with just clipping treatment


gnull2<- lmer(log.ros.areaT1 ~ log.ros.area + trt + (1|plot), data = join, REML = F)
anova(gnull, gnull2, test="Chisq") #this is LRT
#nope!
growth_stat <- rbind(growth,growth1)
gnull2<- lmer(log.ros.areaT1 ~ log.ros.area+treatment*trt + (1|plot), data = join, REML= F)
anova(gnull, gnull2, test="Chisq") #this is LRT?
summary(gnull)

###
#how to get fruitset in here - cant use the vegetative plants here because they have fruitset  = NA
#run other models?
gnull.base <- lmer(log.ros.areaT1 ~ 1 + (1|plot), data = subset(join, !is.na(fruitset)), REML = F)
gnull<- lmer(log.ros.areaT1 ~ log.ros.area + (1|plot), data = subset(join, !is.na(fruitset)), REML = F)
anova(gnull.base, gnull, test="Chisq") #this is LRT


gnull1<- lmer(log.ros.areaT1 ~ log.ros.area + fruitset + (1|plot), data = subset(join, !is.na(fruitset)), REML = F)
anova(gnull, gnull1, test="Chisq") #this is LRT

gnull2<- lmer(log.ros.areaT1 ~ log.ros.area*fruitset + (1|plot), data = subset(join, !is.na(fruitset)), REML = F)
anova(gnull, gnull2, test="Chisq") #this is LRT


#no, doing it with fruitset doesnt help
#no cost on growth

###
# step package:
# https://search.r-project.org/CRAN/refmans/lmerTest/html/step.lmerModLmerTest.html
# backwards selection:
growth.full<- lmerTest::lmer(log.ros.areaT1 ~ log.ros.area*treatment*trt + (1|plot), data = join, REML= F)


step_fm <- lmerTest::step(growth.full,reduce.random=FALSE)
step_fm # Display elimination results
final_fm <- get_model(step_fm)

```

```{r  include = F, eval = FALSE}

#pflower:
ggplot(join, aes(x = log.ros.area, y = pflowerT1))+
  geom_jitter(height = .05)+
  geom_smooth(method = "glm", method.args = list(family = binomial), se = F)+
  facet_wrap(~treatment)
ggplot(join, aes(x = log.ros.area, y = pflowerT1))+
  geom_jitter(height = .05)+
  geom_smooth(method = "glm", method.args = list(family = binomial), se = F)+
  facet_wrap(~trt)
ggplot(join, aes(x = log.ros.area, y = pflowerT1))+
  geom_jitter(height = .05)+
  geom_smooth(method = "glm", method.args = list(family = binomial), se = F)+
  facet_wrap(treatment~trt,  ncol = 3)+
  labs(x = "Log(rosette area) in 2021", y = "Probability of flowering in 2022")

fnull <- glmer(pflowerT1 ~ log.ros.area + (1|plot), data = join, family = "binomial")
f1 <- glmer(pflowerT1 ~ log.ros.area + trt + (1|plot), data = join, family = "binomial")
anova(fnull, f1, test="Chisq") #LTR test
#nope

f2<- glmer(pflowerT1 ~ log.ros.area+treatment + (1|plot), data = join, family = "binomial")
anova(fnull, f2, test="Chisq") #LTR test
#yes, significant! But seems like it is mostly for veg vs the rest

f3<- glmer(pflowerT1 ~ log.ros.area + treatment*trt + (1|plot), data = join, family = "binomial")
anova(f2, f3, test="Chisq") #LTR test

summary(f2)

#what about adding fruitset? NOPE!
fnull <- glmer(pflowerT1 ~ log.ros.area + (1|plot), data = subset(join, !is.na(fruitset)), family = "binomial")
f1 <- glmer(pflowerT1 ~ log.ros.area + fruitset + (1|plot), data = subset(join, !is.na(fruitset)), family = "binomial")
anova(fnull, f1, test="Chisq")


```

```{r include = F, eval = FALSE}
#Survival
#pflower:
ggplot(subset(join, !is.na(psurvivalT1)), aes(x = log.ros.area, y = as.factor(psurvivalT1)))+
  geom_jitter(height = .05)+
  geom_smooth(method = "glm", method.args = list(family = binomial), se = F)+
  facet_wrap(~treatment)
ggplot(join, aes(x = log.ros.area, y = pflowerT1))+
  geom_jitter(height = .01)+
  geom_smooth(method = "glm", method.args = list(family = binomial), se = F)+
  facet_wrap(~trt)
ggplot(join, aes(x = log.ros.area, y = pflowerT1))+
  geom_jitter(height = .01)+
  geom_smooth(method = "glm", method.args = list(family = binomial), se = F)+
  facet_wrap(treatment~trt,  ncol = 3)+
  labs(x = "Log(rosette area) in 2021", y = "Probability of flowering in 2022")

s<- glmer(as.factor(psurvivalT1) ~ 1 + (1|plot), data = join, family = "binomial")
snull <- glmer(as.factor(psurvivalT1) ~ log.ros.area + (1|plot), data = join, family = "binomial")
anova(s, snull,test="Chisq") #LTR test

snull1 <- glmer(as.factor(psurvivalT1) ~  treatment + (1|plot), data = join, family = "binomial")
anova(s, snull1,test="Chisq") #LTR test

snull2 <- glmer(as.factor(psurvivalT1) ~  trt + (1|plot), data = join, family = "binomial")
anova(s, snull2,test="Chisq") #LTR test

snull3 <- glmer(as.factor(psurvivalT1) ~  trt+treatment + (1|plot), data = join, family = "binomial")
anova(s, snull3,test="Chisq") #LTR test

#doesnt converge
#snull4 <- glmer(as.factor(psurvivalT1) ~  trt*treatment + (1|plot), data = join, family = "binomial")
#anova(s, snull4,test="Chisq") #LTR test
```

#What to do about differential flowering success → what about 3 models

```{r include = F, eval = FALSE}
#Probability of flowering model…
fbase <- glmer(as.factor(pflowerT1) ~ 1 + (1|plot), data = join, family = "binomial")
fnull <- glmer(as.factor(pflowerT1) ~ log.ros.area + (1|plot), data = join, family = "binomial")
anova(fbase, fnull, test="Chisq") #LTR test

f1 <- glmer(as.factor(pflowerT1) ~ log.ros.area + treatment + (1|plot), data = join, family = "binomial")
anova(fnull, f1, test="Chisq") #LTR test

f1.1 <- glmer(as.factor(pflowerT1) ~ log.ros.area*treatment + (1|plot), data = join, family = "binomial")
anova(f1, f1.1, test="Chisq") #LTR test

#singular fit
#f2 <- glmer(as.factor(pflowerT1) ~ log.ros.area + trt + (1|plot), data = join, family = "binomial")
#anova(fnull, f2, test="Chisq") #LTR test
#great, this one is sig

f3 <- glmer(as.factor(pflowerT1) ~ log.ros.area*trt + (1|plot), data = join, family = "binomial")
anova(fnull, f3, test="Chisq") #LTR test

f4 <- glmer(as.factor(pflowerT1) ~ log.ros.area+trt+treatment + (1|plot), data = join, family = "binomial")
anova(f1, f4, test="Chisq") #LTR test
f5 <- glmer(as.factor(pflowerT1) ~ log.ros.area+trt*treatment + (1|plot), data = join, family = "binomial")
anova(f1, f5, test="Chisq") #LTR test

summary(f5)

```
```{r  include = F, eval = FALSE}
## make graph for that model:
# pflower av plots
pred.control<-  expand.grid(log.ros.area = seq(1, 5.25, by = .1), trt = "control")#this is making a set of data that the model will predict points for. size 0:6, 25th quarile of summer precip, and control plots! seq(0, 6, by = .1) is the same as 0:6 but smaller increments
pred.control2 <- predict(f2, newdata = pred.control, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
control.pflower <- as.data.frame(pred.control2)
pred.control <- cbind(pred.control, control.pflower)
#
pred.irrigated<-  expand.grid(log.ros.area = seq(1, 5.25, by = .1), trt = "irrigated")#this is making a set of data that the model will predict points for. size 0:6, 25th quarile of summer precip, and irrigated plots! seq(0, 6, by = .1) is the same as 0:6 but smaller increments
pred.irrigated2 <- predict(f2, newdata = pred.irrigated, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
irrigated.pflower <- as.data.frame(pred.irrigated2)
pred.irrigated <- cbind(pred.irrigated, irrigated.pflower)
#
pred.drought<-  expand.grid(log.ros.area = seq(1, 5.25, by = .1), trt = "drought")#this is making a set of data that the model will predict points for. size 0:6, 25th quarile of summer precip, and drought plots! seq(0, 6, by = .1) is the same as 0:6 but smaller increments
pred.drought2 <- predict(f2, newdata = pred.drought, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
drought.pflower <- as.data.frame(pred.drought2)
pred.drought <- cbind(pred.drought, drought.pflower)

ggplot(join, aes(x=log.ros.area, y=pflowerT1))+
  geom_jitter(height = 0.025, size = 1, alpha= 0.5) +
  geom_line(data = pred.drought, aes(x = log.ros.area, y = pred.drought2), color = Z[5], linewidth = 1) +
  geom_line(data = pred.irrigated, aes(x = log.ros.area, y = pred.irrigated2), color = Z[1], linewidth = 1) + 
  geom_line(data = pred.control, aes(x = log.ros.area, y = pred.control2), color = Z[3], linewidth = 1) + 
  labs(x = "log(Rosette Area) in 2021", y ="Probability of Flowering in 2022") +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 6))

summary(f2)


```


# fecundity - 

```{r  include = F, eval = FALSE}
flbase<- glmer(no.flowersT1 ~ 1 + (1|plot), data = subset(join, pflowerT1 == "1"), family = "poisson")
flnull <- glmer(no.flowersT1 ~ log.ros.area + (1|plot), data = subset(join, pflowerT1 == "1"), family = "poisson")
anova(flbase, flnull ,test="Chisq") #LTR test

fl1 <- glmer(no.flowersT1 ~ log.ros.area + treatment + (1|plot), data = subset(join, pflowerT1 == "1"), family = "poisson")
#nope, no converge

fl2 <- glmer(no.flowersT1 ~ log.ros.area + trt + (1|plot), data = subset(join, pflowerT1 == "1"), family = "poisson")
#nope singular fit!

summary(flnull)

flbase<- glm(no.flowersT1 ~ 1, data = subset(join, pflowerT1 == "1"), family = "poisson")
flnull <- glm(no.flowersT1 ~ log.ros.area, data = subset(join, pflowerT1 == "1"), family = "poisson")
anova(flbase, flnull ,test="Chisq") #LTR test

fl1 <- glm(no.flowersT1 ~ log.ros.area + treatment, data = subset(join, pflowerT1 == "1"), family = "poisson")
anova(flnull, fl1 ,test="Chisq")

fl2 <- glm(no.flowersT1 ~ log.ros.area + trt, data = subset(join, pflowerT1 == "1"), family = "poisson")
anova(flnull, fl2 ,test="Chisq")
anova(fl2)

##fruitset:
flbase<- glm(no.flowersT1 ~ 1, data = subset(join, !is.na(fruitset)), family = "poisson")
flnull <- glm(no.flowersT1 ~ log.ros.area, data = subset(join, !is.na(fruitset)), family = "poisson")
anova(flbase, flnull ,test="Chisq") #LTR test

fl1 <- glm(no.flowersT1 ~ log.ros.area+fruitset, data = subset(join, !is.na(fruitset)), family = "poisson")
anova(flnull, fl1 ,test="Chisq")

```


```{r include = FALSE, eval = FALSE}


#pflower:
ggplot(join, aes(x = log.ros.area, y = pflowerT1))+
  geom_point()+
  geom_smooth(method = "glm", method.args = list(family = binomial), se = F)+
  facet_wrap(~plot)
ggplot(join, aes(x = log.ros.area, y = pflowerT1))+
  geom_point(aes(size = fruitset))+
  geom_smooth(method = "glm", method.args = list(family = binomial), se = F)+
  facet_wrap(~trt)
ggplot(join, aes(x = log.ros.area, y = pflowerT1))+
  geom_point(aes(size = fruitset, color = trt))+
  geom_smooth(method = "glm", method.args = list(family = binomial), se = F)+
  facet_wrap(~treatment)
```

#Probability of successfully making seeds ~ treatment*size (data = plants that tried to flower)
```{r  include = F, eval = FALSE}
#of plants that tried to flower, what was their probability of making seeds:
seed <- glmer(as.factor(pseeds) ~ 1 + (1|plot), data = join, family = "binomial")
seed2 <- glmer(as.factor(pseeds) ~ log.ros.area + (1|plot), data = join, family = "binomial")
anova(seed, seed2, test="Chisq") #LTR test
#yes, bigger plants make more seeds

seed3 <- glmer(as.factor(pseeds) ~ log.ros.area + trt + (1|plot), data = join, family = "binomial")
#did not converge
```


#Seed production ~ treatment*size (data = plants that made seeds, this is Poisson)
```{r seed production}
#of plants that made seeds, did that differ between treatment?
noseeds<- glmer(total.seeds ~ 1 + (1|plot), data = subset(clip, pseeds ==1), family = "poisson")
noseeds1 <- glmer(as.numeric(total.seeds) ~ log.ros.area + (1|plot), data = subset(clip, pseeds == 1), family = "poisson")
anova(noseeds, noseeds1 ,test="Chisq") #LTR test
#yep its better

noseeds2 <- glmer(total.seeds ~ log.ros.area + trt + (1|plot), data = subset(clip, pseeds == 1), family = "poisson")
anova(noseeds1, noseeds2 ,test="Chisq") #LTR test
#yep

noseeds3 <- glmer(total.seeds ~ log.ros.area*trt + (1|plot), data = subset(clip, pseeds == 1), family = "poisson")
anova(noseeds2, noseeds3 ,test="Chisq") #LTR test
#yep!
summary(noseeds2)

summary(noseeds3)
#...it doesnt make sense to add clipping treatment, right? 

noseeds4 <- glmer(total.seeds ~ log.ros.area + treatment + (1|plot), data = subset(clip, pseeds == 1), family = "poisson")
anova(noseeds1, noseeds4 ,test="Chisq") #LTR test
summary(noseeds4)

noseeds5 <- glmer(total.seeds ~ log.ros.area + trt+treatment + (1|plot), data = subset(clip, pseeds == 1), family = "poisson")
anova(noseeds2, noseeds5 ,test="Chisq") #LTR test

noseeds6 <- glmer(total.seeds ~ log.ros.area + trt*treatment + (1|plot), data = subset(clip, pseeds == 1), family = "poisson")
anova(noseeds2, noseeds6 ,test="Chisq") #LTR test

```
Great, it's significant - now make a graph

```{r include = F, eval = FALSE}
ggplot(subset(clip, pseeds == 1), aes(log.ros.area, log.total.seeds))+
  geom_point()+
  geom_smooth(method="glm", method.args=list(family="poisson"), se = F)+
  facet_wrap(trt~treatment)+
  labs()
```

```{r include = F, eval = FALSE}
#noseeds3
pred.dat.control <-  expand.grid(log.ros.area = seq(3.25, 5.25, by = .1), trt = "control") #this is making a set of data that the model will predict points for. size 0:6, 25th quarile of summer precip seq(0, 6, by = .1) is the same as 0:6 but smaller increments
pred.control <- predict(noseeds3, newdata = pred.dat.control, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.control <- as.data.frame(pred.control)
pred.control <- cbind(pred.dat.control, pred.control)

pred.dat.irrigated <-  expand.grid(log.ros.area = seq(3.25, 5.25, by = .1), trt = "irrigated") #this is making a set of data that the model will predict points for. size 0:6, 25th quarile of summer precip seq(0, 6, by = .1) is the same as 0:6 but smaller increments
pred.irrigated <- predict(noseeds3, newdata = pred.dat.irrigated, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.irrigated <- as.data.frame(pred.irrigated)
pred.irrigated <- cbind(pred.dat.irrigated, pred.irrigated)

pred.dat.drought <-  expand.grid(log.ros.area = seq(3.25, 5.25, by = .1), trt = "drought") #this is making a set of data that the model will predict points for. size 0:6, 25th quarile of summer precip seq(0, 6, by = .1) is the same as 0:6 but smaller increments
pred.drought <- predict(noseeds3, newdata = pred.dat.drought, type="response", re.form=~0) #re.form = ~0 tells it to not include random effects
pred.drought <- as.data.frame(pred.drought)
pred.drought <- cbind(pred.dat.drought, pred.drought)

no.seeds <- ggplot(subset(clip, pseeds == 1), aes(x=log.ros.area, y=total.seeds))+
  geom_jitter(height = 0.025, size = 2, alpha= 0.5) +
  geom_line(data = pred.drought, aes(x = log.ros.area, y = pred.drought), color = Z[5], linewidth = 1) +
  geom_line(data = pred.irrigated, aes(x = log.ros.area, y = pred.irrigated), color = Z[1], linewidth = 1) + 
  geom_line(data = pred.control, aes(x = log.ros.area, y = pred.control), color = Z[3], linewidth = 1) + 
  labs(x = "log(Rosette Area) in 2021", y = "Total seeds in 2021") +
  theme(axis.line = element_line(colour = 'black', linewidth = 1.1), text = element_text(size = 15))#+
    #scale_x_continuous(expand = c(0, 0), limits = c(0, 6))

no.seeds
#ggsave(plot = no.seeds, file = "C:/Users/Jenna/OneDrive - The University Of British Columbia/Data Projects/Primula/Figures/clipping experiment/round 2/poisson.seedproduction.png", width = 6, height = 6, dpi = 300)

```


